\documentclass[courier]{sffms}
\author{Paul Freeman}
\surname{Freeman}
\address{717 SW 4th Street\\ Corvallis, Oregon}
\title{Enter the Webwork}
\runningtitle{Webwork}
\wordcount{34536}
\begin{document}


\chapter{Broadcast Camp}
The weekly outing to Broadcast Camp was a way of life for
the people living in the foothills. Lacking infrastructure to
carry the signal by wire, the local government had established
the Broadcast system to provide a much larger percentage of
the citizens access to the Webwork. For those living in a
broadcast shadow, travel to a nearby hilltop was usually necessary.
With a weekly schedule and a familiar group of people, it
was only a matter of time until Broadcast became an event, shared
across the area.

Tyler reached the base of the hill. Next, lay the final 
climb up the hill upon
which rested Broadcast Camp. The pack she had carried the
sixteen kilometers from the farm weighed heavy on her shoulders.
She left it on her back, but took a
moment to rest herself, learned over,
letting her back support the pack, and reached her fingers
to her toes. Her body was thin and strong; she reached
easily to the ground and pushed into it with her fingertips
to complete the stretch. She stood up, and reconsidered
her decision last week to cut her blond hair,
which everyone envied, down to almost nothing.
Without much of a second thought, she resumed the
last leg of the journey.

The chilled air whipped up into brief gusts as she neared the top of
the hill, which crept under the collar of her jacket, making
her unconsciously pull it tighter around her neck. Up ahead, the
data camp was already bustling with activity. It was a slow,
steady, productive type of busy. It was the type of busy brought
about by stiff limbs, a barely lit, pre-dawn sky, and recently
awoken minds.

She stopped for a moment, watching these strangers working. Most
groups were unpacking large bags of equipment. Some were working
on their screens. It was too early to setup the power arrays,
but there were enough batteries being wired up on this hilltop
to power a small camp for a week.

Most of this work was performed in silence. The majority of the
voices she was hearing could be traced to the food shed. This
was the only permanent building on the hilltop, and even this
was simple wood construction, no paint, and a roof which would
obviously be leaking in several places if not for the unusually
clear day.

Compared to the rest of the area, the food shed had attracted a
lively group. The owner was serving coffee and seemed to have
plenty of food on the grill. People were gathered, discussing
the mild events of a quiet life.

She became aware of the fact that she was avoiding entering the
camp proper. She set about deciding where to set up. After all,
nothing would postpone the broadcast. It was a busy morning, but
she did not see anyone she recognized, but this didn't really
surprise her. Almost everyone she knew had stayed at the farm.

Out of habit, she headed to her usual spot. It was off to the
side of the camp near a lone fir tree that flagged the nearby
tree line. It was a little lower than most people would set up,
but she hadn't missed a broadcast yet. As she made her way over,
she noticed a few of the usuals camped nearby. She was shy, and
they were shy; which was probably the reason she didn't know
anyone on the hill, despite the number of trips she had made.

The pack she carried was heavy, there was no other way to put
it, and she was happy to lower it off her back. She looked at
her watch, realizing she didn't have much time to waste. Her
setup ritual always started by unpacking everything. After
unzipping the pack and unfastening the waterproof seal, she
began removing the farm's equipment. At first, most of what she
removed were simply cables, bound with Velcro straps or fastened
with string. Each was labeled with tape, declaring the owner of
that specific cable. Under the cables lay the collected
electronics of the farm. Most were wrapped in cloth and bound.
Others were protected further still with foam or waterproof
bags. For now, she left them in a small pile on the ground,
still protected in their individual nests.

Next to be removed was the antenna. There was nothing special
about this device. The gray box was about as long as her forearm,
but squared and heavy. She didn't know the story behind the
farms' antenna, but it was obviously custom made. It was hardly
impressive, and the antenna her family had when she was a child
made this one seem shabby, but it managed to serve the needs of
the farm. Despite her distaste for it, she handled it carefully,
setting in gently on the grass next to the other equipment.

The pack was now empty except for one item. A large battery
pack, easily thirty pounds on its own, filled most of the bottom
area of the backpack. This she left in the pack, but unzipped it
fully to expose the numerous power connections.

It was probably selfish, but when she hiked to data camp alone,
she always connected her equipment first. She removed the worn
Tile from her jacket. It had been given to her by her mother,
who had received it, in turn, from her father. It had been
repaired many times, but seemed to handle each fix well. Her
Tile was the only one in the farm and knew the others thought
her undeserving of such a device. She removed a small cable from
her jacket and connected the Tile to the antenna.

She had instructions for connecting everything else, stored away
in the front pouch of the pack, but she felt certain she could
do it without them. She sat with the backpack in front of her,
between her outstretched legs, and started unwrapping the
smaller pieces of equipment. Many of the devices connected
directly to the battery pack, while others hooked through the
connections on other things. The web of components started
taking a somewhat familiar shape, in a way she couldn't explain
but which told her she wouldn't need to reference the
instructions.

There was now a problem. Her mind told her not to worry, but her
gut knew she was missing a cable. Karin's Hand Page still lay in
the pile of unconnected equipment, and a quick glance at the
pile of cables told her the one she needed was not included in
the set. She picked up the pace connecting the last devices.
Losing Karin's cable would be bad and would not help Tyler win
any points with her mates on the farm. As she made connections
between the last couple devices, her suspicions were confirmed.
Feeling around in the bottom of the pack turned up nothing. It's
doubtful anything fell out of the backpack, what with it being
waterproof sealed and zipped up tight. But even if the wire
turned up later, back at the farm, Karin will have missed her
broadcast, and Tyler will be blamed.

Frustrated with herself, she made a helpless glance around the
area in which she was seated. To no surprise, nothing was lying
unconnected around her. Well, the antenna was still not
connected. She smiled as she hooked up the most important
component, as she thought about how much worse the situation
would have been, had she forgotten to hook up the antenna as she
hunted for one cable. And anyway, Karin and her were on good
terms. Certainly, she could make it seven days without a
broadcast. But still, this was a sloppy move.

As she sat with her thoughts, the sun rose behind her. She
noticed the ambient change and glanced back at the sliver of
yellow in the distance. Two weeks ago when she was here, the sun
hadn't come up until the broadcast had started. Her watch told
her she had another three minutes today.

Sometimes the broadcasts were late. Less often, they were early.
One of her first weeks on the farm, an early broadcast was
responsible for a ninety percent data loss. Joseph was blamed
for the loss, and had few friends for the following six days.
The next broadcast confirmed his story, but even with his name
cleared, he had yet to travel back to the data camp for
broadcast.

The beeps from the devices in front of her signaled that
today's broadcast was more or less on time. The indicator on the
battery pack showed as full. Even Karin's Hand Page turned on,
reminding Tyler of her screw up. She reached over and shut it
off. There was no sense running down the battery, as well. A
quick look over the other equipment verified that everything was
ready for the broadcast.

\chapter{Two}
Tyler rounded the bend that signified she was three miles from
the farm. The broadcast had felt like a wash. On one hand, it
had been smooth: her draw had been high, the manifest had
completed with no errors, and power draw had been rather low. On
the other hand, she was thinking the whole way home about how to
apologize to Karin.

The last three miles was always the longest. On foot, a trip to
data camp took four and a half hours. With a good broadcast draw
you could do the whole thing in five. Many of the other
travelers to data camp came on horseback. Some even drove. On
Tyler's farm, though, the horses were usually put to work. They
didn't have any motorized vehicles, at least, of which she was
aware. They had always walked. She had volunteered for the trips
soon after her arrival at the farm, and after a few months of
shadowing the process, they gave her the responsibility of
making the trip solo.

Despite the season, it had warmed up quickly. She had removed
her jacket before leaving data camp. The skin of her arms and
face was still chilled, but she could tell her shirt was damp
with sweat under the straps of the backpack.

She passed by the farms' nearest neighbor, an old recluse who
went by Peters. His home barely qualified as a shack, but the
old metal roof seemed to miraculously support an impressive
power array. The panels, covered in dust, must have been
working, considering the volume of the music being played in the
house. His windows were curtained with various cloth materials
but Tyler always felt like she was being watched when she was
passing the house.

Another half hour and she was passing through the open gate and
walking up the road to the farmhouse.

The main house was an ancient house, with six official bedrooms,
but it currently slept around thirty people. Additionally,
scattered around the rest of the property were a handful of
other buildings which housed an additional forty or so.

Tyler made her way up to the house. Several of her mates waved
at her as they milled around tending to the business of the
farm, but there was no grand celebration for her safe return.

On broadcast day, all the members of the farm ate lunch
together. Even if you had nothing on the manifest, you were
required to sign in. The landlords would assist in settling
disputes. Issues pertaining to the farm were discussed. Weekly
assignments were given out. At the end of this event, the
devices could be collected.

Since the trip had gone smoothly, there was still time before
the meal was prepared. Tyler had decided to apologize to Karin
before lunch. Inside the house, she made her way downstairs to
the basement. Bryce was in the basement, with several lights on
around him. He was inspecting some data using a page on the
wall. Bryce maintained the data on the farm, and it kept him
very busy. In addition to caring for the equipment, he assisted
with special tasks and device repairs. He was certainly no
wizard with tools, but he cared about details and always took
his time. Also, he was the best person for the job right now.

"You forgot Karin's cable, today," he said as she entered. His
eyes remained focused on his work.

"Yeah...," was the best she could come up with as she crossed
the room and unloaded her pack onto a bench next to the far
wall. The missing cable sat in the center of the nearby table.
"Do you know where she is?"

"Haven't seen her. But she's probably out back. I think she has
the plane working." Bryce gave her a sly smile. Tyler raised an
eyebrow in return. The plane was working? That would be worth
seeing, even if it came along with delivery of some bad news.

\chapter{Three}
It turned out that the plane was not working. You could say the
plane was RUNNING... sort of. You could say the plane was
MOVING. You could NOT, however, say the plane was working. But
still, there it sat in the yard, propeller spinning away with a
quiet hum. A small group of the farms inhabitants were looking
at the plane awkwardly. They were looking at the plane awkwardly
to avoid looking at Karin, who was looking at Tyler.

"So, what you're saying," Karin said patronizingly, "is that traveling to Broadcast isn't
something you're able to take care of on your own?" She continued, obviously
not expecting an answer, "I understand it's a lot of stress. We can find
someone else who wants to take it seriously."

Karin was a little
angrier than Tyler had expected. Their present situation had
been building in the two minutes since Tyler had given her
the bad news. She would have appreciated someone coming 
to her defense, but that wasn't likely. Everyone knew the frustration
of missing Broadcast, including Tyler.

"Look, Karin, I'm sorry. I can't fix this. I can only tell you I'm sorry.
You can be mad at me if you want."

The plea had no affect.

"You don't get it!" Karin finally shouted. "The plan for the last piece of the plane was on my
manifest. What the hell am I supposed to do for the next week? I have
nothing to work on! They never should have let you go alone."

With this final exasperated observation, the young woman turned in
her boots. One quick gesture on her control board silenced the motor
powering the planes' rotor. The small crowd nearby made a performance
of avoiding the enraged girl by nearly scattering as she approached.
Karin lifted the plane despite its seven foot wingspan and headed to
the workshop next to the barn.


\chapter{Four}
By lunchtime, the tension lifted somewhat. The surprisingly beautiful
weather meant that this weeks' Broadcast lunch was held outdoors.
Long wooden tables, set just off the farmhouses' back porch, served
these events well. Off to one side of the eating area, the landlords 
sat at their own, smaller table. The community
sign-in book was open on their table, and the landlords greeted, and
made smalltalk with, the members of the farm as they approached the
table to sign in. Although Broadcast Lunch was taken seriously, there
seemed to be an unspoken agreement amongst the farmers to keep
the mood light.

Tyler was sitting with her friend, Triss. Primarily a field hand, his appearance
hardly fit the job description. He was tall, with miniature, wiry, muscles.
His face was long, narrow, and with high cheekbones. His hair was jet black,
thick, and long enough to cover most of his ears and neck. The poor guy was
allergic to almost everything on a farm, and yet he never complained about
the work. He had tracked her down shortly
after the incident with Karin. Tyler had been close with Triss since her arrival
at the farm six months back. He had been the first person to sit and talk with
her after she settled at the farm. The conversation had been slightly
forced, but she had appreciated his effort despite his noticeable inability
to make casual conversation. She had let his kindness payoff for him just a few days
later. But while he had been kissing his way down her neck, she had been regretting
her decision. She had broken free of him when he made his next move
and walked back to her room alone. Triss had
taken her rejection well, and had not tested the boundaries of their friendship since.

By now, most of their farmmates had gotten seated. The landlord would be speaking
soon. Tyler turned her attention to the landlords' table. She had been told that
the landlords had owned the
property for several generation; since before the Destruction. They had always
had others living on the property. The didn't collect rent. Everyone did their
part. If anyone, including the landlords, became a problem,
there was an anonymous vote. If that
person didn't have the support of two thirds of the farm, they had to leave.
It was simple and it worked. Tyler had never known anyone who had been
forced to leave, but it had been known to happen in the past.

Jondra stood up and called the start of the meeting.

"What an unexpectedly beautiful day for a Broadcast Lunch," she said, and smiled at the
group. "I hope everyone has had positive experiences over the last week."

Jondra was the unofficial head of the landlord family. She was a beautiful, middle-aged
woman with long, dark, curly hair. She was short, with a big smile and dark
skin. Jondra treated Tyler like her daughter. In fact, Jondra treated everyone on
the farm like they were her own children.

Being their pseudo leader, Jondra was usually the speaker
at most of the farm's gatherings.
From what Tyler had heard, she had recently taken over the responsibility
from her father. Most people seemed to have been happy with the change.
The rest of Jondra's family included;
her mother, her father and his mother, her brother, and her brother's adobpted son.
Their family was not large, but they were extremely well respected amonst the 
farm community.

As Jondra summarized the week for the group, her father, 
Alvar, was reviewing the weekly population report.
The report finalized at the end of sign in, and provided
Alvar with extensive data on the changes in population over the previous week.
New arrivals would be welcomed and introduced.

Being a new arrival on the farm came along with some important
responsibilities. Upon arrival, the new potential resident could
sleep in the barn with approval from one of the landlords. During
the day, the temporary residents of the barn were given a variety
of tasks, suitable to their capabilities, although most of the time, 
they worked in the fields. They were required to eat meals with
the other residents, which was, in many ways, their most important
job. Social acceptance by the community was highly important
because at their second Broadcast Lunch, they woud be required
to pass a vote. Failure to pass this initial vote meant expulsion
from the farm. The arrival of new people to the farm was rare,
but it did happen. Tyler's own arrival, for one, but there had
also been several other additions during her six months of residency.
Today, the that roster was empty.

After dealing with the business of new arrivals, the absense of any
residents was discussed. Someone might be on this list for a
number of reasons. Most of the time, the names appearing on this
list were expected. It could be a hunting party, a trip to town,
a visit with friends, or any of a number of other reasons. In fact,
travel away from the farm was encouraged. For some, their
time at the farm simply ended, and they moved on to the next step
of their life. This was less common, but was not discouraged by
the community. Then there were the mysteries. Some would
leave in the night. Others would go to town and never return.
Accidents would happen. These mysteries were investigated,
but not overly so. In these times, things happened; life had to
move forward. As with the new arrival list, this list was reported
to be empty.

With the formalities disposed, there was a noticable increase in
peoples attention toward Jondra. It was time for Collection to begin.

Collection was used to encourage attendance of the lunch.
Bryce hosted this portion of the event and he had been busy
syncronizing devices with the farms cental system and verifying
the Broadcast manifests since Tyler and dropped off the backpack.
To improve the farm's data pool, all
personal devices were required to be syncronized. The community
put up with the personal data tracking, as it increased
community accountability and greatly increased the farms
mining capabilities.

Today was a little odd due to the fact that Bryce had not arrived
at lunch yet. Data syncronization was a relatively
quick process, and Bryce was very practiced at the task. But,
there were many things that could go wrong or slow the
process, and so his absense was not extrordinary.

"As Bryce has not yet arrived,"
Jondra said to the group, "go ahead and enjoy your meals.
We will resume the meeting in a little bit."

The farm enforced Page Silence on the morning of
Broadcast. This wasn't very difficult to enforce, since most devices
were in the pack on the way to Broadcast Camp. However, for
people who had not requested Broadcast, the rule was monitored,
and whoever travelled to Broadcast Camp was also expected
to comply. Everyone considered it a terribly old-fashioned policy
and it was probably the most violated policy on the farm.

To combat the lack of device usage, the farm encouraged a variety
of activities for those not already assigned morning work.
Demonstrations, such as the plane Karin had been constructing,
were also encouraged. Even with the distractions, everyone
was very focused on getting their devices back after Broadcast.

Tyler had resisted the natural impulse, and caught herself
several times pulling out her Page. Had she not resisted,
the central system at the farm woud have quickly noticed
and logged it into her file, which could jeopordize her
ability to make future trips, especially when compounded
with the incident with Karin.

It was not long before Bryce arrived at the table with the
devices. He seemed very focused today, for someone
who was generally very laid back. 

"If I could get everyone's attention for just a couple
minutes," he started. "I have an important announcement
concerning all of us. Then I will distribute devices."

The announcement would be a message from the city. These
messages arrived from time to time, and related to Union-wide
matters. The impact of the announcements
ranged in scale from renaming of far off cities (with which Bryce
would not even bother them) to impending attacks from
other counrties (which, these days, were very rare).

"There is not a great way to start this," Bryce spoke slowly,
"But, basically, it seems they are cutting Broadcast down to
every two weeks." He paused as the audience went from 
silent to distinct murmuring. Bryce went on, "The resons for
this change are not given. I know this is a shock to everyone."

A change like this was big. Broadcast had been established
a long time ago, shortly after the end of the Destruction.
A Broadcast would be missed every now and then. In times
of Union unease, the Broadcast could stop for several weeks.
But, to make a sweeping change in the Broadcast without
reason was a shock.

Bryce wrapped up, "Next weeks Broadcast is scheduled,
but there will not be one the following week, so please
plan ahead. Also, since the Broadcast will be handling
much larger manifests, I would expect higher data loss
rates. We'll have to see how it goes." He started laying
out the devices on the table. "That's all I have for today."

The end of Bryce's talk started the usual commotion, as
everyone milled up to the table to retrieve their device.
The concern everyone felt over Broadcast was quickly
masked by the prospect of their new data. Messages
from family and friends, news from the city, applications,
database updates, packages, and other updates all
awaited them in the Page world. Little would be said
the rest of the lunch as everyone synced themselves.

Tyler was in a rush, too, but was still avoiding Karin.
As Karen arrived at the table, she snatched her
un-synced device quickly and shot Tyler a look of 
cold anger. Karin's anger toward Tyler could be thought
of as a preview of the way the entire farm would feel
in two weeks; after the first of many missed broadcasts.

\chapter{Five}
Bryce took each device out of the backpack and laid it on
his workbench. Despite her screwup today, Tyler always did
a good job traveling to Broadcast Camp, despite growing up
outside of broadcast distance. She had a natural ability
with electronics.

When Tyler had arrived at the farm, there was much
discussion over the situation. Presumably, she had no
family. She claimed her parents had both died in an
accident. She had traveled to the farm after finding it
marked on one of her father's maps. The distance she
had walked was great, and she had had little in the
way of supplies when she arrived, but she was in good
health. She was apparently a strong survivor. However,
it was interesting that, although her father had
apparently known about the farm, no one on the 
farm seemed to know anything about Tyler or her
parents.

And then there was the mystery with her Hand Page.
Bryce removed it from the backpack and set 
it on the workbench. It immediately turned on and
began the syncing process. Bryce watched the progess
on the Page propped up next to him.

Tyler's Hand Page was unique. It was obviously military
quality, but most devices these days were. Very few of
the consumer products were still working, although
there were some.
During his repairs of the device, he noticed technology
which he had never seen, and knew nothing about.
He worried what he would do if one of these parts
ever wore out. And so, he had always done his best
work on the repairs the special device needed.

But still, hers seemed to have
limitless capacity - not that Tyler was using much of it.
Her manifests consisted mostly of books, which she
seemed to have an amazing ability to locate. In the
short time she had lived on the farm, she had increased
the library of books by probably fifty percent.

The sync completed, with the security scan, as Bryce
suspected, showing nothing unusual. It reported the
unusually long web paths and a large number of 
unique retrievals, but this was completely expected
and not unusual for Tyler. In general, her manifest was
valuable for the farm and very clean. The girl was
a good retriever.

Her device powered off when it completed and he placed
the next one on the table. Most of these would not
go as smoothly as Tylers, due to: longer manifests,
slower electronics, and additional security checks.
The one currently on the table was a specific
troublemaker, so he turned his attention to the
Union update.

The Union included a rather large manifest with
each broadcast. Failure to accept the manifest blocked
the entire Broadcast, making it madatory. The
majority of it was useless, and was simply archived 
for later use. Bryce started reviewing the week's
manifest. There was special bulletin which he began
reading.

\chapter{Tyler}
Morgan made her way down the trail she had walked many
times. She was nearing the end and could see the fire
flickering in the distance.

This was the first time this year they had done this.
For years, she and Triss had met out here to play
games, gossip, plan trips, and dream. Late in the fall,
Tyler began joining them, which had originally angered
Morgan greatly, but was now just mildly frustrating.
She liked Tyler, but this time with Triss was important;
he was someone who she had been friends with her entire
life. Coming out to this spot was their tradition
and she didn't like sharing it with someone new
just because Triss had suddenly turned into a love sick
puppy. Strangely, though, Tyler and Triss seemed
to just be friends. And, she had to admit that
Tyler was fun. She brought a wit to the evenings; something of
which Triss was less capable. Tyler was
smart and, yet, seemed to genuinely care about,
Triss, which Morgan appreciated.

As she reached the edge of the light eminating from
the fire, she saw Tyler and Triss sitting, side by side,
in front of it. Both had their Pages out, and were
playing some kind of gesture imitation game. They
both moved their hands in decent syncronization.
Occasionally, one of them would make a mistake
and Triss would erupt with laughter. Tyler would
smile and look sweetly back at him, only
joining in the laughter once in a while.

Everytime Morgan saw Tyler she was reminded how
jealous she was of her hair. That girl had such light
hair. No one on the farm had hair as light as hers.
It was the color of straw and fell halfway down her
back.

"What took you so long?" asked Tyler as Morgan
entered the circle of light from the fire.

"Oh," Morgan sighed, "Gily isn't keeping time
with the other guys and wanted me to skip
tonight. He's mad now because I told him I
wouldn't."

Gily was Morgan's boyfriend of almost three years;
basically the entire time he had lived there.
Morgan had lived on the farm her whole life.
Gily was a burley man, with plenty of extra muscle.
He had arrived with a passing timber company,
and had decided to stay after Morgan had
taken him to her bed... three nights in a row.
Looking back, she
didn't view it as the wisest decision, but she didn't
often regret it. Gily could be a pain and would
sometimes get blindly drunk, but he seemed to
have a soft spot for Morgan, and took good care
of her. On the other hand, he wanted nothing to do
with her friends, Tyler and Triss. Tyler, specifically,
clashed harshly with him, and the two avoided
each other whenever possible.

Changing the subject, she posed the question,
"What do you guys think about the Broadcast
change?"

"Well," answered Triss, "based on what I saw
today, I think Karin is going to be pretty upset."
He giggled and looked to Tyler for approval.
She smiled and gave him a nod. She had made
the same comment to him only moments
ago.

"It seems stange to me," said Morgan, and
then felt very silly for saying it.
Obviously, it was strange. When the broadcast
had originally been scheduled weekly, it was
because of the energy crisis. But certainly,
the crisis couldn't be any worse now than it
had been. Most of the waring had stopped
over fifteen years ago. Shouldn't things be
improving? But, she realized that none 
of these thoughts needed
to be brought up, they were all thinking it.

Tyler looked out into the valley. Quietly,
she said, "It's certainly difficult to figure out what's
going on out there." In many ways, this was as
pointless a comment as Morgan's, but it was
spoken with certain amount of intrigue which
cause both Triss and Morgan to focus on
the words intently. The three of them sat quietly,
listening to the pops of the fire as they stared
into the night.

\chapter{Wood Party}
A couple hours had past and the fire had been
allowed to die down. The were maintaining the
hot coals one log at a time as they sat
together on the bare ground at its front.

The night seemed never ending.
There was gossip of Triss and his "girlfriend" in the big
city, who continued asking him to take her out,
despite being only fifteen and having no idea he
was nine years older. The girls called him a creep,
but laughed it off. He was harmless, anyway,
and would never leave the farm.
Morgan was planning a long trip north to look
for Gily's family. They were leaving in the late
spring. It meant crossing into the next country
illegally and she had little information on the area,
but she was excited none the less. Tyler had a new
book of ghost stories from before the Destruction.
It was fiction, of course, but the world it described
fed their imagination wildly as they sat around the
fire reading.

Eventually, the conversation wound down. Tyler and
Triss sat on the ground, their backs resting against
the big log which had been their chair just a short
while ago. Morgan lay stretched out between them,
her head resting on Tyler's thigh and her legs draped
over Triss's legs. Tyler was hard at work braiding an
elaborate webbing through Morgan's hair using bits of
green wood she had cut from a tree.

As the sat silently (with Triss slowly nodding his head
up and down as he fought sleep), the sound of a owl
began repeating quietly, and then quickly a little
louder. In less than a second, crickets joined in, along
with a quiet wolf howl. The camp was suddenly alive
with the artificial sounds of wilderness. Tyler's Page,
which was still out was laying beside her. When she
glanced over, the owls went silent and a map appeared.

"That's interesting," Tyler said. Morgan sat up, allowing
Tyler to stand with the Page in her hand. She walked
around the fire holding it in front of her. She was now
facing the valley. The others had their Pages out now,
too.

"Can you see them?" asked Morgan.

"No. Not yet. Wait. Maybe." She moved to her right
just a little. "Yes," she affirmed. "Someone is down
there."

The other two stood now beside her and the small group
looked into the valley. Still a good ways away, could be
seen the distinct movement of light through the trees.

\chapter{Visitors}
It wasn't unheard of to see people in the woods at
night. In fact, the only reason the security system
bothered to notify the three of them was because
they were nearby. That being said, Tyler didn't want
an encounter with this group, and it seemed to be
climbing the hill directly towards them.

"They've no doubt seen the fire," stated Morgan,
matter-of-factly. "Should we just head back?" The
trio's campsite was not technically on the farm
property; it was quite a ways off it, actually. But
the land wasn't claimed by anyone else, and the
farm was the nearest settlement.

"It's up to you guys," Tyler decided. "I think I'm
going to wait around and get a look at these 
darks. Shouldn't be too hard to hide out."

"I'm for," said Triss. Morgan felt their eyes on her
and the social pressue won.

"Alright. But let's find a good spot. And far back."

They left the fire and headed off into the darkness.
It was immensely dark. Tyler turned up the
brightness on her page until they had 
enough light to walk.
They move slowly through the underbrush,
as torns and sticks scratched at them.
Tyler had purposefully picked this route as it
wouldn't likely be the route the mystery
party would take.

She led them around the back and then up
a small rise. The small hill put them almost
level with the height of their original location,
but they were now separated from the camp
by around fifty meters of dense undergrowth.
Laying flat on the back side of the knoll, they
would be basically invisible.

They expected to see people any moment,
but it was a long fifteen minutes before lights
and voices began drifting towards them from
beyond the fire. As they had expected, the
travelers had headed towards their campfire.
The first person who walked into the light
surprised all of them. It was a Union Police
Officer.

\chapter{Union Police}
Bishop Dale liked being out in the forest. He
was rarely able to travel away from his urban
neighborhood. He enjoyed taking his children
to the park, and they had even camped in the
park once. Right now, it was dark; really dark.
But he was enjoying the sounds of the forest
and trying not to think too much about the
mission.

"Sir," one of his men reported, 
"we've spotted a fire at the top of the hill."

"Thank you. Bear that direction," Bishop
ordered. "We'll
investigate it." The subordinate turned and
made his way to the front of the party. Soon,
Bishop and the rest of the team was on
the move again.

Bishop hoped this wasn't a settlement
somehow left off the map. His teams presence
here wasn't meant to be secret, but they
weren't trying to trespass, either. Marching
into a settlement in the middle of night was
bad publicity, at best, or deadly, if the
settlement was hostile.

As they neared the hill, and the campfire,
Bishop ordered the team to holster their
weapons. Only a few of the team even had
theirs drawn. He saw no one around, but
the fire was freshly built up. No doubt, the
campers saw his team approaching. They
either left or hid.

"Hello!" Bishop addressed the dark forest,
"My name is Bishop Dale, Rank 3 officer of
the Union Police. Please return to camp and
introduce yourself. We are no threat to you."
He waited patiently for a reply and then
looked back at his team for Gretta. Seeing
her, he said, "Gretta, can you do a scan?"

"Yes, sir," she responded, "Doing it now."

It was a crude tool, the scanner, but it
rarely gave false information, just incomplete
information. As the results appeared on the
screen, he began speaking again.

"Trissan Potts and Morgan Alvarez. I assume
you can hear me. Please remember what I
say and pass it on to your leaders." Bishop
spoke slowly, considering his words carefully.

"Tomorrow, we will stop by to meet with
your community. We may need their help
with our investigation. We request everyones
coorporation." Bishop Dale stood a moment,
considered saying more, and then decided
against it.

He turned around and spoke to the others,
"Alright team, head east along this ridge,
same as before. Keep your eyes open."

The scout of the group considered his
options and then ducked under the low
hanging branch of a large tree and headed
off into the woods. The others followed,
the lights on their uniforms casting that
same eerie glow on the forest around them.
Bishop brought up the rear. Just before he
stepped under the branch he scanned the
dark one more time, but saw no one.

\chapter{The Message}
Tyler watched with her two friends as the
UPs headed east, away from the camp. There
was nothing scary about the encounter; nothing
suspicious; no reason to be hiding in the woods.
Still, when the call had come for them to come
out, she put a hand on each of her friends,
communicating her intention to stay 
where they were.

After they emerged from hiding and returned
to the fire circle, the tone was somber.

"What was that all about?" wonder Morgan aloud.

Triss had a more specific question, 
"Why are the police in the woods?" It was a good
question.

Tyler thought of a question they actually needed
to answer. "Do you think we should tell Jondra
tonight?"

It was already late. Most of the community would
be asleep. Waking Jondra would surely alarm many
others. Perhaps it would be best to wait for morning.
It wasn't like the Union Policy were planning an
attack or anything.

"I think we should. Shouldn't we?" said a rather
worried looking Morgan.

"We should," agreed Triss.

"Why don't you tell her, then," joked Tyler.

Triss made a startled face and said, 
"I don't want to tell her. You're the one she likes."

Triss wasn't being serious, but he was right. Jondra
did like Tyler and Jondra should probably be told tonight.
Tyler placed Jondra into the Page queue and
put the Page away until the connection was made.

They walked in silence a while before the Page
alerted Tyler that Jondra was on. Tyler removed
the Page from its pocket. Jondra looked quite
awake for having been obviously just woken.

"Hi, Tyler," Jondra said softly.

Tyler tried to be concise, "Hi, Jondra. We were in
the forest southeast of the farm about two
kilometers and saw Union Police."

Jondra looked more awake now. "Is everything
alright? What happened?"

Tyler again spoke concisely, "Nothing happened.
We hid, but they knew we were there.
Left a message saying
they were coming by the farm tomorrow to talk.
Then they headed east."

Jondra was quiet. Then she said with a smile,
"Well, it's probably nothing. Thanks for
reporting. Please get back safely."

"We will, we're almost back now."

"Alright. Goodnight, Tyler."

"Goodnight."

The conversation ended and the forest was 
silent again.

Morgan broke the silence. "Hey, why did that
dark only know me and Triss were there?"

"His tech must not pick up my Page,"
Tyler said. "Must only read certain kinds
of hardware."

\chapter{Barracks}
When they reached the fenceline of the farm
Morgan left the group, taking the shorter
path towards the farm house where she
stayed. Tyler and Triss threw up casual
hand waves signifying her departure and began
following the fence in the other direction, towards
the barracks.

Aside the farmhouse, people generally lived
in the barracks. The barracks consisted of three
buildings on one edge of the farm. Those who
did not stay in one of these two places did so
out of choice, and had typically created their
own camps around the farm someplace. Some
people preferred privacy. As for the barracks,
they we roughly divided into three groups:
people with children, long term residents, and
new residents.

The barracks did not provide much in the way
of privacy. Each person had their own small
room, but most of the living space was shared.
When the barracks was powered, it provided
running water and, occasionally, hot water.

Triss lived in the long term barracks, having lived
on the farm his entire life. Tyler and Triss entered
the side door of the long building. It was warmer
inside, but not much. Heating was too inefficient.
Lighting, on the other hand, could be supplied
all night, and a variety of lighting strips gave
the room plenty of light to move about in the room.

Quietly, the pair walked across the open living
area and entered the corridor of the 
northern wing of rooms. Just two doors down,
they reached Triss's room. Tyler gave him a hug
and told him to have a good night. He closed the
door behind him and Tyler continued down the
hallway.

Just three doors down, she paused at another
door, but moments later, turn back, returned to
living area, crossed to the door, and exited.

Back outside, she headed across the circular
courtyard between the three barrack buldings.
She entered one of the others, the new resident
barracks, and made her way to her own room.

She entered her room and sat on the bed. The,
room was mostly empty, common for someone
new to the farm. Most of the decoration were
clothing; a small pile decorated on corner, and
some folded stack decorated a bench against one
wall. From the wall she had hung a variety of item
she had found or collected since arriving. An
unframed canvas painted with a dolpin jumping
over the planet Jupiter hung in the middle of one
wall. The other wall displayed her small collection of
antlers. She had one shelf of item from
pre-Destruction, mostly just stuff that seemed
interesting, but probably had no real value.

She removed her Page from her jacket and
connected it to a cable running from the wall.
It was charging right now, but the barracks would
probably go dead before morning. It was rare to
make it though a whole night with power.

She removed her jacket and hung it on a
hook next to
another, substantially thicker jacket. She slid
her pants off and tossed them in the pile with
the other clothes. From the same pile she dug
out another pair of pants, but these meant for
sleeping. She slipped them on and left her room;
headed for the bathroom.  

\chapter{Morgan}
Although, she and Gily lived in the basement,
in an unfinished room, she appreciated the
conveniences that came from living in the
farmhouse. There was power available on all but the
darkest days of winter, and running water was
accessible from a sink, built into a private
area next to their room.

She stood at this sink, looking at herself in the mirror,
which hung over it. The lighting was poor, but
she wouldn't turn it brighter as it would leak over the
top of the unfinished wall to where Gily was sleeping.
She still felt young, but her body was surely aging.
The creases of her body were turning into permanent
wrinkles. They were soft and she didn't mind them, but
they were slowly taking her youth. She was turning thirty
one next month. Gily was seven years
older than Morgan. His body had
hardly aged in the time she had known him.
She still found herself taking
notice when he walked into a room. He took care of her
and she knew he loved her. She loved him more than
anyone.

Gily had told her about Grace six weeks ago. The
argument had drug out for hours. Morgan helt as
though she had run out of tears. The way he had
made it all her fault was eating away at her. He
had said he could never be faithful with just her.
It stung, and she had grown determined to prove him
wrong. The following weeks had been better. She had
given it her all to keep him at home. It had seemed to be
working until the previous night, when he left after
dinner without saying a word. She was crushed.

Today they had fought until she had left with Tyler
and Triss. They knew none of this. Now, Morgan was
scared again that Gily would leave. Standing there
at the sink, she looked again at the girl in the mirror.
That girl had tears, now, running down her face, but
Morgan thought there was determination in her eyes.
As she removed her clothes, the unexercised, but
not unattractive body, 
which had once been used to convince
Gily to leave the timber company, began to reveal
itself. What she saw in the mirror
was long, dark, hair hanging over a round
face; thin arms, a soft belly, and wide hips;
standing on normal legs.
Fully naked, now, standing at the mirror, she carefully
wiped the remaining tears off her face. She turned and
quietly opened the door to the room where she would
attempt to give Gily at least one good reason to stay.

\chapter{Lack of Answers}
Jondra's meeting with the Union Police had been of little
use to the curiosity of anyone on the farm.
Bishop Dale informed her that his team,
and probably others, would be in the area performing
an investigation. He would appreciate the farms
cooperation with the investigation by simply staying
out of the way. He told her he expected the investigation
to wrap up quickly. He had not answered questions
and he had left before five minutes had past.
It was a small performance considering the
lavish promotion last night in the woods.

None of this followed any reasonable logic, and Jondra
hadn't been fooled. The UPs were investigating
something, that much was true. But this was not
routine, in any sense. There was more beneath the
surface of this investigation, but Jondra would not
learn any more just yet.

Despite her unease, her parents lounged quietly,
as they sat together on the office's plush couch.

"Really, pumpkin," her mother spoke to her sweetly.
"I don't think there is anything to worry about."

Her father agreed. "Yes, honey, there was a time
when police patrolled this area regularly."
He continued, "It's probably not a bad idea
to have them around once in a while." Jondra
decided to keep silent. There was no point
starting an argument with her parents.

"I suppose I can live with that assessment," she
said in a tone meant to settle them, "You two
are always keeping me grounded." She smiled
at them, adoring the way her father still
put his arm around her mother when they sat
together. "Well, I have some things to care for."

She left them the room and each others company
and walked across the second floor of the
farmhouse to her own room. In her memories,
it was still her parent's room, but it had become
hers when she was passed the responsibilities of the
farm. The room was large with an attached
bathroom, as well as a sliding door leading
directly to the porch. The carpet had long ago
worn out, and they had pulled it out, but the
floors gave the room a natural look she liked.

The bed in the center of the room was huge.
Her parents told her it was what used to be
called a "California King". The original mattress
had been replaced long ago with a handmade
one stuffed with feathers. She had grown up
in this room, having shared it with her parents
as a child and then having it to herself these
last few years. This room could be in any other
place in the world and she would feel like she
was home.

She lay back on the bed and glanced at the 
panel on the wall beyond her outstretched feet.
It light up with the power map of the farm.
The lower right quarter of the panel no longer
displayed, but Bryce had coerced the software
into ignoring that space and so the panel
was still limping along.

Looking at the power map confirmed another
strong day for generation. The farm's panels
were providing forty percent over current
usage, and the energy storage system would
be nearly full by sunset.

Out of habit, Jondra reached up to flip the
panel to her next application before
remembering the gesture capture system
had given out last week. With a groan, she
rose to a seated position again and sat
a moment, building the will to actually
stand. Finally standing, she walked the
six or so feet to the panel and brushed
her search application onto the panel. It
would be worth looking a little into the
UP visit. Data could be found, if you knew
how to look. She set about mining the
farm's servers.

\chapter{The Cave}
Bishop and his team entered the cave two
hours after seeing the man enter it. Until
he ordered them in, they had been
standing around outside. Now, he could
happily report, if asked to do so, that they
were standing around inside.

The cave system had extended further
into the mountain than expected, however,
the small part of Bishop that had hoped
to find a super villan lair was left
unsatisfied as they reached the rocky end
of the road and discovered only more
darkness.

Now, standing on the uneven ground,
one of the younger
soldiers suggested it was an elaborate trap,
causing mild panic amongst the team.

"Alright," Bishop conceded, "Head back,
double time. But be safe. Watch your
footing. Let's get out of this damn cave."

He was frustrated leaving. He would have
prefered investigating more thoroughly.
But the kid had been right, a trap like that,
however unlikely, could have been executed
by that man. No sense taking chances.
They would catch up with him eventually.
It was only a matter of time.

But how did
he get out of that cave? Bishop had
seen his scout's live feed as he had eyes
on the dark walking into that place.
Finding him not there only made Bishop
more sure they were on the right track.

His team set up camp at the mouth of
the cave.

\chapter{Day Off}
Having traveled to Broadcast Camp yesterday,
Tyler had today to herself. Days off were not
customarily observed on the farm, and it was
generally expected one would help out in some
way or learn something new. Enforcement wasn't
necessary, it seemed to happen naturally.

It was on these days that Tyler often found
herself in the kitchen, working with Vishnu.
An old man, with graying hair and wrinkled skin,
Vishnu was one of the few residents who had
moved to the farm from the city. He was also
one of the few residents who remembered the
time before the Destruction.

Tyler thought Vishnu an absolute wizard in the
kitchen. He rarely prepared the 
same meals, although
during the winter he stretched this rule a little.
His creativity turned the farm's 
canned fruit and pickled vegetables into fragrant
meals which routinely turned the heads of the people
walking past the kitchen. And in the summer,
with plenty of fresh produce, the food could
take on mystical qualities. In fact, a good deal
of their farm's lore bore mention of Vishnu's famous
creations.

Today, Tyler was sitting in front of a giant stock pot
making something in-between stew and gravy.
Vishnu would hobble up to Tyler with arms full,
the contents of which would be left for her
to clean, dice, and incorporate into the pot.
He would mutter to himself and continue to
explore the pantry, waiting for one of its occupants
to slide into place in one of his mental recipes.

As she finished dicing four large onions, he
startled her slightly by placing his hand on her
shoulder.

"My dear," he said in a surprised voice. "Why are
you crying?"

She turned and looked at him, with tears streaming
down her face. She smiled, and then began laughing
as she attempted to wipe her face with her forearm.
Vishnu's kind eyes looked back at her and he
chuckled to himself. 
He peaked into the pot, standing on tip toe to see
inside. Then he turned and headed for his herbs,
growing in a box on the windowsill.
Tyler, still trying to dry her face,
added the onions to the pot.

"What's next?" she asked him, as he plucked a few
leaves from the herbs which had made it through
the winter. He returned to the pot.

"Oh, I think that will be done now," he said. He moved
a step stool in front of the stove and climbed up to
add the herbs. He stirred the pot slowly with a long
wooden spoon. "Can you put the bread in the oven?"

"Sure," she answered and walked over to four loaves
of bread dough, rising on a pair of cookie sheets.
She brought them to the oven and placed them inside.

Suddenly, curiosity struck her and she said, "Why do
you think the Union Police are here?"

The old man stood stirring the contents of the pot
without responding. It almost seems like he hadn't
heard the question. But he had, because
 he seemed to settle
on his answer.

"You never can tell," he said, stepping down the two
short steps and turning around to face her. "But I
think they would not be all the way out here
without a good reason."

"It worries me," she said.

"Yes. Don't think too hard on it."

"Thank you, Vishnu."

She left the kitchen though the sliding door
to the back porch,
not knowing exactly where she was heading,
but suddenly wanting to be alone.

As she walked across the farm, the
late-afternoon sky was already giving
way to dusk, helped by the development
of heavy cloud cover. The air had lost
some of its crispness and the humidity
in the air was keeping it warmer than
it appeared. Much of the community
was working in the gardens today.
She noticed Karin as she walked by
the workers. The cold eyes that looked
back told her the wound was still
gushing.

The barn was her destination now. She
had made the decision when she noted
that she was walking towards it anyway.
Last she had heard, it was still empty of
travelers or new residents. When empty,
the barn made an ideal place to gather
ones thoughts.

She pulled the large wooden door
open and walked inside. The horses were
out in the field, leaving the barn empty, as
she suspected. She climbed the ladder to
the hay loft and sat in the middle of floor, away
from the barn's large window. Her space 
was cool and dark and smelled of wood and
hay.

Up here, she let her thoughts free, to
wander where they may. At first, her 
thoughts were of the Union Police. Their
encounter in the woods had suddenly
brought the outside world to her
doorstep.
Tyler lived on the farm now, but up until
six months ago, she had lived in physical
isolation with her family.

\chapter{Cabin in the Woods}
Tyler was born during the final years of the
time known as The Destruction. By this time,
the isolation her parents had spent a lifetime
establishing was paying off, and they were
living lives, independent of the dying world,
in a comfortable cabin in the woods.

Living through The Destruction was
unimaginable, and a generation of the
world's population had been scarred by the
event. Tyler's parents had fled, with many
others, to the safety of the deep forest.
The forest was no safe haven, though, and
many who had escaped the wrath of the
civilized world fell prey to the natural world.

The cabin in which Tyler was raised had
been built mostly by her parents hands, 
and with very few
power tools. The family had survived with
just two solar panels for years, which prevented
them from readopting conveniences of the
past, such as heat and electric appliances.
Later, they expanded their array to fourteen,
and quality of life increased significantly.

Neither Tyler's mother nor her mother's
girlfriend had any formal education, which
was common for their generation. Despite
this, they were both accomplished
teachers. The disruption of education during The
Destruction had driven large groups to seek
out online education. Although Broadcast
was not available during The Destruction,
educational data was transported along a
variety of trade routes. 
Both Tyler's parents, but her mother especially,
had an aptitude for mathematics, and they
had worked together, developing educational
courses in a large variety of subjects which
were ushered to the Webwork through the
traveling data centers.

Tyler's childhood had been full of education in
math, physics, engineering, survival, construction,
networking, webworking, and a variety of other
topics. This was the family business. The cabin
rarely had visitors, and the family rarely went to
visit others. To compensate, Tyler came up with
a variety of imaginary friends to play with.

As Tyler grew, the world began growing back
with her. The period of The Destruction was 
declared to be over, and many people seemed
to expect a return to the famed height of civilization.
Unfortunately, the wounds of the past half
century ran deep, and the world was slow to
recover. Micro wars were rampant as local
governments attempted to regain control of
valuable real estate.

When Broadcast was declared by the Union
government, it provided everyone with some
certainty and gave predictability to the spread
of information across the Webwork. Originally,
Tyler's parents praised the Broadcast, but when
it was learned it would cover only a short distance
from major cities, they withdrew their favor
of the program.

Even living far outside of Broadcast range, 
the new program greatly increased her parents
ability to teach. They were able to make
welcome additions to the cabin. In contrast
with the rest of the world, Tyler lived a luxurious
life in their cabin in the woods.

In the midst of her teenage years, Tyler was
sent into Camp for a one year program put
together by the locals to teach leadership to
youth in the area. Camp was the closest
established settlement and claimed a
modest population of around two hundred.

Tyler protested (probably the result of a mixture
of fear and hormones), but found herself in a
makeshift classroom a few months later, with
eleven of her peers, learning public speaking,
military tactics, self-defense, and a spattering
of other topics that the, mostly uneducated,
community had been able to gather together.
She was already more educated than most of
the adults living at Camp, and was insulted her
parents had sent her here. She would later
realize, as an adult, that she had been sent to
Camp to figure out that fluttery feeling she had
gotten in her stomach when she had first talked
to Jeremy; and the appropriate way to respond
to Amber's fist colliding with her nose after
holding Jeremy's hand during lunch. These were
the tools she would never learn to use living
in the cabin.

She returned home from Camp and life resumed,
but the following year Tyler's parents announced
they were taking a six month trip to the city. Tyler
could not accompany them; someone needed
to watch the cabin. This was the first in what
became an endless series of trips to the city for
her parents, which would keep them away from
the cabin three months of every year, usually in the
summer. Tyler was always stuck guarding the cabin.

\chapter{Chapter}
She had been nearly asleep when the noise of
someone entering the barn suddenly focused her
sense of hearing. It certainly wasn't alarming for 
someone to enter a barn during daylight on a
working farm; Tyler's ears were simply doing the
job evolution intended for them. They were
ignoring reason and identifying the sound.
The person walked across the ground level
of the barn and stopped. She guessed they would
be at the base of the ladder and, soon, her
solitude would end. The person climbed the ladder.
She trained her gaze on the hole in the floor
she was resting on, through which her visitor
would soon be poking their head.

The head which appeared was William's.

"I thought you might be up here," he spoke with a
smile. He climbed the remaining rungs of the ladder
until he was fully in the hay loft. Tyler nodded slowly
with a relaxed smile.

In many ways, William was her boyfriend. But that
term seemed a little odd, for the gray haired man
in his forties. Indeed, Tyler did not pretend that he
didn't resemble a father more than a partner. Aside
from the age difference, calling him her boyfriend
did not fit for other reasons. They were casual
partners and had only recently begun spending
a majority of their nights together. Despite their attempt
a distance, it seemed that the farm recognized them
as a couple.

"You never came by last night." The way he said was
matter of fact, as if it was just an observation.

"Yeah. I needed my own space."

"Do you still need space? I can go..." he started, but
she shook her head.

One of the qualities she appreciated about William
was his selfless, giving nature. The man seemed to
always think of others, especially Tyler. He walked
over and sat on the floor of the loft, leaning back
against a bail of hay.

Feeling a need to be closer to him, Tyler half crawled
and half scooted across the wood floor to where he
was sitting. Here, she nestled herself under his arm 
as he lifted it and placed it around her. As they
sat side by side, the memories floating around in her
head seemed to clear. She felt much more grounded.

"I feel unsettled," she admitted to him. "I didn't sync
Karin's Page. And the whole thing with the police
today was odd. I wonder what's going on."

William had been working in the garden today with
Karin and had certainly heard about the mishap and 
Broadcast Camp. And, the whole farm knew about the
visit from U.P.

He tried thinking about how best to reassure her.
"Kid, sometimes things happen and we don't really
understand why. Things like this have a tendency to
be meaningless in the long run." He looked down at
her, realizing he was receiving a dirty look.

"You did it again," she said.

"What?" he responded. Tyler sat up, looking offended.

"You called me 'Kid'! You know I find it creepy and
weird. I hate it!" She hit him forcefully in the shoulder.

Tyler's romance with William had been unexpected,
and there had been no spark when they first
met. In the end, it had been the way he was always
around for her and had never pressured the progression
of the relationship that won her over. She had taken
their friendship to the next level without warning one
night; a move which had surprised them both. At times
like this, however, with their eighteen year age difference
in the spotlight, she felt a little naive and silly.

The man with gray hair and tanned, weathered skin
knew this was not a defendable position. He prepared
for his exit.

"I'm sorry," he said. "You know it's just a bad habit I've been
trying to squash." He got up and headed back toward
the ladder. "Why don't we go have some dinner. It's almost
time." He stopped, offering her help up. Although she was
still wondering why she wasn't with a boy her own age,
she reached up and took his hand. But, his twisted pet
name for her didn't change their relationship if it wasn't 
spoken. She stood with him and then wrapped her arms
around him.

"Dinner looked good tonight," she said. "Let's go."

\chapter{Visitor}
A few miles away from the farm, a small camp had been
built. Although the sun had long since vanished behind the horizon
and the last shades of violet where fading from the sky,
no fire would be built at this camp. This morning had been
too close.

The camp was minimal, even more minimal than simply
having no fire. In fact, it served as little more than a
place to unroll a sleeping bag. It would rain tonight.
In preparation, a thin, nylon sheet had been fashioned
into a leanto shaped structure, but held in place by light
string. The sleeping bag was laid out under the
temporary nylon roof. It was strategically placed next to
the presumed driest location, although this hadn't been
tested. A backpack had also been placed out of the
direct line of tonight's rain.

The lone resident of the camp stood, facing no direction
in particular and looking only forward. With the rain
moving in, they wore a waterproof poncho over a heavy
jacket. Behind this standing point, set up in the middle
of camp, a device had been erected at the top of a
metal pole, which had raised it to a height of almost ten
feet off the forest floor. In the silence of the night, when
the wind was still, the mechanical noise caused by
the devices rotation
could be faintly heard.

Moving to the shelter, the person removed a Page from
their jacket. They flipped through a variety of displays
which informed them the device on the pole was working
correctly. A visit from the Union Police tonight would
greatly alter the plan and must be avoided. But, we the
sheer number of false signal scattered through the woods,
it would unlikely the U.P.s would even be hunting tonight.
Besides, even if they did wonder nearby, the device on that
pole had not been cheap and was capable of sending them
unfairly off course. No, the camp would be under safe
watch tonight.

The figure who was now sitting in the shelter put the Page
back into the jackets pocket. Tomorrow would be
a trying day and now it was time to sleep. Staying up
late and waking up with the Union Police surrounding
the camp would be unacceptable.

\chapter{Union Police Camp}
Having hiked all through the night last night, wasting
much of the morning out at the cave, and then
establishing a reconnaissance camp in the early afternoon;
Bishop had fallen asleep shortly after laying down in the
large tent. Many of his team had followed his lead.

Now it was night again and Bishop couldn't sleep.
He was sitting in front of
a large bonfire built by the other U.P.s, attempting
to formulate a plan for the coming day.

Capturing escaped fugitives was normally a textbook
process: retrieve prior locations, prioritize, and
canvas, all the while scanning for the fugitives 
body identification signature. Bishop was an
excellent officer and was disappointed his current
efforts were not reflecting it.

Every step had been a failure. Last night, there was
no sign of the fugitive whatsoever. Bishop was ready
to call off the search. The interview at the farm had
potential, but was called off to go on a wild goose 
chase through a cave. Shortly after, the forest lit up
with positive body identification signatures from every
direction, rendering the scanner useless.
Sitting in camp was an undeserved reward for thirty
six hours of failure.

He knew his target was out there somewhere. Finding
them was only a matter of getting in their head. He
fell back to a piece of his training he often used. 
In his head, he would ask questions 
of the fugitive and let his subconscious come
up with the answers. It was an unusual technique,
but he had a knack for it and would turn to it
during down time. He started simple:

"After escaping," Bishop asked his subconscious, 
"why did you travel southeast
from the city?"

"I was searching for something," responded the
fugitive.

"What are you searching for?"

"Something worth risking my life for."

Bishop felt like he was already making progress,
and continued the exercise.

"How long will it take to find the thing you are
searching for?"

"I expect to find it soon."

"What will you do after finding it?"

"I will try to disappear. Or possibly return to
the city." But the voice was unsure.

"Where are you now?" asked Bishop.

"Nearby."

"Are you at the farm?"

A pause.

"I don't know," said the fugitive.
Bishop tried to think more generally.

"Do the people at the farm know you?"

"They might know me."

Bishop went another direction, asking, 
"Does the cave have anything to do with
all this?"

"I don't think so," the voice replied.

"So, I should be looking around the farm,"
stated Bishop.

"That is probably a good idea," said the
voice of the fugitive.

The soldier shut off the dialog in his head
and looked up through the tree at the overcast sky.
He wasn't entirely sure he had learned anything
useful, but his intuition was telling him to
return to the farm. Considering he had no leads
at the moment, this unsupported decision
seemed to be as worthy as any other.

His mind settled, at least temporarily, 
the possibility of sleeping was probably
improved. He would sit here a while
longer, he decided, and let the fire die
down. Then he would return to the tent
with the rest of the soldiers.

\chapter{Discovery}
Although she had been quiet and moved
slowly, William had awoken the moment she
got out of bed. As she dressed in the dim
light, he sat up, propping a pillow behind
his back and yawning.

Tyler was cleaning the barn this early morning.
William worked the garden and typically got
a later start. He always woke with her on
barn days, though, and would often read or
catch up on news after she headed out.

Considering most of the community considered
her and William a couple, they would rarely be
seen together during the day. Perhaps it was
Tyler's way of keeping the relationship casual.
It was an unspoken rule that she would head
to her chores in the morning and he would see
her again that evening.

William would probably have wanted a more
serious relationship, if not for her age. He seemed
to recognize her obvious inability to commit
to someone at this point, and had never
challenged her for anything more serious.
Maybe he knew that any pressure on her
would jeopardize their current relationship, or 
maybe her was just putting her best interest
first. It was these kind of traits, whatever
their motives, that had kept Tyler returning to
William day after day.

Fully dressed and ready for what was likely
a frosty morning, Tyler crossed the room and
kissed William gently. 

"Stay warm," was all William provided her as
a farewell. It was enough. She said goodbye
and left the room.

Out in the common area of the barracks,
some of the older residents were already up;
drinking coffee, chatting, and reading up on
current events. One man played solitaire near
one of the barracks only windows.

In the courtyard between the barracks, a small
group was performing their morning Tai Chi.
The Tai Chi group had been a relaxation fad 
amongst the farm's residents a
few months back, but now, only the highly
devoted group of three remained.

The frost Tyler had expected was absent, a sure
sign that the Spring was arriving, but the air
was still cold as she walked to the barn. The farm
kept three horses, which were used mostly in the
field. Cleaning the barn every morning was Tyler's 
first assignment after she moved in, and she had
been doing it ever since. If the Broadcast mishap
of a few days ago caused her to lose that
responsibility, she might be cleaning the barn
for a long time to come.

She arrived at the barn and jumped right into
her chores. The trio of horses began pawing the
ground when she entered the barn. They were
always excited after a long night in their stalls.
She turned the horses out into the field.

The older horse, Charlie, always walked out slowly
and always led the way for the other two. Once
out of the barn, however, the two younger horses
would pushed past him and begin galloping, one
chasing the other, in a circle. This would continue
for and undetermined length of time and would 
then stop suddenly as if they had been given a
silent command. Tyler liked watching this ritual.

She turned back to the work awaiting her inside
the barn. She emptied, cleaned, and filled the
water troughs. She cleaned out the stalls and 
filled in the hole Charlie liked to dig out everyday.
She refilled their hay bins. She swept the aisle down
the middle of the barn. As a final measure, she
inspected the barn, both the ground floor and
the hay loft, for anything unusual. In the past
she had found misplaced clothing, 
rat nests, water damage, trespassers, and a host
of other situations better identified sooner, rather
than later.

The sun had now fully risen behind the overcast
morning. Breakfast would be served soon and work
would begin in the fields.

\chapter{Discovery}
Bishop liked it when his hunches turned out to be
true and this one had been extremely accurate.

He had woken his team up early with new orders.
They were returning to the farm where they would
spend the morning doing reconnaissance. Based
on his thoughts the previous night, and having no
other leads to go on, he was betting the fugitive
would show up. After all, a large effort had been
placed in spoofing the body signature identification
of the fugitive, and that meant they were likely still in
the area.

His team approached the farm from the east. He was
hopeful to find the BSIs in this area, too. For all he
knew, the false BSIs extended in every direction for
miles, but he took comfort knowing that someone
did not want him snooping around in this area.

He divided the team in two, emphasizing slow movement
and detection avoidance. If the fugitive was in the
area, his team could not be spotted first, and he
knew from experience that a team of this size was
difficult to disguise in the forest.

He reminded the troops that every Body Signature
Identification could be the fugitive and each needed
to be treated as such. With that final instruction, he
sent one team around the south side of the farm and
took his own half around the north.

The southern team had spotted the fugitive
within an hour and his best shooter now had a rifle
trained on them. The fugitive had not spotted the team
and seemed to be observing the farm from a tree line.

Bishop and his half of the troops were trying to cover
ground to reunite with the others. There was no way
to tell how much time would pass before the fugitive
moved. He left orders with the other team to pursue
at a distance should the fugitive move and only shoot
if spotted. He trusted his soldiers to make to right
decision.

Bishop's half of the team, there were eight of them,
had come out of the woods and onto a dirt road, which
was helping them close ground between the other team. 
They were five to ten minutes away.

The visual report of the fugitive indicated a female,
approximately late fifties, large build, blond hair. She
was wearing a green, hooded raincoat. The body
signature identification was a perfect match.

An update message came in from the other team.

"Fugitive moving. Maintaining visual contact,"
it read. They
had muted all audio communication to avoid
detection.

"Report direction," he replied, and a few moments later
came the response.

"North. Heading towards barn."

Bishop read this with mixed feelings. They needed to
act quickly. If the woman had friends at the farm, the
situation could get complicated.

As he thought this, the blast of a rifle rang out from up
ahead. A moment later he heard voices in his earpiece,
which had activated automatically in response to the 
gunshot. With the team's voice communication up, his
shooter confirmed his action.

"Fugitive has been shot!" said the voice.

Bishop started running. The soldiers at his side, having
also heard the message, kept pace with him. As he ran,
he sent commands to the team.

"Cease fire. Pursue fugitive. Watch for hostile action
from land owners." He paused a moment and then 
added, "And be careful."

This situation was... not ideal. His team had shot a fugitive
on a property owner's land. They had shot someone who
may be associated with the land owner; who may be 
friends with the landowner. His soldiers were well
equipped to handle whatever the farmers could throw 
at them, but the fallout from an incident out here could be
difficult to explain, even if it occured during the
apprehension of this criminal.
No one appreciated the Union Police flexing their 
considerable strength at the cost of hard working
farmers.

\chapter{Farm Reaction}
Jondra was sitting with 
everyone at breakfast when they heard the shot.
Although they didn't know, at this point, that
it had been a shot, murmurs immediately began ciculating.
Jondra leaned towards her brother, Jamar, who was
sitting next to her.

"You better check that out," Jondra said with concern.

Jamar was the unoffical leader of security at
the farm. He had an obvious interest in protecting
the family land and also was a weapons enthusiast.
He had inherited the responsibility and the desire
from his father, along with a modest weapons
collection. Together with the coorporation of
a few trusted residents,
the small security team worked to keep the
residents safe.

"Yeah," Jamal said to his sister, already standing up.
Then to the people murmuring, he said, "Everyone.
Attention, please. I'm going to go investigate that
sound." Some people were up and shuffling
around. Others were already up and heading
outside. His voice was being drowned out in other
conversations.

"STOP!" he yelled toward the sliding door leading
to the back porch. The room went silent and everyone
looked to him. He made his way to the sliding
door and stood in the opening.

"Wait here," he said to the crowd. He went out back
where the people not eating were already heading
out towards the barn. That must be the source of the
sound.

He started jogging, following the trail of 
others heading to the
barn. He saw a man named Mark already out by the
barn. He turned back to the people following.

"Someone's been shot!" he called out. He turned 
and ran around the side of the barn out of view,
presumably to lend assistance. Jamal drew his gun,
triggering a barrage of alarms on the resident's
Pages. An alarm bell on the farmhouse began
ringing.

After a few moments, Jamal rounded the corner 
of the barn. Looking out into the field, he saw the
cause of the commotion. Ahead of him, but quickly
moving towards him, a few residents were assisting
a woman he had never seen. She was covered in
blood below the waist. She was still conscious,
but was most certainly in shock.

The group asked him to help, but Jamal ignored
their request and waved them past him. His
paranoid brain had reminded him that an
unidentified shooter was nearby. He began scanning
the field behind the barn.

Immediately, he saw the Union Police pouring out of
the tree line. Several officers; all armed. Jamal had
little respect for the Union Police, who only patrolled
these parts when it involved their business and
could never be counted on to make the trip out here
for local crimes. He was certain these officers
were the same who visited the farm yesterday and
they were in pursuit of the unknown bloodied woman
he had just passed. Now they were on his
property and he needed to defuse this situation
before anyone else was injured. The soldiers had
already noticed him, and his gun. He saw them
walking swiftly towards him; assault rifles trained
on him.

Jamal raised his hands in the air, dangling the gun
by two fingers. He made an exaggerated act of
placing his gun back in its holster. This seemed to
settle the aggressors somewhat and they lowered
their weapons.

Jamal noticed at the tree line from where the 
first soldiers had emerged, another group was 
now following them. He was feeling very
uneasy about the whole situation and wanted
to slow things down.

He called out ahead to the soldiers, "I am the land owner
for this farm. I do not wish any further injury today
on my property." The soldiers slowed as the 
approached him. He was addressed by a female U.P.

"Where is the woman?" she asked.

"The residents helped her back to the house," Jamal 
replied. Some of the other residents had begun
to gather behind him.

"Tell your people we must apprehend the woman,"
the soldier said to him. "Abedding the woman
will not be tolerated."

The soldier assigned an officer to guard Jamal as
he sent the system wide message. He was
appreciative they didn't fight him about
removing his sidearm. They made their way
toward the farmhouse, where a group was
attending to the woman's injuries. The farm's
nurse had shown up and was getting ready to
move the woman to a propper table for treatment.

The female soldier, who appeared to be in charge,
pushed in for a closer look at the woman.
The injured woman was pale and nearly
unconscious. The nurse was trying to ask her
questions. The woman put a hand on the 
nurse's shoulder.

"We have a medic who will be here shortly,"
the soldier said to the nurse, "We will
take over treatment. Don't move her, please."
The nurse nodded as she eyed the assault
rifles. Down at the barn, the rest of the
Union Police were running up towards
the farmhouse. She returned to the patient.

Moments later, Bishop arrived on the scene,
with the rest of the Union Police with him.
He assessed the scene in front of him. He saw the group
of residents swarming around the fugitive.
The officer leading the other half of his unit
was standing with one of the land owners.
The people of the farm were everywhere. As a
soldier, he was feeling very unsettled with the
situation. He raised his rifle and fired one
round into the air.

\chapter{Tyler's View}
Tyler was in the farmhouse when the first shot
was heard. She was eating breakfast with Morgan
and Triss.

"What was that?" asked Tyler, as the rooms attention
was drawn to the sound.

"It sounded like a gunshot," said Morgan.

"Should we investigate?" asked Triss. Behind where
he was sitting, Jamal was already on his feet and
saying something.

Tyler spoke next. "I'm going to go..."

"STOP!" came a yell from Jamal. Tyler turned and
looked toward Jamal. His shout had been directed
at the back sliding door, where some people had
begun filing out into the backyard.

Everyone in the room stopped talking
and looked at Jamal. He obviously was
taking this really seriously, which both
alarmed and also calmed the people
eating breakfast. In a way, it was just nice
knowing that someone was going to look
into the situation.

Jamal walked from the table to the door.
He stood in the doorway a few moments
and then headed outside.

"It seems like we might want to stay here,"
said Triss. He seemed nervous. They were
all a little nervous.

"Yeah. Let's at least get a better look,"
suggested Tyler. She got up from table and
walked over to the window in the kitchen,
over the sink. A few other people had gathered
here and seemed to have the same idea as
her. Unsatisfied with the view she was provided,
Tyler abandoned the small kitchen window and
proceeded to the ajoining room - what might
at one point have been a formal dining room.

Morgan and Triss still sat together at the table.
The looked at each, other, each concerned.
With Tyler in the next room, the tension had
increased all the more. Both of them could
feel the additional level of tension in the air.

Triss broke the silence first, saying, "I'm going
to check on Tyler."

"I'm coming with," said Morgan. They stood together.
As they turned toward the room Tyler had
disappeared into, Gily came in through the
sliding glass door. He had a rifle in his hand,
which seemed to agitate many of the residents.
Still, Gily often helped Jamal keep the peace,
so most people simply looked to him for answers.
A small crowd gathered around him, asking
a hundred versions of the same question.

"Folks!" he said sharply, "I'm afraid I don't know
anything at the moment. I'm just here to check
on Morgan." He crossed through the sea of
people and made way to Morgan, who had
waited at the breakfast table for Gily to reach
her. She asked him the same question as
everyone else, somewhat hoping he had
saved the truth just for her ears.

"I don't know. He said. But I'm going to check.
I just wanted to make sure you were alright."
She appreciated the thought, which was
part of the reason she loved him so much.

"I'm fine. I'll wait her with Tyler and Triss,"
she said. He nodded, made his way back
through the crowd, and headed back outside.

Morgan went the opposite way into the other
room where Tyler and Triss were peering out
the window. It was at this point
that the farm alarm system activated. The
blaring alarm of the farmhouse started ringing
and the Pages belonging to the residents
started sounding with emergency messages.
The three of them read their messages in
silence, but together. It was a system message,
but clear and direct:

"Weapon drawn: Jamal Johnson"

This message removed the possibilty
of the event being an accident. Jamal drawing
his weapon meant something unusual
was happening out there.

From the view of the window,
they could see down the long driveway leading
towards the barn. The situation was all 
taking place and this stretch of road between
the farmhouse in the barn. People were mostly
traveling down to the barn. However, at the
end, almost all the way at the barn, a large
group seemed to be moving back up the road.
Tyler was not enjoying sitting inside through
all this.

"I'm going out," Tyler said. 
"They might need all of us." She was partially
aware that it was curiosity over concern which
was drawing her outside, but she lead the
way back into the common eating area.
They found it almost completely devoid of
residents and all but a couple had moved
outdoors. The followed suit and went through
they already open sliding door.

It seemed that almost the entire farm was
out in the backyard now. The community was
gathered a large semi-circle, all watching
towards the barn, and we that same trail of
people moving back and forth to the barn.

It seemed that the group spotted by the barn
just a minute ago had made significant 
progress towards the farmhouse, which
appeared to be their destination. Tyler
suspected by they way they were moving,
they were assisting someone up the road.

Behind this group and a little ways back to
the barn, Tyler identified the likely source
of all this mess... the Union Police. They
were hustling to catch up with group assisting
whoever it was that had been injured.

"Those U.P. bastards shot someone!" Morgan
said. She must have been the first to actually
say it, as it caused a cascade of murmurs to
travel around the group.

There was too large a group around the injured
person to see who it was, but everyone was
talking louder now. The farm nurse pushed
through and went to care for the person.

Tyler (Morgan and Triss probably, as well) did
a quick mental count of the people she knew.
It seemed like everyone she was close with 
was here except William. William would have
been in the Barracks since she hadn't seen him
at breakfast yet. It probably wasn't him.

The Union Police were now also part of the
group surrounding the person. Tyler
heard them say something about apprehending
a fugitive.

"Did he say a fugitive?" Tyler asked no one in
particular. 

"Yeah," replied one of the residents who had
been down by the barn. "The soldiers shot someone
in our field, not one of our people. Don't know
they story. They said she is a fugitive."

"That's amazing," said Morgan. "Probably some
lunatic sneaking here to murder us. Good thing
they were tracking her." As she spoke, another
group of Union Police arrived, including the
soldier who had been to the farm yesterday. This
didn't really surprise anyone, though, since they
were extremely unlikely to see any other U.P.s
for a long time.

That was when the shot rang out and everyone
fell silent. As they had been distracted with all the
events, the head of the Union Policy had fired
a single shot in the air and was now waiting for
everyone's focus to be on him. It did not take
long.

"Thank you," he said to the group. "First, I need
everyone here to please move into one group in
front of me." He indicated an area in front of him,
behind the injured woman, and in the general area
Tyler, Morgan, and Triss were standing. He
dispatched men to gather up the people down
by the barn. Apparently he didn't want anyone
hiding.

"Whoa, what is the meaning of this?" asked Jamal
of the soldier."

Bishop responded, "Look, I don't mean anyone
any harm. Please. Jamal, right? Let's wrap this
business up and we can all get back to what we
were doing before this unfortunate event." Jamal
looked back to the soldier coldly.

"We'll cooperate, but let's not scare anyone
more than we already have," said Jamal.

"That is a fair arrangement," agreed Bishop.
"Keep you people over there and we'll get this
fugitive off your property shortly."

Jamal nodded to the other men on his security
staff, indicating he intended to go along with
this. After all, he couldn't fight the Union Police.

"Now," Bishop continued, "We are taking this
woman into custody and will take over her
treatment from here." The group of residents,
including the farm nurse, the U.P. medic, and
several of the farm's volunteers all looked at
Bishop. He tried being more clear with his
message.

"You people," he started, pointing right at
the group assisting the woman. "We will no
longer require you assistance. Thank you for 
your Samaratanship. Please back away from
the fugitive and rejoin your group." The U.P.
medic assured the nurse with a nod. The
residents moved back from the injured woman.
Many of them were covered in her blood.

The woman seemed unconscious and the
ground around where she lay was covered in
her own blood.

As the space around the injured woman
began to clean, Tyler's heart rate suddenly
began racing. She took a few steps forward
and found she could no longer maintain
a regular breathing pattern.

"Mom?" she spoke quietly. Her entire body
was terrified. Feeling as if she was floating,
she took a few more steps towards the
unconscious woman. Morgan was now holding
her hand.

"What did you say?" Morgan asked Tyler.
No response. Tyler was moving again,
toward the person on the ground, the medic
and the Union Police.

"Mom!" she said louder. She suddenly pulled
her hand free of Morgan and began running
up to the scene. Several soldiers noted this
and quickly pointed rifles at her head. When
she didn't stop running, they backed off
slightly, but otherwise did not react.

Tyler collapsed at the body, startling the medic.

"Mom!" she shouted. Then she turned to the
medic. "What happened. Tell me please, what
happened."

The medic paused for a moment and looked at
here. A soldier came around to the side of the body
at which Tyler was knelt. He put an arm firmly
under her shoulder at the armpit an pulled her
to a standing position. Tyler barely seemed to
notice and begged the medic to answer her with
her eyes.

He spoke. "She has been shot in the leg. She
lost a lot of blood and passed out. I almost
have the bleeding stopped but we have to
transport her to a hospital immediately."
He went back to work. Tyler was a flurry
of emotions and couldn't think of a next step.
Bishop stepped around the body and looked
Tyler in the eyes.

"Do you know this woman?" he asked.

Tyler looked back, a dazed expression in her
eyes.

"She's my mother." Tyler stopped. Her head
was spinning. Bishop looked back at her for a
moment.

He asked another question. "Do you know why
she is here? Tell me the truth." He didn't know
if she would or not, but she was obviously
shook up over her mother. He wanted to take
advantage of her current mental state in hopes
it would avoid any deception.

"No. My mother died," Tyler said quietly. She
was pale and shaking. Bishop believed her,
but would need more information.

"Dear, you should sit down. You don't look
well," he said to her. Then, to the soldier
holding her up, "Take her to those steps. Let
her sit."

The soldier began walking her to the porch steps.
Triss ran up to meet them.

"What's going on?" asked Triss. Tyler was murmuring.
He changed his approach, "Here, come sit down."
He took her other arm, gently. Too gently. The
soldier let go just as Tyler slumped. She slipped
out of Triss's grasp and hit the ground. She was
unconscious.

\chapter{Waking Up}
When Tyler woke up, she was in her own bed.
She was alone. It didn't feel like morning, and
she didn't remember going to bed. What
happened last night? How long had she slept?
Did she need to be somewhere right now?

Slowly, events started coming together. There
was an accident. Her mother was there. She
was injured. Was that a dream? To Tyler, it
did feel like a dream. Her heart rate picked up
again as the events clicked back together in her
head. Her mother appeared in town, shot. The
Union Police shot her. She was unconscious.

Tyler felt lightheaded again and forced herself
to breath. She tried to focus on the events
to learn some details, but they would not solidify.
Every time she focused on an event her head
started swimming and topics would pop in and
out of her mind.

She forced herself to lay motionless in her bed.
She closed her eyes. The sensory deprivation
helped a little. She let her mind think of nothing.
Slowly, she tried to recreate the events. It had
been breakfast. Someone had been shot. They
had all been outside when she realized the
injured person was her mother. She had run
to her. Tyler assumed she must have passed out
around that time.

She was very confused. Both her parents died.
It had been well over a year ago. They were
travelling to the city for work again. One of their
annual trips. When they had failed to report
to work, there had been a brief investigation.
There bodies were found in a landslide not far
from their cabin. They had both died.

Tyler hadn't seen the bodies. The identification
must have been wrong. She couldn't lay here
anymore. If he mother was alive, then her
mother's girlfriend could be alive, as well. She
needed to get some answers. She sat up on 
the edge of her bed. As she waited to see if
her body would cooperate with the upward
position of her head, William entered the room.

"Hey," he said. "Glad to see you up. Now lay
back down.

"Where is my mother?" she asked him.

William sighed and was silent for a second.
He say next to her.

"Let's talk about that," he began, "Morgan told
me you thought the woman who was shot was
your mother?"

"Yes. It was her. It looked exactly like her. 
Where is she."

William answered quicker this time. As he did,
he signed a little.

"The Union Police took her. She needed to get
to a hospital. They left a while ago."

Tyler was so confused. She had no idea what to
say or do. She said as much.

"What do I do now. I thought she was dead, Will."
Tyler was on the verge of tears. Then, she was
suddenly in tears. They streamed down her face.
As she broke down, she wrapped her arms around
William.

"I don't know what to do," she said.

"We'll figure it out." he told her. He knew it wasn't
the best thing to say right now, but it was all he
had. He knew what she had heard about her
parents. A lot of people these days had stories
of death and he had never assumed hers to be
inaccurate.

He asked her a question, "Can you try to sleep a
little more? Or is that out of the question right
now.

All she wanted to do was sleep. Her head was
firing every which way, making it hard to
focus. She would love to turn it off for a while.
On the other hand, she had just learned that
her mother was not dead. No, her mother was
a fugitive of the Union, now in custody in a
prison hospital somewhere, possibly dying, and
Tyler could do nothing about it.

This led her to further questions. If her mother
was alive, why was she suddenly at the farm?
Was she trying to contact Tyler? Was her mother
trying to warn her about something?

She cut her rambling thoughts short again,
feeling that she was generating too many
questions and not enough answers. Maybe 
resting was in order.

"Will," she said as she slowed her crying and
pulled her face off his chest, which was now
damp with her tears, "wake me up at..."

She realized she had no idea what time it was.
Instead of asking, she rephrased the request.

"Wake me up in two hours," she told him, "I
don't know if I'll sleep, but I need to try.
She felt a little better making a rational decision.
The decision felt like the right one.

William got up to leave. He looked like he might
say something, but Tyler buried her face into her
pillow, trying to block her sight, sound, and hearing
at the same time. The wild thoughts in her
head seemed to protest, be did calm somewhat.
William left without speaking.

As he shut the door, Tyler found another round
of tears spilling out of her, but refused to focus
on the new found questions. She was smart
enough to realize that her mental state was not
ready to deal with any of this rationally. Hopefully
in a few hours.

Her entire body seemed to be agreeing with the
idea of sleep. Her tears subsided again and her
mind slowed it's racing. She closed her eyes 
tight and awaited unconsciousness.

\chapter{Realization}
Tyler woke with a start. She was not sure what
the dreams had been about, but she knew they
were horrifying.

William was sitting by her on the bed, his hand
resting on the small of her back. He was gently
rocking her back and forth. She had probably
been moving quite a bit in her sleep.

Her mind had cleared a little. The rest had helped.
She was still constantly thinking about
what she had seen just a few hours before, but
she was thinking with a little more clarity.

Her mother had been here. The thought was
increadible. Why? Where had Tyler's life
gotten so far from reality. Here she was, living
alone on a farm, thinking both her parents
were dead and yet, they weren't. At least,
her mother wasn't. This made her think
of her mothers girlfriend; Tyler's other
mother. Was she alive, too? There was no
way to know.

William was still sitting with her but had not
anything yet. Now she looked up at him. His
calm face was smiling at her.

"What is going on?" she asked him, not expecting
an answer.

"I don't know," he answered. At least he was
being honest. Tyler rolled over onto her back.
She laid a moment and then sat up. Her
room looked strange in light of all the new
information in her head.

"What should I do?" she asked. It was a 
good question. Should life continue as normal?
There was no sure way of finding her
mother at this point. She could be anywhere.

"I don't know if you're ready for this,"
William said, "but there is a soldier here.
He's waiting for you." Tyler turned her
head at his. It was a surprise. It kind of
made sense, though. Obviously, they
would want to talk with the person 
discovered to be related to the fugitive
they were tracking.

Tyler sighed, "What am I supposed to
say to him? I don't know anything and
he's probably not going to believe me if
I tell him the truth."

William thought about this for a moment
and said, "I don't know. Start with the
truth and see how it goes. It can't be that
bad." It was good advice, but Tyler wasn't
sure if it was right for this situation. She
decided the best plan was probably just
to get it over with as soon as possible.

"Where is he?" she asked William.

"She... is still in the farmhouse. She wanted
you to know there was know rush."

Tyler was quiet a moment. "Okay," she
started, "I'll get cleaned up and head over
there. Thank you for everything."

She stood up and walked to William. She
gave him a long hug. Then she left the
room, heading for the bathroom.

Once in the bathroom 
she washed her face in the sink, still
feeling like her head was swimming. It
was kind of like being drunk but without
the fun side effects.

After finishing in the bathroom she headed
over to the farmhouse. The walk was slow
and steady. She was very aware of the looks
she received from her farmmates, but was
hardly caring. This was a slow deliberate walk.

Arriving at the back door of the farmhouse,
she say the soldier sitting inside through 
the window. The soldier's distinctive black
uniform looked out of place with the soldier
sitting casually in a chair drinking tea with
Jondra. Somehow, this site made the whole
situation more nerve racking. Maybe Tyler
was thrown off by the friendliness.

Determined to get this over with, she
opened the door and went inside. Jondra
and the soldier both turned their gaze
to the door as Tyler came in. Jondra
spoke first.

"Hi, Tyler. How are you feeling?"

Tyler walked a little ways toward the
table at which the two women were
sitting.

"It's a lot to take," responded Tyler. The
soldier sat quietly.

Jondra continued, "I guess you heard
from William. This soldier needs to talk
to you. Tyler, this is Jane."

Jane took the opportunity to jump in.
"Hi, Tyler. I know this is a tough time,
but I need to ask you some questions."

"Sure," said Tyler calmly.

"I'll leave you two to talk," said Jondra,
"Tyler, come
get me if you need to." She left the room,
leaving Tyler alone with Jane the soldier.

Tyler sat down in the seat previously
occupied by Jondra. Jane's friendly smile
had gotten more serious, and she was 
sitting more upright. She took her Page
out of her uniform pocket and set it
down on the table between them. Jane
looked carefully at Tyler for a moment.

"I'm going to talk first," said the solder.
"I'm going to tell you as much as I can
about our business here and about the
fugitive we were chasing. Then I'll need
to ask you some questions."

"That's fine," said Tyler, "But can I ask
one question first?"

"Sure," said Jane.

"Was the woman from this morning really
my mother?"

The soldier looked at her and said with a serious
face, "Yes, she was."

/chapter{Aftermath}
Bishop and his team had called for a helicopter.
It was a costly move to make, but the distance
and the condition of the fugitive made a trip
by land too large of a risk. The had rendezvoused
with the helicopter a mile down the road from the
farm. Here, Bishop, the medic, the fugitive, and
one other soldier had boarded the helicopter
to head back to the city. The rest of the team
would be traveling back on foot.

The whole incident had been a mess, but at
least the luck had been good during what
could have been a very violent encounter with
the locals. The fugitive was in custody, and,
thanks to the helicopter, would most likely
survive.

The trip to the city seemed increadibly fast to
a soldier who had spent the previous week
walking on foot out to the farm. Bishop had
been in helicopter's before during the war,
but this was his first trip simply for transportation.

As they traveled the change in scenery was
very obvious. The landscape around the
farm was mountainous and forested. The
settlements were scattered. Very few people
be seen on the ground. By contrast, the area
closer to the city was still very dense.

As they neared the city, the skyline rose up
in front of them. Bishop loved seeing his city.

Many of the larger buildings were no longer
in use; deemed unsafe by the city engineers.
The worst offenders had been leveled, and
experts were predicting few building from
before the Destruction would be standing
fifty years from now. For now, Bishop
appreciated the amazing engineering from the past.

The Hospital was a few miles from the largest
buildings of the city. It had been constructed
near the cities largest power array, which,
combined with an expensive battery system,
provided the hospital with continuous power, 
a luxury in this day in age.

Having uninturrupted power made the hospital
an amazing place to visit. Some of the most
advanced technologies in the world existed in
hospitals.

When the helicopter landed, it was met by
hospital staff. Bishop's medic quickly jumped
out of the helicopter to assist in the handoff
of his patient. He communicated to the doctors
the nature of the injuries, vital signs, and
informed them of the drugs and doses he
had already administered. He walked in with
the patient and the hospital staff. Bishop
ordered the other soldier who had accompanied
them to guard the fugitive until relief could
be sent. The soldier jogged off to catch up
with the procession of people wheeling the
fugitive into the hospital.

Bishop also exited the helicopter. The
exhorbinant price of the flight meant 
that Bishop was on his own from here.
Being back in the city, though, meant
that a number of transportation options
were now available to him.

Bishop's Page had come back alive since
reentering the cities wireless zone. His first
order of business was to check in with his
family. Removing the Page from his jacket,
he requested connection with his two boys
and his girlfriend. The Page informed him
they were not available at the moment,
but he quickly flipped through their events
from the past couple days.

He was on the street in front of the hospital.
A few vehicles moved back and forth on the
streets, but the area was relatively vacant.

\chapter{Back at the Farm}
Tyler was sitting with the soldier, Jane. Tyler
had heard about the U.P.'s reason for being
at the farm and she was more confused than
ever.

Jane had explained to Tyler that her mother
was a fugiitive of the Union, but had escaped
from prison. They had tracked her away from
the city and to the farm. Her mother had been
spotted at the edge of the farm. When she had
seen the Union Police, she had run into the field
behind the barn. One of the soldiers had wounded
her to prevent her escape. This is when she had
been helped by the farmers and had encountered
Tyler. Jane knew Tyler's mother was being taken
back to a hospital at the city by helicopter but did
not know her present condition.

Now, Tyler and Jane sat across from each other
and Jane asked her a question.

"Did you know your mother was alive?"

"No. I had no idea she was alive," said Tyler.

"Why did you think your mother was dead?"

Tyler told what she had been told of her
mother's death. A year ago, Tyler and her
parents had been together at the cabin.
Her parents had been preparing to travel to the
city for work. Tyler, as usual, would stay at the
cabin for the three months they would be
gone. Her parents had left as scheduled and
Tyler had stayed behind.

A few days after her parents had left, Tyler
had received a visit from a neighbor from 
one of the farmers on the road to town. He
had come with grave news. He told Tyler he had
found her parents dead on the road, after having 
been victims of a landslide. They had been buried
under a slide of trees and dirt.

Tyler had not seen the bodies, though, as she
had been too far away and they had already been
creamated by the time she had arrived at the
closest village.

"Do you know anything about what happened to
your mother's girlfriend?" asked Jane.

"No. I assumed she died with my mother."

"Why was your mother trying to find you?" asked
the officer.

Tyler had been thinking about this and couldn't even
figure out how her mother would know she had been
at this farm.

"I don't know," said Tyler.

"Does your mother know anyone else in the area."

"I don't know."

"Have you ever been to the city?"

"No."

The soldier stopped for a moment, gathering her
thoughts. Tyler felt that she was frustrating Jane
a little with the lack of information, but she didn't
get the feeling that Jane suspected she was
lying.

"Tyler, can you think of anything we should know
about your mother that might make her want
to escape and return to this area?"

That really was the question. Both Jane, Tyler,
and probably a lot of other people, all wanted 
to figure out what Tyler's mother might be doing
out at a farm in the foothills of these
mountains.

"I'm sorry," Tyler started, "A year ago, I thought
my parents were just teachers. Then, I thought
they were dead. Now, I find out my mother is 
a fugitive. I think I'm the wrong person to ask
about why she might be out here."

It was a fair point. Right now, Tyler felt like the
person who knew the absolute least about her
mother. It made the whole process even more
difficult.

"Alright," said Jane, sounding like she was
wrapping up the interrogation, "That is all
I have." She picked up her Page. "I'm sending
you my contact information."

Tyler took out her own Page and verified 
she had it.

"Please contact me if you think of any
other information I might need," finished
Jane. "Otherwise, you probably won't
hear from me. Your mother has committed
no additional crimes and will be returned
to prison."

"Can I come see her?" asked Tyler.

"Your mother is in the city prison,"
said Jane, "but you are welcome to
visit her." She got up to leave. "Thank
you for your cooporation. She left out
the front door of the farmhouse. Tyler
sat in the chair in silence.

\chapter{Meeting}
Morgan and Tyler were sitting at a table
in the common area of Tyler's barracks.

"Are you going to go to the city?" asked
Morgan.

"There is so much I don't know right now,"
replied Tyler. "I want to, but I don't even
know where to start."

Tyler was having the hardest time making
decisions right now.

"I think I should find out what really
happened to Coral," said Tyler. Coral
was her mother's girlfriend, and right now
might be her best chance at learning more
about what happened.

Morgan thought about it. "Who was the
person who originally told you about her
death? Do you think you could find them?"

Tyler thought about that. It wasn't a bad
idea. Merl had been the farmer who had
shown up that day with news of her
parents death. Could he have been lying or
was he simply incorrect?

Tyler knew inside that she would not be
able to return to life as usual on the farm.
There were too many unanswered questions.
It was at this moment she told herself
that she would be leaving the farm.

"I think I have to leave the farm," she told
Morgan in a slightly surprised voice. "You're
right, I need to find Merl... the man who 
found my parents dead in the landslide."

"Oh my god!" said Morgan, "I can't believe
you're actually going to leave. Where does
the farmer live."

Merl wasn't that far from the farm. It would
be a few days journey, back into the mountains,
but she knew the way.

"He isn't far. And I have to do this," Tyler told 
her friend.

\chapter{Planning to Leave}
Arranging for her trip was not difficult. Tyler
had arrived at the farm with few possessions
and had not acquired much during her time 
there. She packed a few clothes and a weeks
worth of food. These things filled the bulk
of her pack. In addition, she took the cables
for her Page and the small supply of spare
parts she had acquired over the years. She
also packed her survival supplies; a variety
of things used to trap game in the wild and
prepare shelters.

As she was wrapping up here packing, there
was a knock on the door. She opened it, and
Triss came in.

"I want to come with you," he said immediately.

Tyler looked at him with mild exasperation. "No,
Triss, you can't come with me."

"Why not?" he replied. "We can cover more
ground together. And we'll be safer."

"Do you even know where I'm going?" she asked.

He paused. Then said, "No. I assumed you were
going to find your mother."

"No. I'm not. I'm going northeast, higher into the
foothills. There is another farm up there. I promise
you, this trip is not going to be any fun."

Triss was silent for a while. He just stood thinking.
Tyler was the first to say something.

"Look. I would really like to have you along. You
can come if you want." She smiled a little as she
saw his face light up. She was happy that he wanted
to join her. It would be nice to have someone on
the trail with her.

She started giving Triss some instructions. "You need
a weeks supply of food and some clothes. Bring anything
else you want, but don't overpack. The lighter you
can be, the better." She paused and then added, "If
you can't keep up, I'm sending you back here." She 
told him to meet her by the farmhouse at ten o'clock
that evening and sent him off to pack.

\chapter{Departure}
It was already nine thirty when she and William finally
wore each other out. Now that they had finished their
sexual goodbyes, they were cuddled together,
saying their regular goodbyes.

"Please be careful," William started, wrapping
his arms around Tyler and holding her close
to him. "I know you are used to being away
from community, but it can still be dangerous."

Tyler's natural reaction was to reject warnings
such as these. In fact, it bothered her when
people acted so concerned about her safety.
Maybe she was a little naive, but she had a 
good head and tended to make rational
decisions. Despite this reaction, the way
William said it made her feel more comfortable
about it.

"Ah, this will be a short trip. Don't worry about
a thing."

"So, you're coming back after meeting up with
this farmer you know?"

"Well," said Tyler, "if he has information about
my parents, I will probably want to follow up
on it, but even if I take another trip, I'll
probably come by the farm first."

William ran his hand through her hair. He
had grow attached to her, although he wasn't
about to tell her that.

 "I hope you find what you're looking for," he
said.

"So do I."

/chapter{Still}
It was already almost ten fifteen when Tyler
showed up at the farmhouse. It was raining.
Triss was sitting up under the porch with a
backpack sitting beside him. Judging by the
bulk of the pack, she felt he had done a good
job following her instructions.

Morgan was sitting beside Triss. They weren't
talking, just watching her walk towards them.

"Are you really leaving in all this rain?" Morgan
asked Tyler as she approached. "You could wait
for morning."

Tyler looked out into the dark and then said to
Morgan, "Yeah, but maybe it'll be worse in the
morning. If I wait for the weather, I might be
sitting here until summer."

Without taking off her backpack, she gave
Morgan a hug. She could sense that Morgan
was more worried than she let on. Tyler
tried to reassure her.

"Traveling at night is the best way to go this
time of year," Tyler said. "We'll be on the road
most of the time. Everything will be fine."

Morgan responded, "Message me when you can."

"I will," promised Tyler, "but I doubt I'll be going
to Broadcast on this trip. You might have to wait
for me to get back."

She turned to Triss, who was standing with them
now.

"Are you ready?" she asked.

"Yep."

He sounded both unsure and excited at the
same time. He gave Morgan a hug and put on his
own pack. They put up the hoods on their 
rain jackets and pulled the ties tight in an
attempt to keep as dry as possible. After the
final goodbyes, Tyler and Triss walk off the
porch of the farmhouse and into the night.

Morgan stood on the porch for a while after
they disappeared into the dark.

The beginning of the trip was quiet. The two
were using their freshness to cover a lot of 
ground. The walking was quiet and determined.

Tyler preferred walking at night, especially when
the weather was bad. She wouldn't have wanted
to travel through the forests at night, but walking
on the road was ideal in the dark. Also, by
walking at night, when dawn came and it was 
time for some rest, the farmers of the area were
already out in the field and would usually provide
a place to sleep.

She guessed that the trip to Merl's would take
three or four days. She had the location saved
from long ago. He was north and to the east
of the farm. If they continued from Merl's another
couple day's they would reach Tyler's cabin in the
woods.

Triss had always been a frail boy. However, he
was used to work in the fields and seemed to
hold up to the stresses of manual labor despite
his weak stature. He had no trouble keeping up
with Tyler on the road.

Unfortunately, it rained most of the night,
making the travel colder and the roads
muddier. It was not uncommon in this area
to have several days of continuous rain this time
of year. Living here, you just got used to it.
Even wearing raincoats, their clothes were
completely wet within a couple hours of leaving
the farm. Thankfully, once they were walking
and the blood was moving, the were plenty
warm despite the wet weather.

They followed the road into the foothills. They
were traveling almost the opposite direction
Tyler took to get to Broadcast. They were headed
away from the the city, civilization, and Broadcast.

In places, it could be seen that the road they
were on had been paved at one point. There were
large chunks of concrete and asfault in the ditch
along the road, from where the surface had gotten
so bumpy someone had simple dug it out of the
road and chucked it to the side. Now, most of the
road was bare dirt.

Together, they made a lot of ground that first
night. With the rain, they didn't really look
forward to sitting, and instead seemed to just
want to finish the journey. When dawn came and
the sun began to peak over the horizon, Triss was
begin to wear down. Tyler could sense him wanting
to stop soon, but told him she wanted to put
in a couple more hours. Not, wanting to disappoint
her, he agreed.

By mid morning, though, they were keeping an
eye out for a place to rest. Throughout the night
they had passes farms and houses from time to
time. There were plenty of possible places to stay,
it was just a matter of finding someone friendly to
travelers. These days there were many travelers
on the road, but often, if a resident had a bad
experience with a traveler, it often left a bad taste
in the mouths of all the local residents. Tyler
was hoping for a little luck.

Thankfully, around noon they passed a farmer
who agreed to let them sleep in his barn. It was
probably they best deal they were likely to
encounter and they both accepted the offer.

Sitting in the barn, Triss and Tyler found they were both
tried and extremely wet. The continuous rain had soaked
them completely. Their shoes were soaked with no chance
of drying.

The stall they were allowed to camp in was dry, and would
keep them sheltered from the cold. However, they would
need to at least try to let their clothes dry.

Their backpacks were waterproof, and they quickly
changed into their dry clothes. The wet clothes were
laid out with their shoes and would hopefully be a lot
drier by the time they headed out again this evening.
Now dry, they were feeling sleepy.

"We covered a lot of ground last night," said Tyler. "I
would guess if we could keep up that pace, we might
make our goal in two more days."

The goal was ambitious, and it wasn't her intent to meet
it. They would both awaken with stiff legs and the going
would be slower. They made nests in piles of hay on
the floor of the stall and stretched out.

Tyler was glad to have Triss along. She hadn't expected
it, but it made the process easier and she got along
so well with him.

As she curled up to sleep, she knew immediately her feet
would be cold. Using an old trick, she wrapped them with
her backpack and tied the pack around her legs. It was
silly, but it worked.

She slept pretty well, throughout the day in the barn, even
when a group of people came in for some supplies. She
heard them moving about, and they made no effort to be
quiet, but she never fully woke up throughout the process.

Tyler woke up just as darkness fell. Triss was still sleeping
and it was still raining. She sat up in the hay and looked
around. Despite the fact that she just woke up, her
body told her it had been getting colder.

She unwrapped her feet from her pack and got up to
inspect their drying clothes. The clothes were pretty
dry, but their shoes were still wet. But, she had walked
in wet shoes a lot and it wasn't the worst thing.
Thankfully, they had plenty of food.

She decided not to wake Triss just yet. She would make
them some food. Rice was always a good food to pack
due to the density and nutrition. The only problem was
that it needed to be cooked. They couldn't have a fire -
the farmer had made sure to tell them, so rice was out.
Other than rice, they would be stuck with dried fruit, mostly
berries, nuts and other pack foods. So, it wasn't so much
making food, as it was laying food out. She did need to
get some water. She removed the large pot from her pack
and set off to find water.

She hadn't seen a pump on the way in, and they weren't
near a waterway, like a stream or river. She would need
to hunt around. The easiest way to find water on a farm,
she had learned, was to find the water troughs for the
animals. The pump was never far away.

A few people were still out and about on the farm this evening.
She received a few strange looks as she wandered around,
but no one seemed too concerned. People had a tendency
to size others up; it was just good sense.

Before too long she found the pump, not too far from a
group of cattle.She filled the pot and started back towards the
barn. Full pots of water are difficult to carry
without sloshing half the water out. You had
to move slow, and try to offset the movement
of the water as much as possible. It took two
or three times as long to get back, but it was
good to have something to drink. Both she and
Triss had emptied their water bottles before
resting that morning.

She filled her water bottle from the pot and
drank as much as she could. Even when you're
thirsty you can only drink so much. She refilled
it back to the top and set it aside. She started
laying out some of the food as Triss began
stirring.

Triss opened his eyes and looked at her. The
light in the barn had disappeared and Tyler
was using her Page to light the area. She had
charged it while they slept with a portable
solar charger. It glowed softly as set packages
of food on her jacket, which was laid out
as a placemat of sorts.

"Is it time to go already?" Triss said. His voice
sounded tired and Tyler guess that perhaps
he hadn't slept as well as she had.

"Yep. Get up. Have some water and food."

He sat up and stared into space. Tyler handed
him his waterbottle and he took it.

They ate together and Tyler looked at the map
of their route. She was pretty sure she knew
which farm they were at and, if she was correct,
they had not made the distance she had hoped.
But, she didn't think they'd make up that extra
day of travel anyway and it might be better to
take it slow.

Soon they were back on the road. They put some
ground between them and the farm. The miles
started ticking away.

Today, both of them were chattier, and they
conversed most of the day.Tyler found herself talking a lot about her
parents, and Triss was happy to listen. If anything,
Triss was a good listener. And although he
often wouldn't have much to share at the
end of listening, sometimes that was exactly what
a person needed.

The rain let up around midnight and they actually
walked by moonlight for while. Tyler almost
felt like her feet were drying out when the rain picked
back up. As dawn came, they again decided to
ask for shelter from one of the locals, but they had
a difficult time finding an appropriate place. They were
no longer in farm land, and the residents were few
and far between.

Many of the buildings they did pass were crumbling
and had long since been abandoned. Tyler decided
they would set up camp in one of these. They looked
for a structure that offerred protection from the rain
without the risk of having it crumble on them during
the day.

Camping out in an abandoned building during the
day came with risks. For one, there were not on 
owned property, and other travelers could show
up. And while most travelers were harmless, some
were extremely dangerous.

Triss spotted a building a ways off the road that
looked uninhabited. Tyler felt like checking it out
and they hiked off the road a ways to investigate.
The building wasn't great, but it had a solid roof.
The floor was wet, but they were able to pad it
with branches that had fallen in the area.

One of the biggest advantages of staying on there
own was being able to have a fire. The set about
gathering wood and soon had a warm fire to sit by.

That morning, they cooked up rice and dried their
clothes and shoes. They went to be well fed and
warm. The were not interupted by anyone during
the day.

\chapter{Merl's Farm}
Tyler and Triss reached their destination during
the fourth night, just as she had expected. The
trip had gone very smoothly; there were no
injuries, no strange encounters, and no wrong
turns. Both the travelers were tired. Not wanting
to turn up uninvited at the house of the person
they needed help from, they camped under a bridge
they crossed a mile or so prior.

"What are you going to say to Merl?" asked Triss,
as they sat by their small campfire.

"I don't know," said Tyler, "I guess I just want to
talk to him."

She was being honest with Triss, she had no idea
what she was going to say to him. The last time she
had seen Merl had been almost a year ago, when
he had arrived at her parents cabin to tell her they
had both been killed. Prior to finding her mother
alive a couple days ago, it was the most confusing
time of her life.

The only thing she could say for sure about Merl was
that he had lied to her. She supposed he could have
belived them to be dead, but he had also claimed to
have found the bodies, and he had known her parents
well and they always stopped to see him on their
travels to town.

Tyler also knew Merl well. On the occasional trips she
would take with her parents as a child, they would
often visit Merl. She had many fond memories of his
house.

Sleeping under the bridge was the coldest place they
had slept and had probably been a mistake. Despite
building the fire up, the wind whipped around under
the bridge. This kept the air cold and the fire burning
quickly. The contiually were adding wood to the fire
and trying to keep warm. By the time light began to
appear in the sky, the two were huddled together
as the last of their gathered wood burned down.

They made their way to Merl's farm as soon as
they felt they could assume a regular person
was up. They walked the mile to the farm.

Merl's farm was small and was not a farm
so much as it was a house with a large garden
and a pasture in which grazed a few head
of cattle. Merl lived here with his wife and
their grown son. They had all lived in this
house their entire life. Merl claimed the house
was over two hundred years old and he and
his family worked hard to maintain it. Now,
even Merl's son was getting older. With no
children in the family, it seemed that this house
might soon be on the abandoned ones on the side
of the road.

If there was one thing Merl's family was good at,
it was living off the land. They rarely needed
any supplies and made good use of their land.

As they approached the house, there was no
sign of anyone around. They walked up to the
front door and looked around. Tyler didn't know
what she had been expecting, but was still feeling
weird about showing up unannounced. She knocked
on the door.

"Hello," said a voice. It was coming from the garden.
Tyler and Triss turned and looked. I man stood up
from behind some of the shrubs at the far end of the
garden. It was Pedro, Merl's son.

"Pedro?" asked Tyler. But of course it was Pedro.

"Well, my my... Tyler. Wait right there." He started
walking up towards the house. About that time, the
door opened behind them. The two looked behind them
to see Merl's head in the doorway.

"Tyler!" said the old man in the doorway.
He looked mildly excited to see her. "You better
come inside." He opened the door fully and Triss headed
inside, then turned to wait for Tyler, who was waiting
for Pedro.

Inside, Merl served up hot tea to his son and their
two guests. They sat at his cozy table, eating bowls of
soup.

"How have you been?" Merl asked Tyler.

Tyler, so far, had not told him about her mother. Now
that she was here, she was hesitating a little. She sat
quietly a moment, trying to decide if she made the
right decision coming her. Mostly due to the fact that
she couldn't think of anything else to say, she finally
spoke.

"I saw my mother..." she said simply, letting the
implications of the statement hang in the air. Everyone
was quiet. The silence lasted a while.

It was Pedro who finally broke the silence.

"I thought your mother was dead," he said.

"No," said Merl, still looking at Tyler, "Tyler's
mother is not dead."

The group again sat together in silence. Tyler
expected Merl to continue, but the old man
just sat there quietly. Tyler had to break the
silence.

"What do you mean?" she said to Merl. "How
could you know and never tell me?"

"I will tell you," said Merl. 
"I probably should never have lied
to you, but it was your mother who made me
promise not to tell you."

And after saying that, the story of what really
happened to Tyler's parents was told.

Tyler's mother, Joan, and her girlfriend were
traveling to the city. As usual, they were planning
to stop by and visit Merl. He would feed them
and they would get a good night's rest before
continuing on their journey. Merl had been
expecting them anytime.

Merl had been out in the garden when two
Jeeps drove past the house. The vehicles had
been gasoline powered and were driven by
Union Police. The event was noteworthy;
vehicles, and gasoline powered at that, were
rarely seen around these parts.

Merl had wandered out into the street, trying
to catch a glimpse of where the vehicles were
heading. He had ended up standing in the street
with the vehicles already out of sight. He was just
heading back to his work when he heard gunshots.

Being so close to the farm, Merl decided to
investigate. He grabbed his own rifle from the
house and set off down the street.

Merl was old and didn't travel fast, about half a mile
down the road, he saw the Jeeps in the middle of 
the road. They had seen him and one of the officers
trained a gun on him. He dropped his rifle and
started walking towards the soldiers with his hands
in the air.

He walked up to the Jeeps. Three officers were standing
by the Jeeps. Two of the officers seemed to be ignoring
him while the other kept an eye on him.

The officer spoke to him, "What are you doing out here?"

"Uh, I live at the farm just down the road,"
said Merl, "I heard gunshots."

"Well, this is official Union business. I'm afraid I need
to have you return to your home."

Merl was certainly not going to stay and tangle with
the Union Police, so he turned and headed back to
his house.

He arrived back at the house a few minutes later.
He went inside to find his family and tell them the
news. When he got inside, he was surprised to see
his friend Joan and her partner sitting at his table
with his family.

Joan jumped up as he entered. Seeing her friend,
she calmed and said, "Oh Merl, we're in so much
trouble. There isn't much time!"

"What are you talking about?" Merl said to her.
"Are the soldiers looking for you."

"Yes... and they're tracking me now. They'll be here
any minute. They're going to take us away."

"What do you mean?" Merl asked.

"I can't explain. We have to go. Don't tell them
about Tyler." Joan was already getting up and heading
to the back door. She continued. "The only way
Tyler is safe is if they don't know about her."

"What do I tell Tyler?" he sked, "Does she know 
about any of this?"

"Tell her we were killed. She can't know about
any of this, either." And with that, the two of them
left.

The whole event was over so fast. The Union Police
came by a few minutes later. By this time, Merl was
working in the garden. He nodded at them as they
passed.

The next day he had set out to inform Tyler of the
"death" of her parents. He didn't understand any of
events which had occured, but used the trip to
the cabin to fill them in. By the time he reached
the cabin, he had evolved all the details of the
landslide and her parent's deaths. It had been
the most difficult and complex lie he had ever told.

\chapter{Lies}
Tyler sat quietly for a while after Merl finished the
story. To think that he had kept this secret from
everyone, even his own family, was increadible.

"I can't believe they had you lie to me," she said
after a bit. "Do you have any idea what happened
to them after that?"

"No," said Merl, "I haven't heard from them. After a while,
it was easier to just believe they really were dead."
The old man looked very sad, but Tyler could also
see that a huge weight had been lifted off his 
shoulders.

"I'm sorry you had to live with that," Tyler said
to Merl, "It must have been a huge burden."

"I think it's I that should be sorry, dear. What will
you do now?" The question had been on her
mind as well.

She spoke slowly. "Well, I feel like she probably
needs me. I think I should follow her to the city."
This was the first time she had officially mentioned
traveling to the city. She had always assumed it
might lead to this, but the idea was frightening.

Tyler had never been to the city, and had
still been getting used to life in the small community
at the farm. The idea of traveling to a place filled with
thousands of people gave her shivers.

Tyler added to her last thought, "I don't even
know what happened to Nora. I could never
go back to life on the farm without learnign the
truth."

Merl nodded, and Triss looked at her, as well.

"I'll go with." said Triss.

"Triss, you can't come with," Tyler said. "If my
parents and they seem to be messed up in
something."

Tyler was concerned about what the future
may hold. It certainly wouldn't be a good place
to bring one of her friends, despite how much
she would feel better having him along. But
then Triss said something that changed her
mind.

"I need a friend as much as you need a friend."
He said the words almost on the verge of tears.
"I don't want to be alone again." he continued.

"But, Triss," she tried another time. "This is
not your family. You don't need to do this."

"Even if something bad does happen," Triss
continued, "it will
be better if someone else is there. We can
figure it out together.

Tyler gave in. Triss was her partner now, for
as long as he decided to tag along. And, while
she would do her best to keep him safe, that
responsibility was his, because it was his 
choice to go along.

The talked with Merl a while longer, and Tyler
began to feel nostalgia wash over her. This
was the first time she had visited Merl without
her parents and she longed for the way things
were.

Merl's wife had passed during the winter, having
been married to Merl for seventy years. Merl was
taking it very well and seemed to be happy
for his wife. He said he hoped to join her soon.

The talked until lunch time, at which point, Merl
fed them again. He had such an amazing stock
of food for the time of year and they enjoyed
fresh food not even available back at the farm.

He provided them with a few supplies, although
Tyler was planning to travel back to the farm
before heading to the city. It would be best
to stop in, especially since Triss would now be
joining her for the long haul.

After lunch, Tyler made the decision to leave.
Although they were both tired, Tyler was never
someone to sit around and wait for things to
happen. She wanted to push on for a while
and make up sleep at the first stop. In her
head she had done the math and determined
they actually could get back in three days with
the help of this extra half day.

And so, weary with travel and new goal, the two
headed away from Merl's garden and back down
the road to the very place Tyler's parents were
abducted just a year ago.

\chapter{Back to the Farm}
As the walked together in silence again, Tyler
began to notice that their journeys always
began this way. But she felt she didn't have
anything to say at the moment.

Part of the reason for them leaving early was
due to the fact that it currently wasn't raining
again, although the treat remained.

They walked the entire day and into the night,
but didn't make it very late before giving up.
Having just been in this area, it was nice
knowing where they would be able to stay and
they found a nice building they had spotted
the previous day.

The building they were staying in had no roof,
but the brick fireplace was still standing. Also,
The way the hearth had been situated was in
the corner of two perpendicular brick walls,
making it an ideal place for them to set up a
simple lean to.

Although they were both sleepy, they found they
couldn't immediately sleep. They began talking.

Triss told Tyler of his parents, who had
disappeared after setting out to find others in
the family.He had been really young. He had
been risen as a orphan of the farm and had
never really had a family. The residents of
the farm always made sure he had been fed
and certainly gave him more than his fair share
of chores.

Tyler talked of more personal events, mostly
involving her parents. She told him of trips
to Merl's and to visit other friends in other
towns. She told him about the time they almost
left the cabin to settle by the ocean, but 
had changed their mind suddenly when
violence broke out along their intended route.

Pretty soon, the sun was rising, and both of
them noticed the lightness suddenly. Tyler
worried if this was going to hurt her finely
tuned schedule and Triss thought about the
sleep he was missing. The both agreed to
sleep, and it came to them both quickly.

They slept most of the way through the
day. At one point, they heard someone
passing on the road, singing loudly. Sounded
like he might have a dog as well. Tyler sat up
and looked out of the building, but he was
already past the building and showed no
sign of stopping.

In the late afternoon, the woke from their sleep.
It had been a good rest. They packed up
and headed out quickly. The rain had held
up another day, and their clothes, which had
been quite waterlogged, were now almost completely
dry.

They hit the road quickly, eager to cover a lot
of ground. Tyler felt more like herself, and
attributed the feeling to the few day of coping
she had had and the fact that she was getting
closer to the truth.

Pretty soon, dusk came around. The clouds had
covered the sky and soon it was very dark. The
only light available came from the little bit of
dispersed moonlight shining through the clouds
and the glow of their Pages.

As they came around a bend in the road, they
stopped suddenly when, in front of them, they
say another person. The person in front of the
was using their own Page to light the way and
stopped just as suddenly as they had.
The shape of the figure in front of them was
huge, and Tyler was instantly nervous.

"Hello," she said at the figure in the darkness.

"Tyler?" said the voice, "Is that you?" Tyler
wasn't sure she placed the voice. Her mind
raced to make the connection.

It was Gily. The fact came to her in a flash. But
what was he doing out here. After all, they were
almost three days from the farm.

"Gily, what are you doing here?" Tyler asked him.

"It's your mother," said Gily. "The police brought
her back to the farm. Jondra sent me to find you."

"Oh..." said Tyler. It seemed odd, but the
pieces fit. The two groups approached each other.

Gily came up and put his hand out. Tyler
reached to shake it. But as soon as his hand closed
around hers, she knew she had made a bad move.
His large hand closed around her much smaller one.

Her hand cried out in pain as his large arm pulled
her whole body toward him. He held her tightly in
a big one-armed bear hug. Tyler shrieked and thrashed
wildly in his clutches.

Triss jumped back like a scared animal.

"What are you doing, Gily?" Triss called out. "Let
her go!"

"No, I can't do that," said Gily, "and if I were you,
I'd get out of here while I could. I'm not concerned
with you, I'm just after her."

Gily waited to see what Triss would do. Gily was twice
the size of Triss and far stronger. Tyler still struggled,
bit Gily's arm held her tightly.

Feeling terribly frightened
about what might happen, Tyler began digging her
nails into Gily's arm, creating painful scratches. Gily
did not make a sound, but she had got his attention.
He turned her in his arm and with the other arm,
punched her squarely in the stomach.

Tyler felt all the air leave her lungs and she gasped
for breath. Additionally, the hit left a sharp and
immediate aching in her stomach, and she felt
her eyes immediately tearing up. She doubled over
as much as she could while he held her, trying to get
her breath. Triss was backing away - he had no other
idea what to do. He was going to have to leave.

Tyler had stopped struggling and Gily was basically holding
her up. Gily turned his attention back to Triss, who was still
backing away.

"Go on," said Gily, "Get out of here."

Tyler was torn. She hated seeing Triss leaving, but
knew he couldn't save her. But instead of seeing
him leaving, she saw a shocking decision by
her friend.

Triss was bending over to pick up a tree branch
laying on the ground next to where he stood. It
was large enough that Gily took notice.

"Don't be dumb," Gily said to Triss, but Triss had
already committed to some plan in his head and
was walking towards Gily with the stick.

Although he was skinny, Triss had worked in the
fields his entire life. He had muscle on his bones.
Still he was not a fighter. But he swung the branch
with all his strength at Gily.

Anticipating the blow, Gily put his arm up to protect
his head and turned his back towards the swing.
The branch connected squarely with his back with a
dull thud. It certainly stung the large man, but had
done little to hurt him. Still holding Tyler, he reached
with his free arm to grab the branch before Triss
could yank it back.

Gily was too late, and Triss pulled the branch back
for another swing. Before this could happen, though,
Gily had closed the gap between him and Triss. He
used his free to grab Triss around the neck. He
was now holding both the travelers.

There was little Gily could do in this position and he
knew it. Triss was struggling like a mad man, and 
Tyler was recovering from the blow he'd given her.
He had to get this over with.

He released Tyler with a twist of his arm. The shock
of spinning and no longer being held up was enough
knock Tyler off her feet. She fell into the dirt. Gily,
meanwhile, could now focus all his anger on Triss.

Triss had dropped the branch, his only weapon, in
the hopes of prying himself free of the grasp. Now,
the arm let go of him and he stood up just long
enough to be struck hard in the jaw by Gily's other
fist. There was a flash of white across Triss's vision,
and then blackness as his brain attempted to cope with
the blow.

Triss stumbled back, trying to stall long enough to
at least come to his senses before the next hit came.
He failed. Gily ran at him and tackled him down onto
the road. Triss flailed around uselessly under the
weight of Gily.

But now Tyler was up again. She had her breath
back and was watching her friend about to be
killed by this lunatic. She jumped on Gily's back
and hooked her arms around his neck and
shoulders. Her momentum was enough to
unsteady him and one of Triss's struggling legs
connected with Gily's groin. The man let out a shout
of pain. He raised his body up over Triss, with Tyler
still hanging off his neck, balled up a fist. The fist
crashed down onto Triss's face, and propelled it
down into the hard road below. This time there
was not white flash of light, Triss simply blacked out.

Tyler was desperately trying to choke Gily, but he was
just too strong. With Triss now out of the picture,
he was focused on getting Tyler off his back. He rolled
over, trying to shake her off. She wasn't letting go. In
fact, being on her side allowed her to reposition her
grip, and she went for weak point.

With her hand, she reached up to his face and pressed
two fingers into his eye. She had accidentally poked
people in the eye before, but had never deliberately
attacked someone like this. His eye was surprisingly
soft and provided little resistance.

Gily went off like a top and was yelling furiously.
He reached up with his hands and pulled her arm
off his face. Tyler wormed her small hands out of his
grip and rolled off his back and away from him.

"You bitch!" he yelled. Tyler scrambled to her feet and
looked at him still lying on the ground, gripping at his
eye. He was bleeding down his face.

Before Gily could get up, Tyler tried to find the tree
branch. She saw it lying some distance away, but closer
was a good sized stone. As Gily stood up, Tyler picked
up the rock.

Gily stood holding his injured eye and trying to find Tyler
in the dark.

As his one good eye located her in the dark, 
he was just in time to see her hurl the
apple sized rock at him.

Tyler's aim was excellent and the rock struck
him directly above his good eye. The rock
fell hard to the ground and for a moment it
seemed Gily would absorb the hit. But then
he stumbled back and fell to the ground.

A second stream of blood began pouring from
the wound over his other eye. Tyler wasn't
sure what to do next. Gily was still moving around.
Triss was lying still in the dirt. There was no way
of knowing how long Gily would stay down.
Tyler had to act quickly. She quickly picked up
tree branch and ran over to Gily. As she walked
near him, his dazed attention turned towards
her. His face was covered in blood and his one
good eye looked around in panic. In one last
effort to remedy the situation, he lunged from
the ground at Tyler's legs, but he was too slow.
Tyler stepped back and at the same time swung
the branch down onto his head.

\chapter{Gily Leaves}
THIS NEEDS MAJOR REWRITE

Morgan sat in the corner of her room. Blood
ran from her nose and drops covered the front
of her shirt. In front of her, Gily was pacing
back and forth, looking for various things he
would need on the road.

"Who are you?" sobbed Morgan.

"Oh, sweetie," said Gily sarcastically, "None of this
is your fault. I was put here to keep an eye on
this part of the Union."

Gily had come home unexpectedly in the middle
of the day. Morgan had been in their room,
having lunch. He had told her he had to go and
he wouldn't be back. He had been drunk.

"I have orders," Gily continued, "And now I need
to follow them.

\chapter{Post Attack}
Gily died in the street. Tyler had repeatedly struck
him with the branch until he stopped moving,
which had taken her a shocking number of
swings. When she finally stopped, she was out of
breath and crying terribly. Gily's face was
unrecognizable. He had been breathing shallowly
then, but had stopped at some point while Tyler
tended to Triss.

After she tossed the branch aside, Tyler had gone
immediately to Triss. Compared to Gily, the dark
bruise forming on Triss's face seemed minor. Triss
was breathing steadily but was still unconscious.
Tyler looked at the two men lying in front of her
on the dark road. She turned back to Triss and
picked up his head in her hands and tried to wake
him gently.

For the next minute or so, Tyler cried alone in the
street, unsure what to do. At some point, she looked
down and saw Triss's eyes flicker a little and then
open briefly before squinting and shutting again.
He moaned softly.

"Triss? Triss! Can you wake up for me?" Tyler asked.
She tried again. "Please wake up, Triss."

He did wake up, and looked at her, obviously still
dazed. He didn't seem to know who she was or
where they were. Tyler was just glad to have him
conscious. She sat with him while he brain struggled
to sort everything out. Eventually he spoke.

"Are you alright?"

"Yes," she said to him. "I'm fine, I think." The punch
she had taken had hurt, but she had seen worse.

Triss looked around, saw Gily lying in the road, and
looked back at Tyler.

"Did you kill him?" he asked.

"I don't know," Tyler sighed, "He was breathing." From
where they were, there was no way to tell if he was
still breathing.

"Can you get up?", she asked Triss, "I don't want to
be here anymore."

"Yeah," said Triss.

Triss did not get up right then, but within a few more
minutes, Tyler helped him to a sitting position, and then
they got him on his feet.

Together, the walked over to Gily. His head was now
laying in a small puddle of blood. Tyler confirmed his
breathing had stopped. Gily was dead.

No one would likely be by anytime soon. There was
really nothing that could be done with the body. They
drug the corpse off the road. Tyler wrote out a message
in Gily's Page explaining the death, but not identifying
herself or Triss. No one would question the death or
look for the killers. It was just something that happened
from time to time. It was unlikely Gily would even be
buried.

Tyler and Triss left the scene while it was still the middle
of the night. The walked quickly. Triss's head was
pounding but they both knew it would be a bad idea for
him to sleep.

They walked the rest of the night and all through the
next day, both wanting to be a far from last night's
attack as possible. The going was very slow, and the
pain in Triss's head worried Tyler.

When they had finally walked as far as they could,
they had put almost thirty miles between themselves
and Gily. They would sleep through the night and 
continue in the morning. They could be at the farm
tomorrow night.


They did not make a fire. They sat together in an
abandoned house and ate whatever they had that
didn't need to be cooked. They attempted to plan
their next move.

This issue on Tyler's mind was not knowing the reason
for Gily's attack. Everything had happened so fast
and no one had done much talking. He had mentioned
only needing Tyler, and Triss could go. But it was 
hard to know what that meant.

"Do you think the farm is still safe for me?" said Tyler.

"What do you mean?" said Triss.

"Well," replied Tyler, 
"what if it was Jondra or Jamal that sent Gily out for
me. What if they don't want me around the farm
anymore."

"They would never do that," assured Triss, "They've
never done anything like that, even with the most
dangerous residents."

"I guess, but what other explaination could there be?"

Triss shook his head.

"I think we should be careful tomorrow," Tyler decided.

"We will be," said Triss. And followed with, "I need sleep.
I'm exhausted and my head is killing me."

He bundled up his pile of clothes and lay his head down.
Tyler noticed that he was sleeping soundly in less than
a minute. She felt the same, but couldn't let herself lay
down yet. The mystery of Gily's attack was eating at her.
It gave her the feeling that maybe there was a lot more
going on than she first suspected.

She stood up and walked over to the broken out
window of the building. For several minutes she looked
outside, thinking, but in the end she went to bed with
no resolutions.

The pair slept through the night and work up at first
daylight. Triss still had a large bump on the back of his
head and his face down one entire side. Despite the
way it looked, though, he was in good spirits. Tyler
had escaped major injury and felt horrible for what
Triss had done to save her life.

Back on the road, Triss asked what their plan was.

"I'm think we should go back to the farm." said Tyler.
"If Jondra and Jamal sent Gily after me, I want a
chance to explain myself. If they didn't, we need
supplies before we go into the city.

Triss again defended his opinion. "I don't think they
had anything to do with it. Gily was just crazy."

They walked the rest of the day and arrived at the
farm just after dark. No one was outside. It was
dinner time. People would be in the farmhouse or
in the barracks common area.

Tyler and Triss walked in the front door of the house.
The looks the saw in the faces of the people eating
told them some of the Gily story had made its way
around the farm. Torrin, someone who worked
closely with the landlords, spoke up.

"You two should go see Jondra. She should be
upstairs."

Tyler and Triss went upstairs, and knocked on the
door of Jondra's room.

"Come in." they heard from behind the door. They
entered.

Inside the room, Jondra sat at her desk, eating
dinner. When she saw the two enter her room, a
shocked look came over her face.

"Good god," she said to the two of them, "what
the hell happened to you, Triss?"

Tyler felt a bit of relief at Jondra's concern. It seemed
that she was not the one who had set Gily on them.
Tyler was the first to speak.

"It was Gily," she started, "He attacked us on the
road. I don't know why."

Jondra looked down. "He left the farm two days ago.
He attacked Morgan, too. No one knows why... or they
aren't saying. Everyone's been on edge." Then she
paused and looked carefully at them. "Where is he
now?"

"He's dead," said Tyler. "We fought back and he
was killed."

"Well," said Jondra after thinking a moment, "I'd say
he had that coming. The bastard."

"Why did he attack us, Jondra?" asked Triss.

"Like I said, Triss, no one knows. But since you two
were attacked, I would say it probably relates to the
apearance of your mother, Tyler."

"Yeah," said Tyler, "I was thinking the same thing."

Tyler told Jondra the rest of the story about her parents.
They talked about the trip to Merl's and the attack from
Gily on the way back. She finished by telling of her plan
to travel to the city in search of her mother.

Jondra listened carefully and then said to them,
"We're going to need to tell Morgan. She's been a wreck
the last two days. Wait here. I'll get her."

Jondra left and went downstairs. Tyler and Triss sat 
together in silence. Jondra returned with Morgan a short
time later. She walked in the room with
a large black eye matching the one on Triss.
She looked at Tyler, then at Triss. She noticed
the bruising on his face and gasped in horror.

"What happened?" she asked.

"Sit down, Morgan." said Jondra. Morgan sat.
She looked tired and worried. Jondra
continued.

"Morgan. Gily is dead. He attacked Tyler and
Triss on the road northeast of here. They
defended themselves and he died."

Morgan sat a moment in silence, then began
sobbing. Tyler didn't know what to say, but
thankfully, Jondra was handling this.

"Gily told Tyler that she was the only one
he was concerned about. He tried to get
Triss to leave. Do you know why he would
be after her?"

Morgan looked at Tyler and said to her,
"I don't know. Why did you kill him?" She
seemed immediately more defensive.
"Why couldn't you just run away?" She was
crying so much now that it was hard to
distinguish all the words.

"Morgan," Tyler said, "It all happened so
fast. I didn't have time to think. He just...
grabbed me and we fought back. I'm
sorry."

"Gily loved me!" Morgan asserted. "He
loved me! And I loved him. No one had
ever made me feel that way and now you
killed him."

Morgan stood up and left the room, still
in tears. Jondra sat with Tyler and Triss.
Triss broke the silence first.

"Should I go check on her?" he asked.

"No," said Jondra, "I think it might be a
good idea to leave her alone for a while.
She has had a rough couple days."

Tyler was also on the verge of having enough.
This whole experience had been a nightmare.
And now she was just going to travel to the
city and try to find her parents? The whole
idea was too much to think about right now.

"Jondra, can I go?" asked Tyler.

"Yes, of course. You can go whenever you want."

Tyler got up and left the room. Triss jumped up
and followed. Jondra sat at her desk a while
thinking about everything that had happened.
She now believed Gily to be a spy. She had
wondered if there may have been someone
in their midst who wasn't who they said they
were. It seems that person was Gily. Fortunately,
thanks to Tyler and Triss, that problem seemed
to have taken care of itself. The other problem,
Tyler, also seemed to be taking care of itself.
If Tyler went looking for her parents in the city,
it was unlikely Jondra would ever see her again.
And if she had to lose a good kid like Triss in the
process, she could live with that. She decided
the farm would probably be better off without
Tyler and went back to her cold dinner.

\chapter{Campfire Again}
Tyler had convinced Triss to head out to the
campfire with her. She needed a place to think
and this was where she liked to come. Together
they sat around the roaring fire. Having slept
outside for the past several nights, some of the
charm of their place was lost, but it still had a
hint of memory that gave it a homey feel.

"Triss, you can't come with me." Tyler said,
"This is too big. I'm going to get you killed."

"You would have been killed if I hadn't come
with you, remember?" replied Triss. It was a
good argument, but Tyler wasn't accepting it.

"You're right, Triss," she said, "You're right.
And I'm probably going to get myself killed. But
I can't risk your life, too. You have a good life
ahead of you if you stay here, on the farm."

Triss did consider it, but his mind was made up.
Besides, he was excited about seeing the city.
For someone who had spent his entire life on the
farm, the city had a certain magical quality to it.

"Tyler, you're sweet, but..."

His voice trailed off as they heard sounds in the
woods. Something was approaching. They both
tensed, subconsciously conditioned by recent
events. A man entered the light and walked
toward the fire. It was William.

"Will!" shouted Tyler and ran up to give him a
hug.

William gave Tyler a big hug, and even kissed her,
which they rarely did in front of other people.
Tyler was happy to see him.

Triss greeted William and William sat by Triss
to give his face a quick inspection. The medic
had already given Triss a check, but William
also had a little first aid experience and obviously
wanted his own conclusion. Triss and William
were not friends, but Tyler appreciated that he
checked up on him anyway.

William wanted to know the plan, and Tyler
explained the plan, although it wasn't much of
a plan. He didn't seem to appreciate it, but
understood her need to do it.

"The city isn't like out here," he warned her.
"You'll find everything is different. It's like 
being on a foreign planet."

Tyler knew a little bit about what to expect.
After all, her parents had traveled to the city
once a year for a long time now. They had
told her stories. Plus, there was plenty of
news media coming in on the Broadcast. It
would be a big change, but she was confident
she could handle it.

They talked a while about the city and rumors
they had heard. When the fire died down they
walked back to the farm together. They entered
the barracks together; Triss went to his room,
Tyler and William to William's room.

Triss looked around his room. Unlike Tyler's,
Triss had packed his room with collections
of things from over the years. His walls were
filled with paintings and even a few pictures.
He had a variety of games and carvings set
out on a number of shelves he had hand made
and mounted on the walls.

Living in one place for a long time, it was easy
to collect a lot of stuff. Triss thought about how
he would be leaving it all tomorrow, to go to the
city.

As Triss slept in his bed that night, he was
haunted by dreams of Gily chasing him through
a forest. Running through forest, there would be
moments during which he thought he recognized
where he was. But, the next moment, he would
not recognize anything. He continued running,
as the beast, Gily, chased him, never finding
the farm.

Triss woke early the next morning. He showered
and shaved. He put fresh clothes in his backpack.
They would restock their food supplies at the
farmhouse pantry on the way out.

Triss had not seen Tyler this morning, and started
looking around for her. Walking out into the common
area, he saw William sitting at one of the tables with
a cup of tea. Triss joined him.

"Morning, Will," said Triss to the man sitting quietly
at the table sipping tea. William glanced over a Triss
sat down, but returned his gaze to the window.

"Have you seen Tyler?" he asked William.

William turned his gaze and stared a Triss.

"Tyler's already gone."

\chapter{Tyler's Gone}
By the time Triss learned she had left, Tyler had already
been on the road for several hours. She felt she needed
to have a good distance between herself and the farm
or she'd risk Triss following her. He meant well, but she
knew that this was not in his best interest and could very
well get him arrested or killed.

Tyler had never made the journey to the city. She had
been to several of the smaller towns in the area, but
going the the city was like going to another world. The
city had continuous power and computer networks. It
sucked in the wealth of the entire Union. If any technological
rebuilding was being done in the Union, it was happening
in the city. In addition, it was the seat of the Union
government and the Union Police. It would likely be the
place her mother was being held.

The first leg of her journey had been the familiar trip to
Broadcast Camp. She had never been there on a
non-Broadcast day, and the site was eerie and quiet.
Out of curiousity, she had removed her Page and tested
the webwork connection, but it was quiet as she expected.
It would still be several days she guessed before she was in
range of the continuous Webwork connection.

She kept walking beyond Broadcast Camp, following a fairly
well traveled road from the camp. She was in new territory
now, and had reached the end of what could be planned.

The recent events leading up to her present situation had
all occured since her last Broadcast, meaning she had been
unable to download any information she would liked to have
had available on her trip. Thus, she was making use of
outdated maps and travel information available from the 
farm's servers.

Based on the information she could find, the trip to the city
would take as many as seven days, depending on weather
and what she encountered along the way. Long before arriving
at the actual city, she would reach the boarder of Continuous
Broadcast, within which lived the majority of the Union's
citizens. In this area, she would need to determine where she
needed to go for information about her mother.

Beyond Broadcast Camp, the people were still spread relatively
thin and were organized into small communities similar to the
farm on which she lived. As she traveled closer to the city, the
density of the citizens would increase dramatically. For now, she
enjoyed the country side in which she had spent much of her
life.

As the day drew to a close, she began looking for a place to
set up camp. It was much less common to find an unihabited
building in this area; she was considering finding a local who
would be willing to let her camp out on their land.

One house, in particular, seemed promising as she walked past.
It was a beautiful, well maintained house, nestled next to a 
quiet creek. What stood out about this house was the noise
coming from its yard.

The household such as this one she had come across was a
common site in this areas. It was a large, multi-generational
family, all living together on one piece of property. Today,
the family was having a party of some sort in the yard. There
were many children playing games and lots of food. Tyler
decided it was worth asking if they would put her up for the
night.

She approached the house from the road, and was spotted
almost immediately by someone in the group, who quickly
alerted the other of the stranger approaching the house.
A woman left the rest of the group and headed toward
Tyler, who stopped and waited politely. The woman was
middle aged, with a tough look and short black hair. She
swung her arms confidently as she walked.

The woman walked up and said suspiciously, "What do you
want?" This was common, but the woman's body language
did not convey any anger.

"Hi. My name is Tyler, and I'm passing through. I'm looking
for a place out of the rain to sleep for the evening. I have my
own food."

She felt like she had sold that pretty well. She waited for the
woman's response.

"You look like a thief," said the woman, "Are you sure you're
not going to cause any trouble."

Tyler was mildly offended at being compared to a thief. She
don't know what it was that told the woman that. She
considered just turning around and moving on (sometimes
that was simpler) but she changed her mind.

"I promise I'm not."

The woman seemed to be coming around.

"Alright. Call me Midge. We have enough food. You might as
well come have some."

Midge smiled for the first time and put out her hand. Tyler
shook it and thanked the woman.

As they walked back to join the party, Midge was much more
welcoming. She told Tyler tonight was the party for her
twim grandchildren's birthday. Tyler also learned that twenty
one people made up the clan, thirteen of which lived here and
the rest lived in the house next door. They had been neighbors
until a marriage joined the families a few years ago.

Midge had been correct saying they had enough food. There was
pork in a spicy sause being served on fresh corn flour tortillas.
There was also plenty of rice and refried beans. It was all
hot and filling. Most of the family had eaten, but Tyler was content
eating alone.

When she finished eating, some of the younger children who were
interested in the new stranger wanted to show her their room.
They brought her inside the house and down to the basement,
which was apparently shared by all the children living in this home.
The children had been very creative in using anything they could
find to create an elaborate network of forts. She crawled on
her hands and knees as they guided her through to the central
area. Here, they sat in a circle and the children produced a Page,
which they apparently all shared. It was larger, though, and they
shared with her their favorite games.

Soon, the children grew tired of the fort, but had a new plan of
showing Tyler how they catch catfish from the creek at night.
The parade of children guided her back upstairs where Midge and
they other adults were taking advantage of having Tyler around
entertaining the children. However, despite the children's
enthusiasm, the fishing trip was not allowed. Furthermore,
the children were sent off to bed.

Tyler further made herself useful by locating the kitchen. Here, she
found a man tidying up the kitchen. She offered to help and
he put her to work washing dishes. It was nice to be able to help
out, but before long, the man had disappeared, apparently leaving
her to pay off her meal. It was fair, and she slowly worked through
the dishes of over twenty people.

When she finished, she rejoined the adults. Midge thanked her
for her work. It was getting late, and Tyler asked where she could
get some sleep. Midge showed her to a nearby room. It was mostly
empty and was missing it's exterior window. A cold draft moved
through the room despite the opaque plastic covering put over
they opening. But, the room would be warmer than many of her
previous sleeping locations and Midge was able to provide her with
both a blanket and a pillow. Tyler would likely be quite comfortable
tonight. 

\chapter{Next Day}
When Tyler woke in the morning, the commotion in the house
was more subdued. The children were outside or still sleeping,
and the other half of the family had returned to their own
house. In fact, Midge was in the kitchen with only two other
people, who Tyler recognized as Midge's son and his wife.

The three of them were eating fried eggs which Midge cooked on
an electric range. When she was offered one, Tyler did
not refuse.

While she waited for her egg, Midge's son, who's name was
coincidently William, asked her where she was heading.

"I'm going to the city," Tyler tried, hoping there wouldn't be
too many additional questions.

"Alright," said William, "We get a lot of travelers like you in
these parts."

"How many days walk is it from here?"

William considered the question.

"Well, I've heard it's six days, normally. But a lot can affect
that number."

"Do you have any advice?" Tyler asked next.

"Yeah," said William, "Watch your back. They know everything
that happens in the city. It can be surprising if you aren't
used to it."

"Thanks," she said as Midge server up her egg.

Tyler ate and then got moving. She felt energized after
having such a positive experience with her temporary
family. Now she wanted to start marking off the six
days of travel in between her and her mother.

The sky was dark this morning. It would probably rain
on her before too long. She tightened the straps on her
backpack and quickened her pace.

Her day was productive and uneventful. She felt strong
and she felt like she made fewer stops than usual. At the
end of the day, she found herself sleeping in a run down
bus parked on the street in front of a old man's cottage.
The old man had been sitting in a rocking chair on his
front porch as she walked by. He hadn't even spoken to
her, and had simply pointed to the bus when she
enquired about a place to stay for the night.

Sleeping in the bus sapped some of her strength. It had
been an uncomfortable night which she had forced
herself to sleep through. On top of that, it was raining as
she got off the bus and started walking down the road
again.

Tonight, if she kept the same pace, she would reach the
first town on the way to the city. This meant she could
resupply, possibly get some real food, and maybe 
receive a broadcast.

By mid afternoon, she came upon the edge of town.
For the past couple of hours she had been passing an
increasing number of settlements. Also, the road
she had been following had been joining up with other
roads. Now, she was seeing other people regularly and
had recently been passed by a man on a bicycle.

In many ways, this town was not unlike the town in
which she had gone to school. It was lightly populated
and was little more than a couple hundred homes
congregated around a few key businesses. The majority
of the homes around here would be self sufficient and
would only rely on a few of the local businesses for
conveniences and community.

The outskirts of town gave way to what passed for a
"main" street, Tyler began looking for a store selling
supplies. A building with a hand painted sign reading
"Buck's General Store" would serve her needs. She entered
the front door.

Tyler knew she had some money. Her parents had done
pretty well before they disappeared, and there was
money in the bank. The economy, however, was extremely
unstable. Inflation rates were unpredictable for any given
currency, of which there were three major ones. So,
despite knowing how much money was in the bank, Tyler
had no way of knowing what that would actually buy her.

She walked in the store. The shop was divided roughly in
half, with half the store devoted to food and the other
half to everything else. Tyler took a slow walk through the
food section, as there were many items which simply were
not seen very often on the farm. Inflation had not been
as bad as she had feared, which was a good sign. Having
usable currency on a trip like this would make things a lot
simpler.

She approached the man at the front counter with her
supplies, and also a box of cookies with the Union symbol
on the front. She remembered the cookies from school and
couldn't resist the urge to get them again.

As the man scanned her purchase into the register, she
asked about Broadcast.

"Is there anywhere in town to get on the Broadcast?"

"Nope. You're still about forty miles from Broadcast coverage."
the man replied.

That was disappointing. Her purchase was processed, and 
she took out her Page and made the payment. She unzipped
her bag and put her new supplies in the pack. She thanked
the man and walked out with the cookies in her hand.

She walked down the street nibbling on a cookie. It was dry,
crumbly, and super sweet; just the way she remembered.

Being so disconnected had never really been an issue for
Tyler. Her once a week Broadcast had been more than
enough for the books, news, and history she had been
interested in reading. But now, with her mother being held
by the Union Police, she needed access to maps, Union
trials, news stories, and email addresses. It had already
been over a week since her last Broadcast, and this next
week was the first non-Broadcast week since the change.
She was beginning to feel very out of touch.

She decided if she was going to learn anything before
reaching Web range, she would need to post a manifest
to the Webwork. She found a good spot to sit and pulled
out her Page.

The Webwork was a decentralized way of finding information
developed during the Destruction. It was slow, but given
enough time, it could be very effective. This was especially
true in more populous areas.

Before planning out her manifest, Tyler did a quick scan of 
the area. The more web threads she could pick up, the
better her chance of finding the information she wanted.
To her surprise, the thread statistics in the area were high.
Tyler looked around a little surprised. The area did not seem
like it would be well connected, but there was a lot of data
moving around this little town. A small shop down the street
advertised Page repairs. Tyler decided to check it out and see
if they knew anything about the webwork statistics.

When she got to the shop, she found it rather busy with
people. It seemed to be a meeting of some type. She was
standing just inside the front door. In front of her, a glass
display case served both as the place to store items for
sale and the repair counter. It was currently unoccupied.

In the back of the room, a few chairs had been set up and
around ten people were sitting together, working on their
pages. This was probably the source of the unusual webthread
count. The people sitting in the chair had heard Tyler come in.
They were waiting for someone to say something, which
eventually happened.

"Can we help you?" asked a voice off to Tyler's left. She turned
and saw a young, exceptionally short, woman standing behind
a desk. She was working on something different from the others
and they seemed to be taking their cues from her.

"Uh, yeah," said Tyler, "I was putting a manifest on the webwork
and noticed a lot of threads in the area. Is that coming from here?"

"Yes," began the woman, "I do believe so. There isn't much that
happens in this town without it coming through this room. 

"Is there a connection to Broadcast here?" Tyler asked.

The woman smiled.

"Well, no. Not exactly. You might say that we run our own
Broadcast, though. We're developing an open source application
to augment the service of the Broadcast. We basically provide a
longer range communication than what you can get from a
Page alone."

Tyler was impressed. These people had set up there own Internet.
It was probably primitive, and obviously a lot of work, but it was
an impressive feat all the same.

"Is it alright if I use it?" Tyler asked, "I just have a few requests
to dispatch."

"Sure. Let me get you set up."

The woman showed Tyler how to access the network and showed
her how to send in her manifest. Then, Tyler went and sat with
the others at the tables. It was like a library of sorts. Everyone
was here to get information off the webwork. Tyler appreciated
the way the community was supporting an initiative such as this.

The persons she sat beside was an older man with white curly
hair. He had offered her the spot next to him when she 
walked over. She had accepted. He had not introduced himself.
He was reading a listing of obituaries and eating popcorn
from a plastic tub.

A few minutes after dispatching her manifest, the log provided
her with data indicating the current progress. She was impressed
with the results. Pulling data off the webwork from the farm
was basically impossible, but here, the information was already
being received on her page. If she stayed within range of this
cities signal, she might have the data she wanted tonight or
tomorrow morning. Although it was still early, the idea of
getting her data tonight made Tyler reconsider logging some
more miles before bed. She ask the man about local
lodging options.

"Jake has some tents setup, and rents space to people
passing through," the man said, "That's half a mile west of here.
Look for the big white tents on the south side of the road."

Tyler thanked the man and the woman working in the strange
little shop. She left and headed west.

Jake's tents were easy enough to find. They were right where
the man said they'd be, which was fortunate. There were
two tents. These tents
weren't little camping tents, they were large white tents, the size
of a house. Originally meant as temporary shelter, these
tents now seemed to be more or less permanent structures that
would easily sleep forty people each; or twice that in an
emergency. Each tent had been visibly repaired in several places,
but at least they had been repaired.

The place was deserted, with no sign of Jake. Tyler looked around.
The only person she could see was a young girl walking a dog
down the road. She was walking this way. The girl threw a ball for
the dog, who ran off into a field to retrieve it. As the girl got
closer, Tyler pegged her at twelve years old. She wore overalls, boots,
and a cowboy hat. Tyler called towards her.

"Hi. I'm looking for Jake. Is he the one who rents these tents? Go you
know where he is?"

The girl continued walking. She was closer now, about ten feet away.

"I'm Jake," said the girl. Her dog ran up and she threw the ball again.
"I rent out the tents."

"Really," said Tyler, "How old are you?" It was a rude question, but
Tyler could not avoid her curiosity.

"I'm fourteen," said Alex. She must get that question a lot.
Tyler thought that fourteen might be an exageration.

"Right," said Tyler. And then, "I'm sorry. That was rude. I need to rent a
place to sleep for the evening."

Alex threw the ball for the dog again.

"Okay," Alex agreed. "Fifteen hundren for the night, and I don't be
surprised if other show up in the night. That tent will sleep an
army and you sure aren't getting the whole things to yourself.

Tyler paid with her Page again. There was no key or anything for
Alex to give her. Tyler thanked Alex and headed to the tent.

The inside of the tent was completely empty, as Tyler had suspected.
This beds were bunkbeds, to be specific, and it looked to Tyler
link an army barracks. None of the beds were partitioned in to rooms,
or even their own area. It was true barracks style living.

Despite the warning from Alex, Tyler was relatively confident that
no one else was staying in this tent tonight. She made a quick check 
of the beds and picked the best one for herself.

That evening, she lay in bed and watched the news roll in on her Page.
She admired, again, the network of this city. Many of the items on her
manifest were still a long way from complete, but just the fact that
she had received a few things off her manifest was miraculous. She
spent the evening laying on her bunk bed and catching up with the
outside world.

The first thing she was able to get off the webwork was her bank
information. Her parents had always believed in banks and she
had always had a bank account. She had rarely used it before today.

Based on her account information, it seemed that she would have
enough money for a couple weeks.

Tyler fell asleep reading messages and updates from her friends. Many
had heard about her mother and were offering condolenses.

/chapter{Attack}
Tyler woke up to the sound of gunfire. It was a very recognizable
sound. She had been sleeping in the top bunk. She looked around the
barracks and saw that it was still empty. Still groggy, she jumped down
from the bunk and carefully went to the window. As she neared the
window, she heard more shots, but looking out the window, all she
saw was darkness.

Whatever the reason for the shots, they had been
far away. For all she knew they always fired off their guns at night.
Tyler returned to her bunk. She lay for a while and, hearing nothing
else out of the ordinary, she drifted back to sleep.

Tyler woke a couple hours later when several people entered the
barracks. It was still a few hours before
dawn. The young girl, Jake, was with them. One of the others, a
young man in his twenties, spoke to Tyler.

"Miss, can you please get down from the bunk and answer a few
questions for us?" the man asked. the group looked serious.
Tyler could not think of anything she had done wrong and so she
complied. She walked over an stood in front of the group.

They man asked a first question, "Have you been here all night?"

"Yes. Of course. What happened?" she asked.

"Let us finish our questions first," said another member of the group.

"Do you know the whereabouts
of Junior Jones, Leon Watts, or McKenzie Umbrey?" said the same
person who had asked the first question.

"No," said Tyler, "I don't even know who those people are."

The group continued asking questions of her for almost a half hour.
At the end, they seemed to be safisfied and the group dispersed,
although, Tyler could tell many of the people were still up upset.
Only Jake and the interrogater remained, which meant it was time
for Tyler to ask a couple of her own questions. She started with
the simplest question.

"What happened?"

"The city was invaded by several men and women on horseback,"
the man told her, "They kidknapped several of our citizens. Since
you just arrived, we felt it was important to question you. Tyler
asked another question.

"Do you have any idea who it was?"

"No. The people were unknown to us."

Before too long, the man and Jake left. He told Tyler to
stop by his office in the morning before leaving town.
Tyler was up for most of
the rest of the night. She couldn't help but parallel the kidnapping
tonight with that of her mother's. In both cases, the attackers
were strangers who showed up out of nowhere and took someone
away with them.

The next morning, Tyler packed and headed out of town. Before
leaving though. she stopped by the office of a man named Cody;
the man who had questioned her the previous night.

Cody did not have anything else to question her about, but she
did find out that one of the residents of the town had been killed
in the attack. Tyler was already beginning to feel the safety of the
farm vanishing behind her as she walked closer and closer to the
City.

Now on the road again, Tyler was keeping an eye open for anyone
on horseback. She had her fullproof alaibi down and felt she could
handle the cavalry, but didn't want to chance it.

Today the weather changed to rain again, and for some time, it
was so intense that Tyler hid out under a large tree, in an attempt
to keep her shoes and socks dry.Trying to keep her feet dry would prove to be impossible
and she opted for heading back into the rain. It was too
hard to try to wait it out.

She walked along in the rain for a long, which did eventually
give way to a drier weather, but having a cold breeze.
Even with the terrible luck she was having today with
weather, Tyler felt as if things were actually going pretty
well.

The previous night, as her manifest had began rolling in
from the webwork, she had been able to finally begin
planning the next steps she would need to take once
reaching the City. The Union Police were stationed on
the far west side of town, meaning she would have
almost another full day of walking just to get to the
other side. On the other hand, in the city, there would
be other forms of transport, which could get her to that
side of town.

The Union Police station, was half emergency handling,
half prison, and half military. The Union Police was the
generic name given to the security branch of the
government. Their reach was far and wide.

Once she reached the station, she would probably be
able to inquire about the reason for her mother's
arrest and maybe even have a visit with her. This is
where she intended to start. If she could talk with
her, face to face, she would be able to figure out some
of the reason for the false death report about her mother.

If her mother needed her help, she would stay in the
city. There were many things she would do to assist
in winning back her mother's freedom. And there was
also still the issue of her mother's girlfriend, whose
whereabouts were still unknown.

Tyler didn't let herself consider any situation other than
one in which her mother was still alive. She had spent
they last year believing she had died. She did not want
to continue that line of thought any more until she
saw her buried in the ground.

Tyler decided to walk late into the night. It had already
been dark for some time, and she was particuarly tired.
In addition, there had been no good places to set up
for the night. So, she kept walking.

As she came up and over a larger hill, she got a first
glimpse of the faint glow of the City in the distance.
It was impossible to make out any of the actual city
as she was just seeing the reflection of the lights off
the clouds, but to her it seemed that she was making
good progress to her goal.

She walked a couple more hours until she passed an
abandoned market on the side of the road. It was
probably not the safest place to rest up for the night,
but she was getting tired and wanted to be out of the
cold for a while. She did a quick check of the 
property to see if anyone was living in it, and then set
up a sleeping area in the back. She set up a few larger
pieces of debris around her so that anyone else trying 
to camp out here would need to make a good deal
of noise before reaching her sleeping space, allowing
her time to sneak out another way. She stretched out
on the floor and went to sleep. 

During the next day of travel, the road she had been
following joined up with one that was much larger
more traveled. It was obvious that she was now on
one of the main highways of the Union. According to
her map, this was one of the primary routes from the
city, though the mountains and to points beyond.

Although it was considered a highway, it's actual use
was still fairly limited. The surface was paved. Many
of the roads in the area had been paved at one point,
and the old asphault surfaces could often be seen
under the dirt. The difference with this road, however,
is that this road was still maintained. It lacked the
potholes, loose dirt, and gravel which plagued the other
roads. Never had Tyler seen a road maintained as well
as this one.

The maintenance of this road meant it was traveled by
an entirely different category of vehicles. Many of the
vehicles were cargo vehicles, carrying goods from city
to city. Tyler had never seen cargo vehicles travelling so
fast and straight on such a smooth surface. 

The width of the road was also impressive. For most
of the distance, Tyler guessed that four or five vehicles
would be able to travel side be side.

Despite the impressiveness of the road, it was only
minimally used. Tyler only saw a handful of cars during
her first hour following the road. More common, were 
people walking along the side. There were also some
bikers and people on horseback.

After following the highway for a while, she began to
feel less safe. The people in the vehicles were traveling
to fast, and the walking were getting too numerous.
She would not feel comfortable sleeping along this road.
She decided to plan an alternate route.

After taking a break and sitting under a fir tree to have
some lunch, she had mapped out a new route on her
Page. The new route would take her through some of
the smaller communities on the outskirts of the city
instead of following the highway.

One of the things she was happy to notice while looking
at the map was that she was now approaching
Broadcast range and would soon be in the arms of
continuous webwork coverage. If she calculated correctly,
she would cross over sometime the next morning.

Tyler had about three more hours to cover today. Then
she would establish camp. Tommorow she would enter
Broadcast range, and by the next day, she would be
standing in the center of the city.

With a new plan in place, she exited the highway and
made for the smaller roads. The foothills from which
she had been decending the past couple days had
given way to flat, fertile, ground. She was now 
walking through farm country.

The farms in this part of the Union were unlike farms
like the one on which she had lived. The farm she had
lived on was a community farm. The farm produced
a variety of crops for the purpose of feeding the 
members of its community. In contrast, these farm
produced single crops, which they sold in the city.
Many of the farms in this area had been farms for 
centuries. The population of these farmhouses was
usually a single family. Many of these families were
not considerate of travelers and would turn away people
such as Tyler. Whenever possible, Tyler would avoid
these people for a place to sleep.

Instead of checking at the farm, Tyler kept walking.
She continued looking for an unoccupied place
she could sleep for the night, but the unoccupied
buildings were getting very difficult to find as she
got closer and closer to the city. This close, an
occupied building was usually torn down so the
materials could be reclaimed.

As the night stretched out, Tyler began getting less
picky about her location for resting. She remembered
the night under the bridge just a couple days ago
and promised she would not make the mistake again.

In the end, she ended up crossing a field into a wooded
area. A trail had been warn down somewhat which led
to the area, but there seemed to be no fresh tracks.
Once at the trees, she poked around in the dark, using
her Page to
light the way. Camps had obviously been set up here in
the past. It was times like these that Tyler wished she
owned a tent. She never had owned one, and it seemed
useless to own one when there were so many empty
buildings in the area in which to sleep. On nights
like this, though, she felt very different about the situation.

In the end she found some pieces of lumber which she
threw together to make a basic lean to. She simply
rested the larger pieces against a tree, and laid the other
pieces against those. She didn't think it would be water
tight, but it didn't look like rain tonight and she had been wet
before, even if it did rain.

The simple shelter had done quite well for the night. It had
been a little cold at times, but she had stayed well bundled.
Anyway, if everything went according to plan, she'd be in
the City tonight and wouldn't have to sleep outside.

Yesterday, the scene had changed from foothills to farmland.
Today, the scene changed again; to neighborhoods.

Before the Destruction, there were so many people alive
that they lived in massive groups of houses all clustered
together. Miles and miles of homes were constructed and
packed together as tightly as possible to accomodate the
dense population. These areas were usually situated on the
outskirts of major cities. Tyler was entering the edge of what
used to be one of these now.

The change from farmland to neighborhood land was abrupt.
One moment Tyler was walking between adjacent farms
and then the farms on both sides of her ended at an old,
crumbling wall which extended on both directions. The wall
had and opening through whcih the road entered. Tyler passed
between the walls and continued following the road.

Once on the other side of the wall, she could see that the
road had at one point had a variety of other roads connecting
to it. Only a few of these were still in any use. Most had been
reclaimed by nature.

The second thing Tyler noticed was that this neighborhood had
been home to many, many, houses. Inbetween the old roads,
empty foundations littered the grounds in what appeared to be
almost a grid formation. The areas that weren't road or foundations
had been grown in with vegetation, giving the impression that
Tyler was walking through a paved forest.

There were still homes in the neighborhoods, but they were
sparse. It appeared that for every one hundred homes that
were originally standing, only one was now left. The others
had been harvested and sold, their materials being reused in
other projects.

The land was no good for farming, but many of the people
living in these unusal areas had begun raising cattle. In most
places, barbed wire lined the edges of the street and Tyler
noticed a number of cows, quietly chewing their cud and 
watching her pass. 

She walked through area like this for a long time and
found it remarkable how many people must have lived
here at it's peak. She imagined hundreds of people
surrounding her in the steets on their way to or from
work, school, or the homes of family and friends.

As she continued, she passed other area which seemed
to have been almost completely flat and paved in the days
before the Destruction. Everything for great distances
around her would be flat and paved with piles of other
stuff that also looked flat and paved. Nature had not made
much recovery in this area, and people seemed to be
avoiding it, as well.

It was around three in the afternoon when her Page
alerted her that it had connected to the Broadcast.
She took the Page out of her pack and enjoyed, for the
first time in her life, unlimited access to data. Manifest
items she normally waited all week to access were now
available just a few seconds after requesting them.
She was amazed at the potential in her hands but
forced herself to put it away.

Now inside the Broadcast zone, the landscape around
her changed dramatically. Immediately, she began seeing
a lot more people. Fewer building had been torn down
and most of them had solar power arrays. This explained
the obvious increase in electricity usage.
Everything was still paved, but instead of piles of
rubble, the residents had put in gardens. Electric vehicles,
passed her frequently on the streets and she had to 
actively remember not to walk blindly in to the road.
She began seeing many businesses; restaurants, electronics
stores, hardware stores, fabric stores, and building supply stores.
This city was the most active place she had ever seen.

As she continued walking, she thought of her parents
spending months here every year. Despite all the time
they were here, they never brought her along and they
rarely talked about it. Seeing it all for the first time now,
Tyler was irritated they had never shared this experience
with her.

It was time to find somewhere to sleep for the night. The
sun was just setting now, and it would be getting dark.
But as Tyler began to consider her options, the lights
lining the street came on. Tyler admired the simple
luxury of the street light and kept walking. There was no
need to stop now.

She walked another hour and a half before seeing a Motel
on the other side of the street. She had always heard not
to sleep on the streets in the City, so she'd need to pay
for somewhere to stay for now.

The motel was small and only seemed to have around
five rooms. At least, that is what she saw from the street.
It was a simple rectangular, single story, building with six doors. The
first five had the letters A through E on them and the 
last door had the letter M, G, and R. She walked
cautiously into the door for the manager.

The manager was sitting at a regular desk in the small
room. There was nothing on the desk and Tyler guess 
it was only there to give the man sitting at the desk a 
place to set his Page. Tyler stood just in the door and
waited politely.

"Do you need a room?" said the manager.

"Uh. Yes." said Tyler.

The manager launched into what must have been
a common utterance.

"It's 24000 coin a night. We take dollars at the current
rate. Checkout time is 10 am."

Tyler was shocked at the price, and tried to talk him
down.

"That price is a bit steep. I paid half that last night."

"Not around here, you didn't." the man said, "24000
is the going rate. Do you want the room or not."

He could have been telling the truth; he could have
been lying. There was no way to know. But,
Tyler believed the man was probably right about the
price. She filled out the appropriate form
on her Page and submitted payment for the room.

Tyler received access to room five. It was sent to
her Page. She walked the short distance from the
manager's office to the door marked with the
number five. The software on her Page unlocked
the door and she went into the room.

Tyler was used to sleeping outside, and her room
at the farm had been minimal. In contrast, her
room at her parents cabin had been quite nice.
The room in which she would be staying tonight
was similar to her room at the farm. The bed was
made of a simple wooden frame with a firm
bedding pad laid on top. For someone used to
sleeping on the ground, this would be a nice
change. A few decorations hung on the wall.
A long, narrow, wooden table sat along the wall
opposite the bed. Tyler set her pack down on the
ground and looked at the rest of the room.

There was a closet, but it was completely empty,
without even a shelf inside. It was obvious this
was not a room in which they wanted you to
be unpacking.

The most amazing feature of the room to Tyler
was the bathroom. Never in her life had she
stayed in a place with an attached bathroom with
working plumbing. At the cabin, they had used an
outhouse and inside had installed a small shower.
The farm had a shared bathroom for each
barracks. Tyler marveled at the toilet and decided
to immediately give it a trial run. The bathroom
also contained a bathtub, although a sign
above it warned that the hot water was only
available during the day. Since she would be
leaving early tomorrow, it was doubtful she
would get a hot shower. She returned to the
bed a sat down on it. She pulled up the city's
news channel on her Page.

Normally, Tyler was not interested in the news of
the city. Living in an iscolated community meant
that news from the city was only important if war
errupted, and they last few years had been peaceful.
Now, being in the city, it seemed like it might be
good to know a little about current events. Plus,
the Broadcast access meant the channel would be
avaliable to her basically live.

The news broadcast for the day discussed, among
other things, the cut to the far reaching Broadcast.
This peaked Tyler's interest because she had not
yet heard the details of this decision. The report had
a number of Union representatives on the program
speaking to why the decision was made. Very few
specifics were given other than vague terms such as
"budget limitations" and "power limitations". As
usual, no real information was provided.

The next full Broadcast was coming up in just a few
days, and Tyler decided she needed to apologize to
Triss. After all, if she didn't get the
message to him on this Broadcast, he wouldn't
hear from her for another two weeks. She wrote him,
urging him to be patient and try to understand.

After finishing the letter to Triss, Tyler planned her
trip to the Union Police Station tomorrow. The station
was on almost the complete opposite side of town,
and would be a full day walk. She knew the city had
a transportation system, but was not sure if it would
take her to the station.

She was able to find the schedule for a train which
ran in an east west direction across town. She could
connect with it to the south of the motel. It would take
her across the city, leaving her just a few miles
south of the Union Police Station. The site for the
train did not service any other transportation options,
but explained that local taxi service was available
throughout the downtown city area.

The train was a good option for her. It seemed reliable
and was not too far out of the way. If it all worked out,
this would save her most of the day; she could be at the
station before noon.

She was happy with her plan. Other than the run in with
the investigators in the other town, the trip to the City
had been smooth.

With the last of her time before bed, Tyler decided it would
be a good idea to get her clothes washed. She unpacked
and threw all her clothes into the bathtub. She also removed
the clothes she was wearing and
added them to the tub. She filled the
tub with a small amount of cold water. Kneeling beside the
tub and using the soap
left by the sink, she scrubbed her clothes clean as best she
could, then wrung them out and hung them to dry in the
bathroom. Then, she got in the tub herself and washed
in the cold water.

Tyler laid down on the mattress and pulled the blanket
around herself tightly. She was cold from the bath and from
not having anything to wear while her clothes dried.
However, it was nice to be in a heated room again and before
long she was warm and sleeping.

\chapter{Union Police Station}
The next morning was sunny and warm. It was going
to be a very nice day. Tyler was wearing clean clothes
and was excited to be nearing the end of her trip.
She left the room by eight. She stopped by the
manager's office to check out, but the door was locked,
so she just left.

It was active on the street. Most of the people she saw
appeared to be heading to the market or jobs away from
the home. Children were heading to school; some alone
and some with parents. She headed south from the motel.
The train station was about a mile away.

The short walk was nice, and made her feel like she
hadn't traveled several days to get where she was. No, this
just felt like a quick trip across town. Tyler had never
really thought she would like city life, but she was now
beginning to see how the conveniences could be very nice.

She reached the train station to find a large group of
people waiting for the next arrival. She stood on the
platform with the others and waited.

The train arrived about twenty minutes later. The machine
was quite the sight to see. It was three train cars, very
warn down, and in need of paint. The top of the train had
been modified to hold solar arrays. This was obviously
a train from before the Destruction and Tyler was amazed it
was still running. But, the people standing with her on the
platform did not hesitate boarding it. Tyler followed.
The entry through which she boarded was missing the door
and she noticed many of the other doors were also absent.
It seemed that having a door on the trains was fairly low
on the list of maintainence priorities.

The thirty or so people who boarded with Tyler were at
first riding a mostly empty train. By the next stop, the train
was full. At the third stop, Tyler was amazed to learn that
the train had not been full at the previous stop, and the
number of people on the train roughly doubled. As the train
continued, the rider population eventually stabilized, but
not before Tyler had gotten very comfortable with an older
woman and skinny man with a beard halfway down his chest.

The buildings the train was passing were getting increasingly
fancy, implying to Tyler that this was a much nicer area of town.
The power usage in the area was remarkable. The streets were
lined with lighted windows and giant displays scrolled
advertisements for fashions, makeup, jewelry, and things Tyler
had never seen before. As the train traveled through this
area, many of the working class got off the train, obvious
off to service the rich community that populated this part of
town.

There were still a number of stops until the one at which 
Tyler had
figured was the best to desembark. She saw the affluent
section of town fade quickly and it was replaced by several
miles of demolished wastelands. Tyler recognized this
area as a casualty of war. During the Destruction, at the
height of violence, the City had been liberated by Union
forces, and this section of town had been the battlefield.
By the end of the Destruction, the population of the area
had been so greatly reduced, that rebuilding this area
simply had not been an option and it existed now mostly
devoid of life; a landscape of urban destruction. The track
on which the train ran seemed to be one of the only
things now stretching through this barren strip.

Before long, the train rose up and crossed a large river.
When it decended on the other side of the river, the
destruction through which they had been traveling was
replaced by another area of civilization. Looking outside,
Tyler saw warehouses and other industrial looking buildings
interspersed with large gardens,
and factories. This area had been the primary focus of
rebuilding in the city since the destruction and was home
to the growing middle class population.

Tyler was nearing her stop. After another mile the train
slowed, came to a stop, and Tyler was finally able to get
out of the cramped train. She was not clostrophibic, but
she had never been around that many people and
the experience had been understandably stressful.

The train had dropped a good distance away from the
station; around three or four miles away. She decided
she could walk it, although she was tempted just to
take one of the many pedicabs cruising the area looking
for passengers.

The perception from the train made this part of town
seem quite populous. On the contrary, it was actually
similar to most of the other parts of town. Many of the
buildings were crumbling and boarded up. Most of
the properties were locked behind fences; owned but
unused. Much of the land was currently unused.

Additionally, the streets were now mostly empty.
A few people roamed the area and pedicabs moved a
few people from place to place. Tyler saw many people
working in the gardens, which had been strategically
placed in parking lots and abandoned lots having
good sunlight. These gardens supplemented the
nearby residences and helped offset the high prices
of food.

Tyler walked through this area and eventually reached
the Union Police Station. The facility was one of the
only buildings in the area which had been completely
constructed since the Destruction. It seemed extremely
modern compared to most of the buildings in the area.

Because the Union Police State also hosted the prison
for the area, it was completely enclosed in fencing. Tyler
followed this around until she found the public entrance.
She entered the building and found herself in small room.
Aside from the entrance door, there was another door,
which lead to the heart of the station. This door was
guarded by a U.P. soldier. Next to the door, a counter had
been installed and behind the counter on the other side
of the locked door, another soldier sat looking down
at something in front of him on his side of the wall. This
would be the place she would get information.

The soldier guarding the door eyed her but did not say
anything. The soldier behind the counter did not even
look up at her. Now that she was finally here, she realized
she didn't really know what to do.

She walked up to the counter, which caused the soldier
to finally acknowledge her but looking up at her. He
didn't say anything, though.

"Hi," she said to him, "I need to get some information
about a prisoner. Actually, two prisoners."

The officer directed her the the appropriate form to
request information. There were chairs sitting around the
outside wall of this small reception room and Tyler sat in
one of them to begin filling out the form. After half an
hour, the forms were completed and she transferred them
into the stations system. She returned to the window and
informed the clerk that she had completed the forms. He
verified her identification and told her to return in two
hours for the information. Tyler left the waiting room,
not wanting to sit around in
there for two hours waiting. She didn't really have anywhere
to go, though.

/chapter{Morgan and Triss}
Morgan looked around her bedroom she had shared with
Gily. Her heart and her body missed him all the time.
Her mind went back and forth. For one moment, she
would feel happy to be rid of him and his temper. During
these times, she would remember that Gily had been
sleeping with Grace. The reasonable part of her brain would
empathise with Grace since, she too, had lost the man she
cared for. Morgan had seen Grace around the farm a few
times since Gily's death. No one on the farm knew about
Grace and Gily. It would be risky if that kind of information
got out. Morgan could see Grace's grief, hidden behind her
strong face. As much as Morgan hated that woman for
coming between her and her husband, she felt terrible
for Grace having to grieve alone and in silence.

It was Morgan who approached Grace while she hung
laundry on a line next to the barracks. Grace stopped
what she was doing as Morgan approached. Grace watched
Morgan, and Morgan mostly looked at the ground.
Then Morgan reached down and picked up one of the bedsheets
from the laundry basket and began hanging it from the line.
The two women hung the rest of the laundry in silence. When
the last item was hung and the basket was empty, Morgan
stepped forward and hugged Grace. Grace stood, arms at her
side, unsure what would happen next. Morgan just held her
and then whispered two words in her ear.

"It's okay."

A tear rolled down Grace's cheek as she raised her arms and
hugged Morgan back. The two women stood in silence,
once enemies, but now with a common sadness. They
stood together for some time, and as time passed, Grace
held her tighter. Then, suddenly, Grace pulled away and
looked down at the ground.

"I'm sorry," she said to Morgan. She then walked quickly
away, leaving Morgan alone.

The next morning, Morgan was working in the garden
with Triss. Triss had been very anxious since Tyler had
left and she seemed to be the only thing on his mind.
He seemed to be transforming his anger at being left
at the farm into worry about Tyler's safety.

Morgan had been trying to keep silent around Triss,
and Triss had done his best to avoid her since her outbreak
in Jondra's office. Between his worry for Tyler and his
fear of Morgan, he was obviously struggling to keep
his mind on his gardening. And to this Morgan's mindset,
and the whole process of gardening was just asking for
a blowup. Tensions were high.

In the midst of this, Grace walked up. She was leading
a horse which was pulling a cart of manure. The manure
was loaded in burlap sacks in the back of the cart.

She walked over to where Triss and Morgan were working
together in silence. Morgan and Grace may have had their
moment yesterday, but today, their relationship felt like it
had backtracked some, at least to Morgan it did.

"Triss?" called Grace in a friendly-enough tone, "Would you
please help me unload this cart?"

Obviously Triss knew nothing of the secret relationship
between Gily and Grace. He stopped his work and went
to help. Morgan watched as she continued hoing in the
dirt. She tried to hide the one eye she seemed to have
continually watching the man who had killed her husband
and the woman who slept with her husband.

Triss lifted the sacks of manure down to the ground as
Grace slid them towards the back of the cart. Together,
they made short work of the task. When the cart was
empty she jumped down from where she had been standing
in the back. She thanked Triss and then gave him a hug.
Morgan found the hug offensive. A hug for unloading a
cart of manure. She found the forced flirtation terrible
and regretted consoling the woman yesterday in an
effort to make her fell better. It seemed to have done the
job and Grace seemed ready to move on the the next
victim. But at least Triss was single. Still, Morgan did not
like thinking that Grace's next target was her friend
(former friend?), Triss.

Her current job done, and with nothing further to flirt
with Triss about, Grace returned to wherever it was she
came from. Morgan watched and felt a strange
satisfaction having Triss back helping her in the garden.

That night, Morgan took her dinner to her room to eat
alone. Spending all day as the widow of a violent maniac
who had been hiding out in the community was hard
enough during the day. It was nice to be away from
everyone whenever possible.

Morgan sat cross legged on her bed. She had a small
chair and desk in the room, but she preferred to sit on
the bed most of the time. Tonight she was listening to
music on her Page. Mostly she listened to New Rock, but
would also browse music from the last two centruries
and enjoyed the low quality music characteristic of 
early recording technology.

As she sat engrossed in a particularly interesting song
which she had never heard, there was a faint knock
on the door to her room. She waited for a second
knock, which came a couple seconds later. She got up,
set her dinner on the desk and crossed the room to
the door.

She opened the door and saw Triss standing on the
other side.

"Hi, Morgan." he said quietly.

Morgan sighed, but she wasn't mad, just tired of thinking
about everything.

"What do you want, Triss?" she said.

"Uhm," he started, "I'm supposed to have you read
something."

He handed her a folded scrap of paper. It seemed
very childish to be using paper to pass notes. But,
she took the paper and unfolded it. It read:

Triss,
Please share this note with Morgan. Then
meet me at the Education Circle at
10 o'clock. It concerns Gily and Tyler.
Please keep this a secret.
~Grace

Morgan read the note twice through before her head
began to comprehend it. She was actual reading a
secret message. Her heart beat jumped substantially
as she considered the implications of what the
message meant. In a way, it was terrifying.

Triss was still standing outside her room, and Morgan
stepped aside so he could come inside. She closed
the door behind him. He stood inside the room,
apparently unsure if he was supposed to say anything.

Two days ago, she would have marched straight to
Jondra with a note like this, but with everything that
had been happening, it deserved more consideration.
She sat on the bed and looked at Triss with desperate
eyes. She really had no idea what to do.

It might have been the mention of Tyler, but Triss knew
what he wanted to do.

"I want to go." he said with confidence.

His determined stance and the issue was enough for
Morgan, who wouldn't have been able to make this
decision. She shrugged and put her hands up.

"Sure," she said, "let's go, I guess."

The Education Circle was about twenty minutes away
from the farm. It was used for a variety of farm events,
but it got it's name from it's use as an outdoor
classroom for children. It was a simple ring of logs
for seating in a cleared out area of the forest.

As Triss and Morgan approached the Circle, Morgan
had a sinking feeling that they were
about to be murdered by
Grace for killing Gily. But, she was commited
at this point to meeting Grace, so she pushed
the thoughts from her head and pressed onward.
Triss was more eager and had been setting a quick
pace since they left the farm.

At the circle, they saw Grace standing alone in
the middle of the Circle. She was bundled up
in a thick jacket and hat. She also had a large
scarf wrapped around herself. It all combined
to add sustantial bulk to someone who was
actually quite thin.

She watched them approach, but didn't move.
She kept her hands in her pockets as Morgan
and Triss entered the circle and walked up to
her.

"Hi Grace," said Morgan.

"Hi," said Grace, and she smiled, "Thank you
for coming."

Grace's smile was very warm and, Morgan
thought, maybe only a little forced. But, she
felt instantly a little more comfortable knowing
that this might not be the last few moments
of her life.

Grace jumped to her point.

"There is something that needs to be told,"
said Grace, "and I want to tell you."

She paused.

"I've been spying on the farm. I work for the
Union and I've been spying on the farm."

Grace exhaled, having obviously just had
a heavy burden lifted from her. But she was
also obviously nervous about admitting it.

"What?" said Morgan. "Why would you tell
us that?... Why would you do that?"

Morgan was stunned. It was unthinkable.
Why would there be a spy on a farm? What
had she been doing that they didn't know
about.

"Look," Grace replied, "I've had a change of
heart. I've learned too much and I can't
do it anymore." She looked at Morgan.
"Losing Gily was the last straw."

"You're really a spy?" asked Triss, "You kill
people and stuff?"

"No," she said, "I'm not an assassign. I don't
kill people."

Morgan spoke up again. She was angry.

"I don't understand what you're trying to
say to us. Why don't you just leave? Just
leave us all in peace and let us get back to
our lives!"

She turned around and walked away, her
hands rubbing tears away from her eyes.
She walked across the circle and sat on one
of the logs. Triss looked back at her, concerned,
but he still had another thought
that was at the front
of his mind.

"What does this have to do with Tyler?" he asked
Grace.

"Gily was sent to kill Tyler." she said, plainly.
"That's what it has to do with her."

Morgan looked up suddenly, "What about Gily?"

"Gily was also a spy."

Morgan stood up and walked back towards
Triss and Grace. When she neared, she suddenly lunged
at Grace. She pushed her hard and Grace fell back on
the ground. Morgan fell on top of her and with her right
hand she connected a strong slap across Grace's cheek.

"You bitch!" screamed Morgan.

Grace had her arms up to defend herself and Triss
was trying to pick Morgan up and pull her off Grace.
Morgan fought to free herself. Grace didn't fight
back and soon Morgan had calmed down a little.

"Gily was not like that! He loved me and he would
never do that."

Morgan was a mess. She was standing, but was
crying. She fought against Triss and probably
would have run back the farm if he had let
her go. In her head, there were so many conflicts
that she couldn't think straight.

Grace began to stand up slowly. Her cheek was
bright red and in the cold it felt like it had cracked
open in a million places. Her eyes watered and 
she held her hand to her face in a futile attempt
to ease the pain.

Grace spoke again, "I want to help. I'm risking
my own life and giving up a great career. Please
just listen to me."

Morgan finally gave into the emotions racing around
in her head. She went suddenly limp in Triss's grasp
and fell to the ground and the tears came in streams.
Triss knelt beside her and tried to hold her. For the
next few minutes, the three of them held their
positions. Morgan cried in a fetal position, processing
recent events. Triss held her quietly, not sure what
to say or do. Grace rubbed her burning cheek and
silently watched the scene.

Finally, Morgan's sobbing subsided, and Grace
risked taking a few steps forward. She sat down
on her knees facing Triss, who was holding Morgan.
Morgan did not look at Grace.

"Let's go save Tyler." she said, looking at Morgan.
"She is in danger. Many people are. We can help."

"What do you mean?" Morgan's muffled voice
came from Triss's shirt. "Who is in danger?"

"Let me explain," said Grace, "I'll tell you what
I know."

Grace told them about her spying. She had joined
the Union Police when she was younger and had
quickly been recruited as an undercover soldier.
There, she had worked a variety of jobs infiltrating
the lives of criminals and bringing evidence to the
Union. Her skills in this had led her to be offered an
assignment with a special unit.

"Slaves." she said.

"Slaves?" repeated Morgan. She had slowly forgotten
about her anger and she listened to this women
spill her story to them. It was an unbelievable
scenario.

"Yes. The Union is taking slaves."

"What would be the reason for needing slaves?" said
Morgan.

"The Union needs to rebuild the technologies from
before the Destruction. The secrets of that prosperity
are locked away in records. The governments that
unlock the mysteries first are the governments that
will be on top."

Morgan went on to tell them what she knew about
the process. The mission of Grace's team was 
to identify and mark the smartest people they could
identify from all across the Union. Once those people
were identified, the Union Police were sent in to
apprehend them. The government would arrange for
a falsified trial and the people were sent to work in
the technological reclaimation project. The project,
composed of enslaved teams of engineers and scientists
across the Union worked together to bring back
the technologies of the past.

"So, wait," Triss said, "No one from the farm has been arrested.
If both you and Triss worked as spies, how come no one
was taken away?"

Morgan agreed with Triss's observation and looked inquisiteivly
at Grace.

"I don't know." Grace said. "We were both put here and told
to keep our eyes open and report in regularly. That was it."

Morgan felt like she was leaving something out. But, there
was nothing about the story that she could point to as being
inaccurate.

"So, why did Gily suddenly go after Tyler?" Morgan asked.

"After Tyler's mother showed up in town, Gily received
instructions to capture her. He was not supposed to kill
her."

Grace seemed to be finished with the story. She then,
went on to tell them her plan.

"I have an idea for how to save Tyler. We need to get to
the city first." Grace said.

Morgan and Triss considered what she was saying. If Grace
really intended to go to the city, they would need to be 
completely sure they trusted her story.

Triss said, "How do we know we can trust you?"

The question sounded very cliche at the time, but it was
perfectly reasonable to ask.

"Look," said Grace, "When Gily went after Tyler, I realized
that this line of work will eventually force you to do
something that I wasn't prepared to do. When I realized
this, I knew I had to do something."

Grace went on to explain that she had grown very happy
on the farm. She liked Jondra and she liked the people.
She realized the corruption that existed in the city and
within the government. Grace also did not believe in
slavery and would no longer be able to support a
government that was now embracing it in a world
that finally seemed to be, in many ways, on the right
direction. Grace was really taking a new path with her
life.

"It might be too late," she said to them, "I may lose my
life for this decision. But with Gily gone, now, it seemed
like the right time to make a change in my life. I want
to do the right thing."

Morgan looked at her. The last thing she had said
about Gily had reminded her that this woman had
taken her husband away from her. This was not a
woman to be trusted, but Morgan believed most
of her story. If she was who she claimed to be,
then Tyler really was in trouble. She could use
Grace's knowledge to get Tyler back. Then they
could decide what to do with Grace.

Morgan stood up and put out a hand. Grace took
it and shook it and tried to give Morgan a little
smile. Morgan was able to give one back.

"So, what's the plan?" asked Morgan.

The three of them spent the next couple hours
talking about their trip to the city. They would take
basically the same route as Tyler. It was the best
way to get to the city. They would send messages
to Tyler if possible, although they needed to be sure
were not being monitored. They would look for Tyler
in the city and hope to reach her in time. Grace knew
the area and had training hiding out. They would
have to move quickly and there was no way to know
for sure the plan would work.

Triss asked if they would tell Jondra.

"No," said Grace, "I have another idea."

\chapter{Leaving the Farm}
The next day, Triss and Morgan went about
their chores as usual. It was a rainy day, and
everyone was working indoors as much as
possible. Morgan had been trying to get some
cleaning done in the farmhouse. She started on
the top floor and began working her way down.

Triss was doing some repairs in the barracks.
There were a few things which had been on
his todo list for some time, and with the rain
he decided to get them done.

Around lunch time, Triss headed over to the
house for some food. When he got inside he
served himself up a plate of food from the
meal which had been prepared by Vishnu.

As he sat eating lunch, Morgan came over to
join him. She also had a plate of food. They
sat and talked and decided they would take 
a walk after lunch.

They grabbed jackets and headed outside
in the rain. The walked out west, towards the
Education Circle. No one on the farm saw them
return.

By mid-afternoon their absence was noticed.
And Jondra was notified. She sent Jamal out
to look for them. Another resident, Grace, was
also missing. Jamal searched around the forest
and found a few of what looked to be their
footprints, but they were only able to track them
a short distance before the rain washed away 
the evidence.

The small search party returned to the farm to
began looking for the other missing person,
Grace. In her room, they found the answer to
all three of the missing people. The evidence
was turned over to Jondra.

Jondra read a letter, the evidence that had 
been found, and learned that Grace had been
working with Gily. Both her and Gily were Union
agents and had been living undercover at the farm.
As part of the investigation into Gily's death, she
had been ordered to bring Morgan, his widowed
wife, and Triss, one of the two involved in his
death.

She had taken them secretly so as not alarm the
farm. Jondra was free to tell the residents anything
she wished. Jondra read the letter carefully.

Losing three more people caused her a great deal
of concern. She felt as if the residents she looked
after we all living secret lives. She wondered how
many other people had hidden agendas or secret
communication with the outside world. She decided
she would need to have a long meeting with Jamal
to get to the bottom of this mess. She stormed off
to her office to make plans.

\chapter{On the Road}
Mrgn Grace and Triss were now on the road. They
were walking in the rain. Grace had brought their
packs out to the woods earlier, allowing them an 
easy way to leave the farm. Now they all walked
together, ready for their trip to the city.

Triss and Morgan were both a little worried. Neither
of them had spent much time away from the farm.
They were now on a new road to a new place. None
of this was normal for them.

"How many days is it to the city?" asked Triss.

"Probably four days if we can cover good ground."
replied Grace. "And I might be able to get us
transportation at some point.

Morgan noticed that Grace's personality had
dramatically changed since she had revealed
herself to be a spy. Before she had been quiet,
and reserved. Now she was confident and sturdy.
It was easy to see why she was recruited for
the job she had. The way she had hidden this
personality for her time on the farm had been
amazing.

Grace had been on the farm for almost two years.
Morgan remembered that Grace had arrived after
Gily. At the time, of course, she had no idea that
Gily and Grace were both part of the same group
of soldiers and were undercover agents working
on the farm.

As they walked, Grace explained the situation.
Having abandoned her post at the farm to help
expose the Union for the slavery scandal, she
would almost surely be executed. Grace knew
this and she accepted it. But, Grace was also
trained at blending in and staying hidden. She had
abandoned her Page at the farm, meaning her
entire connection to the world was severed, but she
would be establishing a new identity, anyway, once
they reached the city. She had a few connections
still which were not loyal to the Union and she could
ask a few favors.

Having no Page, though, meant she had no money.
Morgan and Triss had very little money, as they had
lived on a communal farm their entire lives and had
little need for it. Still, they would need to move the
money soon. It was unlikely Jondra would notify
the UP's of anything, but if the soldiers came by the
farm, Jondra had no reason to hide anything from them.

All the signs pointed to having a plan that assumed
the Union would figure out everything. Grace would
show Triss and Morgan how to move their money to
an unanimous location and how to get access to it
when they needed. She would show them a couple
simple tricks for hiding there whereabouts. There was
no reason for them to get rid of their Pages, but there
were certain habits they needed to pick up.

\chapter{Tyler's Parents}
Tyler returned the the Union Police information desk.
The soldier now had several people in the waiting room,
including two other soldiers, one man in handcuffs, and
several other people who seemed to all be friends of the
man in handcuffs. They were having a heated discussion
with the soldier on the other side of the counter who
had helped Tyler just a while ago.

The soldiers were trying to get the proper permission
to admit the man to the holding cell in the back. The man
waiting for be thrown in jail seemed to not care what
happened one way or another, but his friends were adamant
that he had done nothing wrong.

The scene went on this way for some time, but eventually,
the beurocracy gave way and the two soldiers and the man
under arrest were admitted through the locked door and
disappeared into the depths of the Union Police station.
The other people fought in vain with the soldier at the
counter but eventually retreated to the chairs where they
pouted and continued arguing with each other.

Tyler waited patiently and tried to judge when the soldier
manning the counter was ready for her. He seemed to
work continuously with a variety of forms, so she eventually
just approached and asked her question directly.

"Is my information ready?"

The soldier looked at her a minute as if he didn't recognize
her. Then it struck him and he nodded.

"Yes. The inquiry." he said to himself. "No matches, I'm
afraid. They aren't in here."

Tyler was confused.

"No. They have to be. The soldiers came to the farm and took
my mother to the City. They said she was a fugitive. She was
injured."

The man in uniform looked back at her.

"Look. They aren't here. That's all I know, and that's all
I can tell you. Anything else would need Union Court
approval."

The soldier went back to his work despite the fact that
Tyler just stood there. When she realized he was reliberately
avoiding her, she walked away.

She felt a blow to her spirit. She had come all this way,
hoping to be reunited with her parents, even if just to
see them for a few moments, and now she was being
told they simply weren't here. She didn't have another
plan; there was nowhere else to go.

Tyler sat on the sidewalk down the street from the
station. As she considered her next move, three
soldiers approached her. One of the soldiers stood
between the other two and seemed to be in command.
He looked at Tyler for a moment, seeming to size
her up, and then spoke.

"Tyler, you need to come with us."

"Why?" she asked.

"You are being placed under arrest. We will detain
you until we receive further instructions."

The soldiers on either side of him stepped forward.
Being on the ground, she had no chance of escape,
and she probably wouldn't have attempted it even
if given a better opportunity. She had no other
ideas. There was nothing to do right now. She had
no place to stay tonight and she had no idea where
her parents were. At least, by being arrested, she
would be able to get some answers to her questions.

Tyler stood up and held up her hands. The soldiers
began the process of her arrest. Within a few
moments, they were heading back toward the
office and Tyler felt confident she would soon
find herself on the other side of the the man and
his counter.

\chapter{Morgan and Triss}
Morgan, Triss and Grace were spending their first
night on the road to the city. Grace was on high
alert for UPs, which would be on the lookout for
her, the runaway spy. Fortunately, in this area,
Union Police were rarely encountered. Still, to be
safe, she had insisted they sleep far from and traffic
and had hiked them a good half mile off the road.

They were learning a lot about Grace. She carried
a gun. She was great at picking a camp site. She knew
where to find food. Befriending a professional
spy was useful.

The campsite she had found was a shed of some sort,
on the edge of a river. The floor in the shed was rotted
and damp, but she improved this by laying down
tree limbs. Part of the metal roof had rusted out and
she used it to vent the small fire she build right inside
the sleeping area. The built the fire small, but surprisingly
warm and she showed them how to keep it from smoking
too much.

Grace went down to the stream and came back thirty
minutes later with fish. Triss and Morgan were both
impressed. They wrapped the fish in moss and cooked
it right on the fire. They went to bed warm, full, and
comfortable.

The next day they woke up early and continued their
journey. It was another rainy day.

Grace asked for one of their Pages and Morgan took
out hers and handed it to Grace. Grace showed them
how a Page could be used to provide a rough map of
people in the area. At least, it could identify anyone
who was carrying a Page or another similar device.
She explained that it was a feature built into the
webwork, but was not provided to most people. In
addition to people without pages, it would not identify
devices off the webwork, which would include many,
but not all, of the Union Police devices. Some UP devices
still utilized the webwork to maintain communication
with the station.

Morgan had been warming up to Grace, which upset
her whenever she stopped to think about it. She felt
there was a silent agreement between the two women
not to bring up Gily or anything related to their relationship
with him. This was probably wise, since thinking about
Gily was still difficult for Morgan.

Triss was fascinated by Grace. At least, Triss was
fascinated by the new Grace. Undercover, Grace had
been plain, soft spoken, and capable at basic farm
chores. Most people knew her, but she had few friends.
She had never stood out in any way. Looking back,
Morgan realized this is exactly the way you want to
act when you are spying.

The new Grace was very good at everything she did.
She even looked different. She had changed her posture
and was even wearing her clothes a little different.
All these changes were reflected in Triss, who she
noticed was following her around like a puppy. Morgan
recognized it as the way Triss was around Tyler. The
interesting thing about Grace was, again, the change.
Triss had never taken notice of her on the farm and now
he seemed ready to profess his love.

That night they reached the small town. It was the same 
small town Tyler had spend a night in just a few days
before. Grace was cautious, but still walked straight
into town. If she was worried about the UPs it wasn't
showing. It seemed as if Grace might have a destination
in mind, which she did. She walked them into a bar, 
probably the only bar, along the cities main street.

The bar was populated by what were obviously regulars.
There were half a dozen or so, sitting right up at the bar,
talking with an old bearded man who was probably the
owner and the sole employee.

Grace through her pack down at one of the tables and
motioned for Morgan and Triss to have a seat. They
sat down their own bags and sat in the wobbly, hand made
wooded chairs. Grace walked up to the bar.

The group had the attention of the bar tender, and the
regulars, so Grace had no trouble getting service. The
man with the beard walked over.

"What can I get for ya?" he asked Grace.

She responded in a low, indirect voice, that was probably
heard just find by the bar tender but was almost
impossible to work out from where Morgan and Triss
sat. Another spy trick, apparently.

She had a long transaction with the man and, in the end,
the man shook his head. Grace's demeanor changed and
she stood up from the bar stool. She said a few more
words to the man, but he was just shaking his head and
slowly walked back to the regulars.

Grace walked back to the table with a scowl on her face.

"This isn't the place." was all she said.

She picked up her pack and hoisted it back onto her
back and headed for the door.

Morgan and Triss caught up with her on the street.

"What was that about?" asked Morgan.

Still bitter, Grace said, "I was hoping to work out a
place for us to stay tonight, but I guess we're camping
again."

The group walked on. It was already late, but Grace
took her time picking a place that was far enough from
the bar in case her outburst had raised any red flags.
The found a house that seemed abandoned, but there
was no fresh food that night. They ate dried food from
the farm and went bed.

The next couple days of travel passed in the same
manner as the first, except without the run in with
evil bartenders. Grace continued to lead the way
towards the city with Morgan and Triss in tow.

Eventually, they reached Broadcast Coverage, and
Grace began to be more cautious. She had told them
she planned to stop by and visit a friend who could
help them with some supplies.

Shortly after reaching Broadcast Coverage they came to
a railroad bed. It was highly grown in, but it was still
obvious in many places that it had once carried trains.
There were some places where the iron track emerged
from the ground and continued a distance before
burrowing back into the encroaching nature.

The followed this track for several miles, although
they were still passing through the limits of the City.
There were people living in the houses and other
buildings on either side of the track, but not very
many.

Grace had been here before and knew the way. She
steered them off the track at one point and walked
through some fields before arriving at their destination.

The place they had reached was more like a fortress
than a house. It was a lone building, smaller than
many buildings in the area, but on a much larger lot.
The lot was contained by ten foot fencing with razor
wire running around the top. A sign warned that
anyone crossing the fence would be shot. It warned
not with words, but with an illustration showing a
stick figure being shot off the top of a fence.

The small building in the center was obviously not
the reason for the extreme level of protection. Surrounding
the small building, placed right on the ground, a
massive solar array had been installed on the ground
around the building. There appeared to be hundreds
of panels, of different shapes and sizes, all wired
together. Whoever lived here was in control of a
significant amount of electricity.

The group went to a gate that seemed to be the only
entrance into the compound. Morgan noticed several
unmanned turrets following their movements, ready
to shoot them down at command. The gate opened
shortly after they walked up, without any
communication needed. The guns were still trained
on them as they entered the fenceline and approached
the building.

Before they reached the building, the gate was closing
behind them and, at the same time, a man was
emerging from the building. He was a middle aged,
muscular man with a goatee. He wore a dark grey,
hooded sweatshirt under a black leather vest. He had
a sidearm holstered at his side and was carrying a
long rifle casually in this right hand.

As he approached, another man came out from the
building. The second man was thin and clean cut,
with blonde hair cut very short. He work a thick,
short sleeve jacket, and black gloves. He stood closer
to the entrance of the building and did not approach
the group.

As the first man reached the group, he put his arms
out to give Grace a hug.

"Jackie! How are you?" the man said to Grace.

"Hi, Joe," Grace replied. "I'm good. And it's Grace now."

"Grace, huh? Well, it might take me a while to get
used to it. Who are your friends?"

"Joe, this is Morgan and Triss." said Grace.

"Good to meet you two. I guess anyone with Jackie...
or Grace... is more than welcome here."

Morgan and Triss shook hands with the man named
Joe and they started walking towards the building.
As the walked, Joe pointed ahead to the other man
standing in fron of the building.

"This here is Nate. He's got the smartest head I've
ever seen."

Nate waved and walked forward to meet them. They
all shook hands.

"Well," said Joe, "We should get inside and catch up.
There is always a heck of a story when Grace shows
up."

Nate replied, "You go ahead. I'm out here now. I
may as well wipe down the panels."

Nate went off to start his work. Joe showed them inside.

The inside of the building was much more finished than
the outside had been. Morgan suspected the outside
must have been a decoy intended to not drawn any
attention. From to looks of things on the inside, Joe
and Nate actually had a large respect for details.

The deceptive quality of the outside was the size. Standing
out amonst the panels, the building seemed small
and not extremely comfortable. In side, though, the space
had been used extremely well. Additionally, Morgan saw
a staircase leading to a complete lower floor and who knows
how many more floors lay below that. She imagined a
continued levels going down forever.

Joe kept the group on the first floor and guided them into
a large room with a long table with plenty of seating for
everyone. The lighting in the room was amazing. There
were artificial windows around much of the room and
the windows put off a glow of natural light, making it
seem you were sitting inside on a hot summer day.
The over all ambiance of the room complimented this
feeling. It was warm, but not too warm, and although
it was probably only fifty degrees outside, the warmth
of the light coming in the windows tricked Morgan's
head into thinking it was actually much warmer. 

Joe brought them beer, in a bottle, something Morgan
had never had. Once in a while, people on the farm
woud barter for beer from one of the local traders, but
not very often. People at the farm had tried making
their own alcohol from time to time, but it had never
really been worth the effort. The few people on the farm
who did drink regularly, bought a foul tasting chemically
mixture that was available for cheap.

Triss seemed to be new the the drink, also. He took a
small sip and then glanced over at Morgan with a weird
face that almost made her laugh out loud. Curious, she
took a drink of her own bottle and realized that Triss's
face was about right. It wasn't bad, so much as it was
and odd flavor to be drinking. She took another sip, trying
not to let her curiosity show too much. She decided it
was probably something she could get used to.

Grace and Joe had begun talking. Grace was telling him
that she had left the Union Police and was trying to help
find Tyler.

"Jesus," said Joe, "You've given yourself a death sentence!"

"Yeah, maybe I have," said Grace, "but I couldn't support
the Union slave trade anymore. You were right this whole
time. I should have gotten out years ago."

"Well, I'm glad you came to you senses. But to just leave
your post? I could have helped you get out cleanly." said Joe.

"I know," Grace said, "But there really wasn't time. I had to
make the decision then.

"What happened to that husband of yours?" Joe asked Grace.

"He died a long time ago," said Grace, and suddenly looked
very, very, sad.

Losing his smile, Joe said, "I'm sorry, dear, but that guy was
not the one for you."

"No, I suppose not."

Joe changed the subject.

"Well, obviously you're here because you need something.
What can I do for you?" he said.

The four of them talked about the plan. Mostly Joe
and Grace talked, obviously being the more experieced
ones, but Triss and Morgan had a role to play as well.

Grace told them she needed money, of which she had
plenty but could not access it right now or it would
reveal here location. Joe had a couple idea for solving
this, but wasn't sure which one would actually work.
They moved on.

The second topic was transportation. It would be
useful if there was a fast way to the city. Tyler already
had a three day head start on them and was probably
already at the city. If they could get to city by tonight
or early tomorrow, they would have a better chance
of finding her before she was picked up by the Union
Police. Joe could help with this.

Joe asked them about supplies, food, weapons, and
other things they might need. Grace explained that
they may need a few basics, but nothing too aggressive.
She wanted to avoid violence, if possible.

Nate came inside, apparently done with his cleaning
of the panels. He offered to make dinner, which was
agreeable to everyone. He went to work again as the
conversation continued.

Joe wanted to know what information they would need
for the journey. Grace asked what he knew about the
Union Police locations and if he knew anything the
locations of the slaves.

"Well," said Joe, "the location of the slaves has always been 
somewhat a mystery. I didn't even know if they
existed for sure until now. It was always just a
rumor."

"I know, Joe," said Grace, "But they are there, somewhere.
Any ideas?"

"Well, I can think of two places you can check, but don't
be surprised if there is nothing to find."

Joe took out his Page and pulled up a map.

"The first location," he said, "is this large building located
directly next to the Union Police station. It is large, I think
it used to be a hospital, but it's abandoned now. This is 
the most obvious place."

He pointed to another location.

"This is a second place I've considered. It's outside of
town but is still maintained for something. Union Police
are sometimes seen in the area, but it's pretty quiet.
It might be worth checking out."

"Our first priority is finding Tyler," said Grace.
"She is heading right
to the Union Police, and doesn't realize they will arrest
her on sight."

Joe said, "Tyler will probably go right to the Union
Police station, unless they pick her up on the way
there. Either way, she'll probably be held in the
temporary cell while all the paperwork is processed."

"How long is that?" asked Triss.

"Probably twenty four to forty eight hours." said Joe.
"Does she have her Page on her?"

"Yes." said Triss. "She always has it, and I know she
left with it. In fact, I got a message from her when
she was a few days outside of the city."

"I did, too." said Morgan.

"Well, we ought to be able to message her now, right?"
asked Grace.

"Yes, we are in Broadcast range." said Joe.

"I've been trying," said Triss. "There's been no response."

"Then we have to assume she has already been arrested,"
said Joe, "And also, the Union Police will probably start
monitoring your Page, Triss. Probably yours, too, Morgan."

"We should probably take them off the webwork now,"
said Grace.

"I agree," said Joe.

Morgan and Triss took out there Pages and Joe guided
them through the process of turning off the antennas.
He also walked them through the process of turning it
back on, since they would no doubt need it at some
point.

It was around this time that Nate finished dinner and
called them all into the kitchen to get a plate.

Joe and Nate didn't have a garden and didn't have any
animals such as chickens or goats, from which to
get food. Because of this, she was quite surprised with
the food. It was all really good.

As Nate explained, he and Joe were part of a small
group promoting the use of bulk produced foods, a
manufacturing process which had all but died out
during the Destruction.

Processing foods in bulk and distributing them allowed
large supplies of food to be produced which would
keep throughout the winter. It allowed a greater
variety of foods to be provided year round.

Triss and Morgan were very impressed by the variety of
meats and vegetables they were eating, and although
the flavor was fairly dull, she was happy just be eating
some items which normally were only available for
short times of the year.

When the dinner was finished, Nate collected the
dishes and went off to clean up the kitchen.

"What are you doing with all the power you're
generating outside?" asked Morgan of Joe.

"Ah, well, I don't share all my secrets," replied Joe,
and then he changed the subject, "Do you guys want
to see your transportation?"

Joe took them across the building. They entered a
room at one
end which was large and cold. The floor was cold,
smooth, concrete. Joe turned on the lights. In front
of them, in the center of the room, a large object
was covered with a sheet. Joe removed the sheet
to reveal a large vehicle.

"Wow!" said Triss.

The vehicle was impressive. It was wide and
low to the ground. It was almost entirely black.
The entire surface of the car was covered in 
solar panels.

"This is a big improvement over that last piece
of junk you had," said Grace.

"That's thanks to Nate." said Joe.
"I told you he was a
genious, right?"

Joe walked around the car.

"I'll have to drive you, but it will hold all of us.
And it has enough charge to get all the way
there and back even at night."

Morgan and Triss were both excited at the prospect
of getting to ride in this. Even Grace seemed a
little excited about the trip.

"We can leave soon," said Joe, "Let's just get
Grace her money."

The process of unlocking Grace's money from
her identity took Nate's help. He used a service
based outside the Union, through which he
submitted a request to move Grace's coins to
a temporary card. Temporary cards were used
for people without Pages or without bank
accounts. They were called temporary cards
because they were not meant to hold coins for
long term. However, since they could be
unanimous and hard to track, they were commonly
used for underground transactions.

"Okay, Grace." said Nate, "Here's
the card. I'm sure you've
used these before, and things haven't changed.
Most places will accept them, but it always raises
a red flag. Some people will even call the UPs if
you use it, so be careful.

"They'll be able to see that you moved the money
from the account, but they won't know where. So,
you're pretty safe. It will probably be twelve hours
before the card will work."

"Thanks, Nate." said Grace.

Next, Joe took them to his pantry, and gave them
a few small supplies. They didn't need much, but
they did take a couple of their processed goods,
which were relatively easy to carry.

Grace asked about weapons, and disappeared with
Joe downstairs. Morgan and Triss were not invited.
They reemerged shortly and Morgan was a little
relieved to see that Grace didn't have a rocket
launcher or other overly large weapon.

It was getting late, which was confusing since the
false windows in the building made it feel like
early afternoon. Based on the time, it would
already be dark outside.

They hauled their stuff to the car. First, Nate held
open the large door leading outside the building
and Joe rolled the car out into the yard. The rest
of the group followed with all their bags and
supplies. Joe packed it all carefully in the cars
tiny storage space.

Nate gave the vehicle a quick inspection and
verified everything was ready to go. The three
travelers got in, followed by Joe in the driving
seat. The gate at the front of the compound
was already open and Joe didn't waste anymore
time. He pressed the accelerator and the
vehicle began rolling towards the gate with
only the crunch of the wheels rolling on the
dirt and the faint hum of the electric motors.

\chapter{Driving}
The trip in the electric car was amazing for
Morgan and Triss. It was a very rare experience.

At first, the roads were bare dirt, and were not
well maintained. But, the car had been designed
for this kind of surface and did a good job
absorbing the impact of the bumps which Joe
was unable to avoid.

Joe explained that there were several roads
through the city which were regularly maintained,
the closest of these was a couple miles away.
Until they reached these, the going would be
slow.

The total distance to the Union Police station was
around thirty miles and most of that would be on
the maintained streets. The electric car was not
very fast, but Joe figured they could make it in
roughly two hours.

The plan that Joe and Grace had devised was not
violent, but it would be tricky. Grace was going to
let herself be arrested. Without her Page or any
identification, she would be put in the holding cell
which would hopefully be where Tyler was being
kept. But, knowing that Tyler was off the grid, it
was likely that this was where she was. Once inside,
she could get a message to Tyler.

Grace assured Morgan and Triss that she could
break the two of them out once she got inside. All
they needed to do was wait nearby.

The vehicle was approaching the maintained street,
which could be identified as a long string of lights
stretching out into the distance. Joe slowed the 
vehicle as it approached the road. After allowing
several vehicles to go by, he pulled out onto the
smooth pavement.

On the smooth surface, Joe accelerated the vehicle
up to its top speed, which was a little less than forty
miles per hour. This limit was mostly self imposed by
the sheer amount of weight in the vehicle, but keeping
the speed helped ensure the vehicle could provide
the distance necessary to make it practical.

There were a good number of vehicles using this
road, more than Triss or Morgan had ever seen at
one time. White headlights and red taillights glowed
in both directions as the followed the road. The
majority of these vehicles were commercial transportation
vehicles, carrying cargo across the Union and to other
countries for trade. Occassionally, though, they would
pass or be passed by a smaller vehicle.

As they traveled, they passed from the outer area of
the city to the downtown area. The size of the city
was astounding. In some of the older areas of the
city, skyscapers still stood from before the destruction.
Although many of these building had be demolished
due to safety risks, the Union had left some of them
up, although the grounds on which they stood were
off limits. In fact, most of the area around these large
buildings was uninhabited.

Everyone had seen videos of large cities before the
Destruction, and a few of the older people still shared
stories of it, but actually being there and trying to
picture what it used to be like was very difficult.

The road they were on never brought them close to the
old downtown area, but instead looped safely around it.
They were now just a few miles from the Union Police
station.

As they approached the area of the station, Joe explained
that he would drive past the station and then find a safe
place to drop them off away from the entrance. All vehicle
traffic was cateloged in the city, and although no one ever
really seemed to monitor it, caution was still important.

Joe turned off the main road and onto the side streets.
These roads were still maintained, although not to the 
same level as the primary roads through the City. He
made another turn on the road which he said would 
bring him directly by the Union Police station. They drove
at a regular speed past the office where just a few
hours earlier, Tyler had been arrested. Joe
continued driving another half mile and then turned down
a side street and stopped the car.

The group emerged from the car and Joe helped unload
their packs. It was dark, but it wasn't particularly late, and
a few people were walking around in the night. Joe gave
Grace a hug and whispered something in her ear. Then he
approached Morgan and Triss and gave each of them a
warm hug as well. He said goodbye and got back in the car.
Before they knew it, he was gone.

Grace got the group moving again, as she was the only
one not currently enthralled with their environment.
Since both Morgan and Triss had never been to the city,
she was going to get them setup. They had the easy
job of waiting. While Grace went undercover and broke
Tyler out of the Union Police station, all they needed to
do was hang out in a hotel room and wait. Grace was 
even paying for the room since they had almost no
money. Grace felt a little cheated about having to risk
her life, do all the work, and pay for everything,
but this was the way the plan had come together.

The place they had been dropped off was not by a
hotel, but a quick check with one of the locals left them
with several options. They chose the one closest to the
Union Police station and headed that way. As they
walked, Grace gave her coin card to Morgan.

"I can't go in and get the room with you." said Grace,
"It will raise suspicion when I don't ever show up again.
Do you still remember what to do?"

"Yes. I just go to the front counter and prepay for a room
for four nights. I ask for a spare key. Then, I meet you
back outside with the key and the room number."

"Good." said Grace.

The got to the hotel, which was of modern design but
still seemed run down. Grace did a walk around the
block while Triss and Morgan went inside.

The check-in process was completely automated, which
made things easy. The only problem came when they
needed a spare key, which the automated system was
unable to handle. Morgan pressed a button for help
and after a few minutes, a disheveled man came to
help. He seemed confused at first about the spare key,
but their made up story about Triss not having a Page
seemed to clear things up and the man disappeared for
a few minutes. He returned with a card that looked 
similar to Grace's coin card and handed it to them.

"That should do it." he said to them. "The range on those
things ain't great, so if it gives you trouble, wave it right
in front of the lock."

The man left and they went back outside to meet Grace.
She met them a ways down the street. They gave her
the spare key and the room number. Morgan gave her
a big hug.

"You don't really have to do this." Morgan said to Grace
with tears forming in her eyes. "None of this is your
responsibility."

"Yes it is." said Grace, "And even if it's not, I have the
opportunity to do something good and make up
for some of the bad deeds I've done in my past. This
is something I want to do."

Morgan kept hugging her. Eventually, their embrace
ended and Grace turned and walked away. Morgan and
Triss watched her for a moment and then returned
to the hotel. They walked past the automated check in
machine and up the stairs to their room.

\chapter{Imprisoned}
Tyler was in the holding cell. There were a couple other
people with her in the cell, and she was avoiding all
of them. She was scared and felt very alone.

After they had processed her at the front desk, they
had taken all her possessions and put her into the
cell without any information other than that she would
be in the cell until the next morning. So, she was sitting
and waiting. It was cold and uncomfortable.

One person
in the cell with her was an elderly woman, pacing back
and forth. Whenever Tyler looked her direction, the
woman would snap and start yelling at her. The Union
Police soldier would then come tell her to quiet down
and the process would repeat. At this point, Tyler had
become good at avoiding looking her way.

Another person was very young, definitely less than
twenty. She looked tough, and dangerous. She sat
in one corner confidently and stared at
Tyler. The few times Tyler had glanced at her, she
had received a suspicious looking smirk that made
her skin crawl. It was as if the girl had already made
plans for Tyler and was just waiting for her opportunity.

The last two prisoners we friends, probably more than
friends, based on the fact that they were holding each
other. They were obviously drugged up, probably self
induced, and likely didn't even know where they were.
They sat together on the floor whispering and giggling,
at least during the times they were conscious.

Compared to the prison cell with the men in it, Tyler's
cell was tame. Shortly after she arrived there had been
a fight in the cell, and the soldiers had broken it up with
a beanbag cannon. The loser of the fight had been drug
out of the cell and somewhere out of the room, the
winner of the fight had been bean bagged, tazed, and
drugged. Many of the other men in the cell were passing
the time by whistling at Tyler and the other women in
her cell.

No one new had been added to Tyler's cell since she
had arrived, but it looked as if there might be someone
else being brought in. One of the soldiers had left the
room and as he left, Tyler could see a group of soldiers
by the door.

A few minutes later, they came in with a woman in 
handcuffs. Her hair was a mess and it looked as if
the soldiers were basically holding her up as they
made their way to the cell. All the prisoners' attention
was on the new girl.

"Put her in with us!" shouted one of the men from the
cell on the other side of the room.

"Shut up!" barked one of the soldiers, but otherwise
ignored him. The legs of the woman they were escorting
suddenly buckled and she fell to the ground.

"Get up!" said the soldier support her right side. He and
soldier on her other side lifted her up, but the woman
was not coorportating and held her legs in the air.

They issued more commands.

"Put your feet down! Put 'em down!"

One of the soldiers behind her slapped the back of her
raised ankles with his hand. The woman relented and
put her feet under her and again supported her own
weight.

One soldier slid open the cell door and the others pushed
the woman in to the cell. She stood on her own and they
let go of her. She stood with her head down, hair covering
her face. She half fell, half sat down and slumped over. She
almost seemed to be asleep.

The soldiers shut the cell door. Most of them left, leaving
just the one soldier who had been guarding the prisoners
for most of the night. He returned to whatever he had
been doing on his Page.

The crazy elderly woman who had been pacing walked up
to the new girl on the floor. She leaned over and shouted
into her ear.

"Move out of my way!" she shouted.

"Hey!" shouted the guard. "Knock it off."

The new girl stood up slowly, using the bars of the cell
for balance. She started moving over toward where
Tyler was sitting alone on a bench. Suddenly, the new
girl ran at Tyler, tackling her off the bench and onto
to the floor. The guard jumped up immediately.

"Hey!" he should again.

The guard ran up to the cell and banged on the bars
with his nightstick. Tyler was on the ground with her
up, protecting her head. She felt like the new girl was
trying to bite her neck. Tyler flawled, but she wasn't
strong enough to get free. Suddenly the woman whispered
directly into her ear, close enough that it drowned
out the guard's banging on the bars.

"It's Grace, from the farm," said the woman, "Pretend
you don't know me."

The woman suddenly stopped thrashing Tyler about, but
continued to hold her down. Tyler stopped and looked
at the woman. She recognized her face for the first time.
It looked calm, rational, and intelligent. She did know this
woman from the farm.

Suddenly, the woman's face twisted and she looked
suddenly insane again. She turned her head to the guard
who had gone to get the bean bag cannon. She jumped up
and suddenly ran at the bars. She didn't stop running
and ran right into the bars. There was a loud clanking
sound and the woman fell to the ground and didn't move.
The guard came over to the bars and knelt to get a
look at the crazy woman on the ground. He seemed
to decide that everything was back to normal and returned
to his chair. He took out his Page and continued whatever
it was he had been doing.














\end{document}